---
title: "girlSurvey Data Management"
author: "Kevin Gilds"
date: '`r Sys.Date()`'
output:
  html_document:
    toc: yes
---

# Data Management

### Set working directory, library, and read raw data (needs updated data)


```{r}
########################Set Working Directories##################
setwd("C:/Users/kevin/Dropbox/GetReal/Data/2015-2016/June 2016")

library(dplyr)


###########################Read Data#############################################

rawdata <- read.csv("girl_survey_06262016.csv", skip=1)

rawdata <- rawdata[-(2),]

dim(rawdata)

names(rawdata)

```


### Change column names to make them human readable.
```{r}

########################### Change Column Name #################################

colnames (rawdata)[7] <- "hr.sum"
colnames (rawdata)[8] <- "hr.avg"
colnames (rawdata)[9] <- "hr.stddev"
colnames (rawdata)[10] <- "hr.disqualify.sum"
colnames (rawdata)[11]<- "hr.disqualify.avg"
colnames (rawdata)[12]<- "hr.disqualify.std"
colnames (rawdata)[13] <- "ae.sum"
colnames (rawdata)[14] <- "ae.avg"
colnames (rawdata)[15] <- "ae.stddev"
colnames (rawdata)[16] <- "am.sum"
colnames (rawdata)[17] <- "am.avg"
colnames (rawdata)[18] <- "am.stddev"
colnames (rawdata)[19] <- "ae.disqualify.sum"
colnames (rawdata)[20] <- "ae.disqualify.avg"
colnames (rawdata)[21] <- "ae.disqualify.std"
colnames (rawdata)[22] <- "am.disqualify.sum"
colnames (rawdata)[23] <- "am.disqualify.avg"
colnames (rawdata)[24] <- "am.disqualify.std"
colnames (rawdata)[25] <- "council"
colnames (rawdata)[26] <- "girlCode"
colnames (rawdata)[27] <- "school"
colnames (rawdata)[28] <- "grade"
colnames (rawdata)[29] <- "Time"
colnames (rawdata)[30] <- "inProgramLastYear"
colnames (rawdata)[31] <- "iamMotivatedToGraduateHighSchool"
colnames (rawdata)[32] <- "iReadBooksforFun"
colnames (rawdata)[33] <- "ireallyLikeWhoIam..."
colnames (rawdata)[34] <- "..ImproveMySkilsThisYear"
colnames (rawdata)[35] <- "...UnderstandMyClassWork"
colnames (rawdata)[36] <-  "learningatSchoolIsImportantToMe"
colnames (rawdata)[37] <- "oneOfMyGoalsIstoLearn..."
colnames (rawdata)[38] <- "...WillHelpMeLaterInLife"
colnames (rawdata)[39] <- "ifIHaveASeriousProblem..."
colnames (rawdata)[40] <- "inAnyRelationshipOrNotIMakeItClear"
colnames (rawdata)[41] <- "iTalkWithMyTeachersBeforeOrAfter..."
colnames (rawdata)[42] <- "iHandinMyAssignmentsOnTime"
colnames (rawdata)[43] <- "iFinishMyHomeworkEvenIfItisBoring"
colnames (rawdata)[44] <- "ifICantUnderstandMySchoolatFirstI..."
colnames (rawdata)[45] <- "iLetPeopleKnowIfTheyHurtMyFeelings"
colnames (rawdata)[46] <- "iLetMyFriendsKnowWhenIThinkTheyAreGoodAtSomething"
colnames (rawdata)[47] <- "ILearnedFromTheBooksWeReadThisYear"
colnames (rawdata)[48] <- "myReadingSkillsImprovedThisYear"
colnames (rawdata)[49] <- "EstablishedAPostiveRelationship..."
colnames (rawdata)[50] <- "...HelpedMeRecognizeThingsIDoWell"
colnames (rawdata)[51] <- "whatDidYouLearnThisYear. "


```

### Make Student Code as class character and make all codes upper case.

```{r}

######################## Change Girl Code #################################

rawdata$girlCode <- as.character(rawdata$girlCode)

rawdata$girlCode <- toupper(rawdata$girlCode)








str(rawdata$girlCode)

dim(rawdata)

```


### Test Chunk
```{r}
###Test to see if any test girlCode in system
#rawdata$girlCode

####Test to see if any test schools in syste
#rawdata$school

###Fix if any girlCode is in Test
rawdata <- filter(rawdata, girlCode !="TEST")

council_girlCode <-with(rawdata,table(girlCode, council))

#council_girlCode

```




### Subset all finished surveys

```{r}

####################Subset Finished#####################################
# Finished 

fin <- subset (rawdata, Finished  == 1)


str(fin$girlCode)




dim(fin)


```

#Pre Surveys

### Subset Pre surveys

```{r}

############################## Subset Pre ############################3

pre <- subset (fin, Time == "Pre")
dim(pre)

```


### Subset Pre Surveys with unique student codes

```{r}

######################Find Unique Values################################################
preUnique<- pre [!(duplicated(pre$girlCode) | duplicated(pre$girlCode, fromLast = TRUE)), ]

dim(preUnique)

```


### Subset Pre Surveys with duplicate student codes (needs updated data)
```{r}
##############################Subset duplicated girl codes##################

setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

preDupes <-duplicated(pre$girlCode) | duplicated(pre$girlCode, fromLast=TRUE)

preDupes <-pre[preDupes, ]

dim(preDupes)



```




# Post Survey 

### Subset post girl surveys

```{r}
##############################Subset Post###############################
post <-subset (fin, Time == "Post")


```


### Find unique student codes from post surveys
```{r}
##########################Subset Unique Post Values####################

postUnique<- post [!(duplicated(post$girlCode) | duplicated(post$girlCode, fromLast = TRUE)), ]


```


### Find duplicate student codes from post surveys
```{r}

#########################Subset Unique Post Values######################
postDupes <-duplicated(post$girlCode) | duplicated(post$girlCode, fromLast=TRUE)

##### I think this is pulling the actuall duplicate values####################
postDupes <-post[postDupes, ]


```

### Save Data to Shiny (Web Application)
```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Reports/Apps/girl_survey_app")

saveRDS(preUnique, file="girl_survey_03092016.rds")

```




### Send data to Sqlite database
```{r}
library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

### Write Q1 Expelled data to sqlite database
dbWriteTable(conn = getReal_2016db, name = "girl_pre", value = preUnique, row.names=FALSE, overwrite=TRUE)

dbWriteTable(conn = getReal_2016db, name = "girl_pre_duplicates", value = preDupes, row.names=FALSE, overwrite=TRUE)

dbWriteTable(conn = getReal_2016db, name = "girl_post", value = postUnique, row.names=FALSE, overwrite=TRUE)




```

