---
title: "girlSurvey Data Management"
author: "Kevin Gilds"
date: "Saturday November 14, 2015"
output:
  html_document:
    toc: yes
---

# Data Management

### Set working directory, library, and read raw data (needs updated data)


```{r}
########################Set Working Directories##################
setwd("C:/Users/kevin/Dropbox/GetReal/Data/2015-2016/November 2015")

library(dplyr)


###########################Read Data#############################################
rawdata <- read.csv("girl_survey_11142015.csv", skip=1)
dim(rawdata)

```


### Change column names to make them human readable.
```{r}

########################### Change Column Name #################################

colnames (rawdata)[6] <- "hr.sum"
colnames (rawdata)[7] <- "hr.avg"
colnames (rawdata)[8] <- "hr.stddev"
colnames (rawdata)[9] <- "hr.disqualify.sum"
colnames (rawdata)[10]<- "hr.disqualify.avg"
colnames (rawdata)[11]<- "hr.disqualify.std"
colnames (rawdata)[12] <- "ae.sum"
colnames (rawdata)[13] <- "ae.avg"
colnames (rawdata)[14] <- "ae.stddev"
colnames (rawdata)[15] <- "am.sum"
colnames (rawdata)[16] <- "am.avg"
colnames (rawdata)[17] <- "am.stddev"
colnames (rawdata)[18] <- "ae.disqualify.sum"
colnames (rawdata)[19] <- "ae.disqualify.avg"
colnames (rawdata)[20] <- "ae.disqualify.std"
colnames (rawdata)[21] <- "am.disqualify.sum"
colnames (rawdata)[22] <- "am.disqualify.avg"
colnames (rawdata)[23] <- "am.disqualify.std"
colnames (rawdata)[24] <- "council"
colnames (rawdata)[25] <- "girlCode"
colnames (rawdata)[26] <- "school"
colnames (rawdata)[27] <- "grade"
colnames (rawdata)[28] <- "Time"
colnames (rawdata)[29] <- "inProgramLastYear"
colnames (rawdata)[30] <- "iamMotivatedToGraduateHighSchool"
colnames (rawdata)[31] <- "iReadBooksforFun"
colnames (rawdata)[32] <- "ireallyLikeWhoIam..."
colnames (rawdata)[33] <- "..ImproveMySkilsThisYear"
colnames (rawdata)[34] <- "...UnderstandMyClassWork"
colnames (rawdata)[35] <-  "learningatSchoolIsImportantToMe"
colnames (rawdata)[36] <- "oneOfMyGoalsIstoLearn..."
colnames (rawdata)[37] <- "...WillHelpMeLaterInLife"
colnames (rawdata)[38] <- "ifIHaveASeriousProblem..."
colnames (rawdata)[39] <- "inAnyRelationshipOrNotIMakeItClear"
colnames (rawdata)[40] <- "iTalkWithMyTeachersBeforeOrAfter..."
colnames (rawdata)[41] <- "iHandinMyAssignmentsOnTime"
colnames (rawdata)[42] <- "iFinishMyHomeworkEvenIfItisBoring"
colnames (rawdata)[43] <- "ifICantUnderstandMySchoolatFirstI..."
colnames (rawdata)[44] <- "iLetPeopleKnowIfTheyHurtMyFeelings"
colnames (rawdata)[45] <- "iLetMyFriendsKnowWhenIThinkTheyAreGoodAtSomething"
colnames (rawdata)[46] <- "ILearnedFromTheBooksWeReadThisYear"
colnames (rawdata)[47] <- "myReadingSkillsImprovedThisYear"
colnames (rawdata)[48] <- "EstablishedAPostiveRelationship..."
colnames (rawdata)[49] <- "...HelpedMeRecognizeThingsIDoWell"
colnames (rawdata)[50] <- "whatDidYouLearnThisYear. "


```

### Make Student Code as class character and make all codes upper case.

```{r}

######################## Change Girl Code #################################

rawdata$girlCode <- as.character(rawdata$girlCode)

rawdata$girlCode <- toupper(rawdata$girlCode)

str(rawdata$girlCode)


```


### Subset all finished surveys

```{r}

####################Subset Finished#####################################
# Finished 

fin <- subset (rawdata, Finished  == 1)

dim(fin)
```

#Pre Surveys

### Subset Pre surveys

```{r}

############################## Subset Pre ############################3

pre <- subset (fin, Time == "Pre")
dim(pre)

```


### Subset Pre Surveys with unique student codes

```{r}

######################Find Unique Values################################################
preUnique<- pre [!(duplicated(pre$girlCode) | duplicated(pre$girlCode, fromLast = TRUE)), ]

dim(preUnique)

```


### Subset Pre Surveys with duplicate student codes (needs updated data)
```{r}
##############################Subset duplicated girl codes##################

setwd("C:/Users/kevin/Dropbox/GetReal/Data/2015-2016/November 2015")

preDupes <-duplicated(pre$girlCode) | duplicated(pre$girlCode, fromLast=TRUE)

preDupes <-pre[preDupes, ]

dim(preDupes)

####Save object to RDS file
saveRDS(preDupes, file="duplicate_girl_survey_11142015.rds")
write.csv(preDupes, "pre_girl_dupes.csv", row.names=FALSE)

```


### Save Pre Data to RDS File (needs updated data)
```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/2015-2016/November 2015")

saveRDS(preUnique, file="girl_survey_111415.RDS")


```



# Post Survey 

### Subset post girl surveys

```{r}
##############################Subset Post###############################
post <-subset (fin, Time == "Post")


```


### Find unique student codes from post surveys
```{r}
##########################Subset Unique Post Values####################

postUnique<- post [!(duplicated(post$girlCode) | duplicated(post$girlCode, fromLast = TRUE)), ]


```


### Find duplicate student codes from post surveys
```{r}

#########################Subset Unique Post Values######################
postDupes <-duplicated(post$girlCode) | duplicated(post$girlCode, fromLast=TRUE)

##### I think this is pulling the actuall duplicate values####################
postDupes <-post[postDupes, ]


```


### Save Post Survey (needs updated data)
```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/2015-2016/November 2015")

saveRDS(postUnique, file="girl_post_11142015.rds")



```

