---
title: "parent data management"
author: "Kevin Gilds"
date: '`r Sys.Date()`'
output:
  html_document:
    keep_md: yes
    number_sections: yes
    toc: yes
---

# Data Management Script for the Data Survey. 


**Data must be download from Qulatrics into a CSV file. Save the csv file into the directory below.**


## Set up R to receive the data and load the data into R. (update directory and file name)
```{r}
library(dplyr)

setwd("C:/Users/kevin/Dropbox/GetReal/Data/2015-2016/July 2016")

parent <- read.csv("parent_survey_07152016.csv", skip=1)



```



## Make variable names easier to read
```{r}


colnames (parent) [6] <- "council"
colnames (parent) [7] <- "girlCode"
colnames (parent) [8] <- "schoolName"
colnames (parent) [9] <- "Time"
colnames (parent) [10] <- "graduate"
colnames (parent) [11] <- "sheHasSelfConfidence"
colnames (parent) [12] <- "goodAttitudeAboutSchool"
colnames (parent) [13] <- "readsBooksForFun"
colnames (parent)[14] <-  "positiveRelationships"
colnames (parent)[15] <-  "homeworkWithoutSupervision"
colnames (parent) [16] <- "helpedMyDaughterGainConfidenceInHerAbilities"
colnames (parent)[17] <-  "helpedMyDaughterAchieveSuccessInSchool"
colnames (parent)[18] <-  "helpedHerEstablishPostiveRelationshipsWithHerClassmates"
colnames (parent) [19] <-  "helpedYourDaughterAchieveSuccessInSchool"
colnames (parent) [20] <-  "ImproveTheGetRealProgram"


```


```{r}
parent <- filter(parent, girlCode !="Test")
parent <- filter(parent, schoolName !="Emerson")

### Change council names to be consistent wiht how they displayed with the surveys
parent$council <-sub("Girl Scouts of the Gateway Council", "Gateway Council", fixed=TRUE, parent$council)

parent$council <-sub("Girl Scouts of Citrus Council", "Citrus Council", fixed=TRUE, parent$council)

parent$council <-sub("Girl Scouts of Southeast Florida", "Southeast Council", fixed=TRUE, parent$council)

parent$council <-sub("Girl Scout Council of Tropical Florida", "Tropical Council", fixed = TRUE, parent$council)

parent$council <-sub("Girl Scouts of West Central Florida", "West Central Council", fixed = TRUE, parent$council)

parent$council <-sub("Girl Scout Council of the Panhandle", "Panhandle Council", fixed = TRUE, parent$council)



```






## Fix varaibles that will be trouble later
```{r}
##################Data management########################33


parent$girlCode <- as.character(parent$girlCode)
###Change girl code to character

parent$girlCode <- toupper(parent$girlCode)
###update girl Code to Upper Case




```


## Subset for finished surveys

```{r}
parfin <- subset (parent, Finished == 1)
### Find the finished data entry

##### Elements of the data frame
dim(parfin)


```







# Pre Survey
```{r}

parentPre <-filter(parfin, Time =="Pre")


```



### Find and subset unduplicated Pre cases
```{r}


parentPreUnique <- parentPre [!(duplicated(parentPre$girlCode) | duplicated(parentPre$girlCode, fromLast=TRUE)), ]

dim(parentPreUnique)

```


### Find the duplicated student codes

```{r}



### Find duplicates
parent_pre_dupes<-duplicated(parentPre$girlCode) | duplicated(parentPre$girlCode, fromLast=TRUE)

##### I think this is pulling the actuall duplicate values####################

parent_pre_dupes<- parentPre[parent_pre_dupes,]

## How many duplicates
dim(parent_pre_dupes)

```







# Post Surveys
```{r}

#### Subset Post Surveys
parentPost <-filter(parfin, Time == "Post")


```

## Find and subset unduplicated Post cases

```{r}

parentPostUnique <- parentPost [!(duplicated(parentPost$girlCode) | duplicated(parentPost$girlCode, fromLast=TRUE)), ]


```



### Send data to Sqlite database
```{r}
library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

### Write Q1 Expelled data to sqlite database
dbWriteTable(conn = getReal_2016db, name = "pre_parent", value = parentPreUnique, row.names=FALSE, overwrite=TRUE)


dbWriteTable(conn = getReal_2016db, name = "pre_parent_duplicate", value = parent_pre_dupes, row.names=FALSE, overwrite=TRUE)


dbWriteTable(conn = getReal_2016db, name = "post_parent", value = parentPostUnique, row.names=FALSE, overwrite=TRUE)




```