---
title: "Program Components"
author: "Kevin Gilds, MPA"
date: "July 22, 2016"
output: word_document
---



```{r echo=FALSE, warning=FALSE, message=FALSE}

library(dplyr)
library(pander)
library(ggplot2)
library(sqldf)
library(psych)
library(knitr)
library(gridExtra)
library(effsize)
library(likert)

library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

books <- dbReadTable(getReal_2016db, "girl_post")

books <- books %>%
    select(46,47)


pander(sessionInfo())

```



Program Components:

 The education literature has shown that students who are engaged in school achieve better educational outcomes such as higher grades and greater achievement on standardized tests. In contrast, students who are disengaged are at a higher risk for dropping out of school. Student engagement is multiple dimensional including behavioral engagement, emotional engagement, and cognitive engagement. Behavioral engagement consists a student's participation in school activities. Emotional engagement refers to the connections and interactions a student has with peers and teachers. Cognitive engagement refers to resilience and the hard work required to be successful at school (Fredricks et al., 2011).
 
The program components of the Get REAL! program address the multiple facets of student engagement through a literacy program, character building, educational enhancements and community service opportunities. Facilitators and mentors work together to establish relationships with at-risk students and provide opportunities for educational enhancement trips and community services. The program components and activities of the Councils will be discussed in this section.

Literacy Component:

The reading portion of the Get REAL! program uses the See Girls Read! curriculum, and girls read at least five books during the 30-session program. As part of the Girl Scout process, students are given input about what books they wish to read. Mentors facilitate discussion about the books the girls are reading, and participants read and write in their journal. The group discussions and writing activities help increase emotional and cognitive engagement in the students. Periodically the girls are encouraged to share their journals with their mentor and the mentor will respond to them. Journaling gives girls additional writing experience and helps establish connections with their mentor. 

```{r}
book_1 <- lapply(books, factor, levels=c("Don't Know/Prefer Not to say","Strongly Disagree", "Disagree", "Disagree a little","Agree a little", "Agree", "Strongly Agree" ), ordered=TRUE)


table(book_1)

```


### Character Building/Life Skills:

Relationships and connections with peers and teachers plays a critical role in academic engagement for students (Fredricks et al., 2011). All Girl Scout councils utilize the modules "Being a Girl", "Friendship" and "Body Image" from the Girls Circle curriculum. The modules focus on self-esteem, social development and interpersonal relationships to help the students solidify relationships with themselves, peers, and teachers.

### Educational Enhancements:

Girls in the Get REAL! program participate in educational enhancements that consists of out-of-school learning experiences which  include camp visits, legislative day and half-day trips to local educational facilities.  Examples of the educational enhancement opportunities offered to the students in the program this year include legislative days, educational programs at theme parks, financial literacy workshops, summer camp, college tours, and a STOMP performance.

At legislative days student attended workshops on public speaking, self-esteem and advocacy and opportunity to meet local representatives.  Students from Tropic Council had the opportunity to attend Disney Youth Education Series that provides students with a hands on educational adventure. Students from Girl Scouts of West Central Florida took a Behind the Scene literacy trip to Universal Studios where they learned the science behind creating a theme park. 

### Community Care Projects


An important part of Girl Scouting is community care projects to help girls identify what they can do to help their community. Each program group develops their own projects that is specific to their community.  Students from the Gateway Council created "Reading Gardens" at community and senior centers. Part of the project was to clean up an area and provide a small table and two chairs for people to sit and read a book.  No other council provided any reports on their community care projects.
