---
title: "Q1grades_dm"
author: "Kevin Gilds"
date: "December 5, 2015"
output: html_document
---

### Intro this section needs to be updated. 

```{r}

#### Load the Libraries
library(dplyr)
library(reshape2)
library(pander)


### Locate file to read from
setwd("C:/Users/kevin/Dropbox/GetReal/Data/2015-2016/December 2015")

### read the data into R
grades <- read.csv('grades_q1_12182015.csv', skip = 1, na.strings="")


```

```{r}

### Demo Variables
colnames (grades) [7] <- "council"
colnames (grades) [8] <- "girlCode"
colnames (grades) [9] <- "schoolName"
colnames (grades) [10] <- "dateEnrolled"

#### Behavioral Variables
colnames (grades) [12] <- "unexcusedAbs"
colnames (grades) [13] <- "excusedAbs"
colnames (grades) [14] <- "inSchoolSusp"
colnames (grades) [15] <- "outofSchoolSusp"
colnames (grades) [16] <- "expelled"


### Reading Courses

colnames (grades) [19] <- "mjIntensRead"
colnames (grades) [20] <- "mjIntenseReadCareerPlaning"
colnames (grades) [21] <- "mjRead1"
colnames (grades) [22] <- "mjRead1Adv"
colnames (grades) [23] <- "mjRead2"
colnames (grades) [24] <- "mjRead2Adv"
colnames (grades) [25] <- "mjRead3"
colnames (grades) [26] <- "mjRead3Adv"
colnames (grades) [27] <- "mjDelaESOLRead"
colnames (grades) [28] <- "readFree1"
colnames (grades) [29] <- "readFree2"


### Lang Arts Courses

colnames (grades) [31] <- "mjLangArts1ESOL"
colnames (grades) [32] <- "mjLangArts2ESOL"
colnames (grades) [33] <- "mjLangArts3ESOL"
colnames (grades) [34] <- "mjDevelpmentalESOL"


colnames (grades) [35] <- "mjLangArts1"
colnames (grades) [36] <-"mjlangsArts1Adv"
colnames (grades) [37] <-"mjLangArts2"
colnames (grades) [38] <- "mjLangArts2Adv" 
colnames (grades) [39] <- "mjLangArts3"
colnames (grades) [40] <- "mjLangArts3Adv"


colnames (grades) [41] <- "mjEng2Cambsec2"
colnames (grades) [42] <- "mjIBLangArts1"
colnames (grades) [43] <- "mjEng2CamSec1"
colnames (grades) [44] <- "mjIBLangArts3"
colnames (grades) [45] <- "mjIBLangArts2"
colnames (grades) [46] <- "mjEng3Cambsec3"


colnames (grades) [47] <- "mjIntensLangArts"
colnames (grades) [48] <- "freeLang1"
colnames (grades) [49] <- "freeLang2"
colnames (grades) [50] <- "mjLangTran"


```


```{r}
################Finished Data Entry####################################33

### Eliminate uncompleted data entry
gradesq1 <- filter(grades, Finished == 1)


```

```{r}

#######################Fix Factors ###################################

### Make all girCode to upper case for matching
gradesq1$girlCode <- toupper(gradesq1$girlCode)

### Make sure R does not make this a factor variable
gradesq1$council <- as.character(gradesq1$council)

### Make sure R does not make this a factor variable 
gradesq1$girlCode <- as.character(gradesq1$girlCode)



```


```{r}

##############################Subset Duplicate Values##################
### find the duplicates
q1Dupes <-duplicated(gradesq1$girlCode) | duplicated(gradesq1$girlCode, fromLast=TRUE)

### Subset the duplicates
q1Dupes <-gradesq1[q1Dupes, ]


```

```{r}
##################Duplicates#########################################

### Find the unique girlCodes and subset them
gradesUnique <- gradesq1 [!(duplicated(gradesq1$girlCode) | duplicated(gradesq1$girlCode, fromLast = TRUE)), ]



```

### Save data object Grades to RDS for status report

```{r}

### Save in relevant data file
setwd("C:/Users/kevin/Dropbox/GetReal/Data/2015-2016/December 2015")

### RDS file for status report. 
saveRDS(gradesUnique, "grades_q1_12132015.rds")

```


```{r}
###############Reading Clean Up###############################################################

### Select data of interest
q1Reading <- select(gradesUnique, 7,8, 19:27)




### Put the data in the shape you want it. 
mq1Reading <- melt(q1Reading, id.vars=c("girlCode", "council"))


####################change column names
colnames (mq1Reading) [4] <-"readingGrade"
colnames (mq1Reading) [3] <- "readingCourses"


### Omit the blanks 
mq1Reading <-na.omit(mq1Reading)


###Need to rid grades of plus signs
class(mq1Reading$readingGrade)

southeast <- filter(mq1Reading, council == "Girl Scouts of Southeast Council")

southeast_course <- filter(mq1Reading, readingCourses == "mjIntensRead")





mq1Reading$readingGrade <-sub("B+", "B", fixed=TRUE, mq1Reading$readingGrade)

mq1Reading$readingGrade <-sub("C+", "C", fixed=TRUE, mq1Reading$readingGrade)

mq1Reading$readingGrade <-sub("D+", "C", fixed=TRUE, mq1Reading$readingGrade)

mq1Reading$readingGrade <-sub("C ", "C", fixed=TRUE, mq1Reading$readingGrade)

mq1Reading$readingGrade <-sub("c ", "C", fixed=TRUE, mq1Reading$readingGrade)







###Change grades to all upper case to match
mq1Reading$readingGrade <- toupper(mq1Reading$readingGrade)

###change reading grade to factor 
mq1Reading$readingGrade <-as.factor(mq1Reading$readingGrade)

summary(mq1Reading$readingGrade)


### Create table to sneak peak at the data.    
table(mq1Reading$readingCourses,mq1Reading$readingGrade)

with(mq1Reading, table(council,readingGrade))

### Check the levels
levels(mq1Reading$readingGrade)

names(mq1Reading)


```


#### Check for Read Free Data Entry

```{r}

q1free_read <- select(gradesUnique, 7,8, 28:29)

names(q1free_read)



```

```{r}


```



### Save Reading to RDS File
```{r}

### I want the data to go here. 
setwd("C:/Users/kevin/Dropbox/GetReal/Data/2015-2016/December 2015")

### Save the object for analysis in another script
saveRDS(mq1Reading, file = "reading_q1_12132015.rds")

```


#### Language Arts Courses

```{r}

### Select the data of interest
q1LangArts <- select(gradesUnique, 7,8, 31:47, 50)


### Put the data in the shape I want it in
mq1_lang <- melt(q1LangArts, id.vars=c("girlCode", "council"))



####################change column names
colnames (mq1_lang) [4] <-"langGrade"
colnames (mq1_lang) [3] <- "langCourses"


### Get rid of blanks
q1_lang <- na.omit(mq1_lang)


###Change grades to all upper case to match
mq1_lang$langGrade <- toupper(mq1_lang$langGrade)

###change reading grade to factor 
mq1_lang$langGrade <-as.factor(mq1_lang$langGrade)

### Create tables to sneak at the data
table(mq1_lang$langCourses,mq1_lang$langGrade)
lang_courses <- table(mq1_lang$langCourses) #for output







```

### Free Language Arts
```{r}

### Review Free Text Entry
free_lang <- select(gradesUnique, 7,8, 48,49)


### Test to determine if there is any data in those columns
table(free_lang$free_lang1)
table(free_lang$free_lang2)

```

### Lang Arts Save to RDS

```{r}
### Ensure the dat goes to the correct directory
setwd("C:/Users/kevin/Dropbox/GetReal/Data/2015-2016/December 2015")

### Save the object for analysis script or file
saveRDS(mq1_lang, "langQ1_12132015.rds")

```



### Unexcused Absences

```{r}

### Select the data of interest
unexcused <- select(gradesUnique,7,8, 12)


### Create table to view the summary
unexcused_tbl <- table(unexcused$unexcusedAbs)

### Print the table
unexcused_tbl

```

### Excused Absences

```{r}
### Select the data of interest
excused <- select(gradesUnique, 7, 8, 13)


### Create table to view the data
excused_tbl <- with(excused,table(excusedAbs))

### View the output
excused_tbl

```


### Total Absences

```{r}


#### Merge unexcused and excused objects
total_abs <- inner_join(unexcused, excused, by = "girlCode", Copy=FALSE)


### Sum up the two columns to get a total 
total_abs$sum_abs <-total_abs$unexcusedAbs + total_abs$excusedAbs

### Create table to view the data
total_abs_tbl <- with(total_abs, table(sum_abs))

### See the table output
total_abs_tbl

```


### Total Suspensions to RDS

```{r}

### Set to save data to correct file folder
setwd("C:/Users/kevin/Dropbox/GetReal/Data/2015-2016/December 2015")

### Save to read data for analysis script or file
saveRDS(total_abs, "total_Absences_12132015.rds")

```


### In School Suspensions

```{r}

### Look at data of interest
in_school <- select(gradesUnique, 7, 8, 14)


### Create table to look at data
in_school_tbl <- with(in_school, table(inSchoolSusp))

### View table
in_school_tbl


```

### Out of School Suspenions

```{r}

out_school <- select(gradesUnique, 7, 8, 15)

out_school_tbl <- with(out_school, table(outofSchoolSusp))

out_school_tbl

```


### Total suspensions

```{r}

susp_total <- inner_join(in_school, out_school, by = "girlCode", copy=FALSE)

head(susp_total)

susp_total$susp_sum <- in_school$inSchoolSusp + out_school$outofSchoolSusp

head(susp_total)

susp_total_tbl <- with(susp_total,table(susp_sum))

susp_total_tbl



```

### Total Suspensions to RDS

```{r}

### Save file to correct file folder
setwd("C:/Users/kevin/Dropbox/GetReal/Data/2015-2016/December 2015")

### Save to RDS for analysis script to read
saveRDS(susp_total, "total_susp_12132015.rds")

```

### Expelled

```{r}

### Select the variable of interest
expelled <- select(gradesUnique, 7,8,16)

### Create table to view the summary
expelled_tbl <-with(expelled,table(expelled))

### Print the table
expelled_tbl

```

### Expelled Object to RDS

```{r}
### Save object to correct desintation file folder
setwd("C:/Users/kevin/Dropbox/GetReal/Data/2015-2016/December 2015")

### Save to RDS for analytics script. 
saveRDS(expelled, "expelled_12132015.rds")

```

