---
title: "Q2_grades_dm"
author: "Kevin Gilds"
date: '`r Sys.Date()`'
output: html_document
---

### Intro this section needs to be updated. 

```{r}

#### Load the Libraries
library(dplyr)
library(reshape2)
library(pander)
library(sqldf)


### Locate file to read from
setwd("C:/Users/kevin/Dropbox/GetReal/Data/2015-2016/March 2016")


### read the data into R
q2_grades <- read.csv('q2_grades03122016.csv', skip = 1, na.strings="")


```

```{r}

### Demo Variables
colnames (q2_grades) [7] <- "council"
colnames (q2_grades) [8] <- "girlCode"
colnames (q2_grades) [9] <- "schoolName"
colnames (q2_grades) [10] <- "dateEnrolled"

#### Behavioral Variables
colnames (q2_grades) [12] <- "unexcusedAbs"
colnames (q2_grades) [13] <- "excusedAbs"
colnames (q2_grades) [14] <- "inSchoolSusp"
colnames (q2_grades) [15] <- "outofSchoolSusp"
colnames (q2_grades) [16] <- "expelled"


### Reading Courses

colnames (q2_grades) [19] <- "mjIntensRead_quarter"
colnames (q2_grades) [20] <- "mjIntensRead_semester"

colnames (q2_grades) [21] <- "mjIntenseReadCareerPlaning_quarter"
colnames (q2_grades) [22] <- "mjIntenseReadCareerPlaning_semester"


colnames (q2_grades) [23] <- "mjRead1_quarter"
colnames (q2_grades) [24] <- "mjRead1_semester"


colnames (q2_grades) [25] <- "mjRead1Adv_quarter"
colnames (q2_grades) [26] <- "mjRead1Adv_semester"
 

colnames (q2_grades) [27] <- "mjRead2_quarter"
colnames (q2_grades) [28] <- "mjRead2_semester"


colnames (q2_grades) [29] <- "mjRead2Adv_quarter"
colnames (q2_grades) [30] <- "mjRead2Adv_semester"



colnames (q2_grades) [31] <- "mjRead3_quarter"
colnames (q2_grades) [32] <- "mjRead3_semester"



colnames (q2_grades) [33] <- "mjRead3Adv_quarter"
colnames (q2_grades) [34] <- "mjRead3Adv_semester"



colnames (q2_grades) [35] <- "mjDelaESOLRead_quarter"
colnames (q2_grades) [36] <- "mjDelaESOLRead_semester"



colnames (q2_grades) [37] <- "readFree1_quarter"
colnames (q2_grades) [38] <- "readFree2_quarter"


### Lang Arts Courses

colnames (q2_grades) [41] <- "mjLangArts1ESOL_quarter"
colnames (q2_grades) [42] <- "mjLangArts1ESOL_semester"



colnames (q2_grades) [43] <- "mjLangArts2ESOL_quarter"
colnames (q2_grades) [44] <- "mjLangArts2ESOL_semester"



colnames (q2_grades) [45] <- "mjLangArts3ESOL_quarter"
colnames (q2_grades) [46] <- "mjLangArts3ESOL_semester"



colnames (q2_grades) [47] <- "mjDevelpmentalESOL_quarter"
colnames (q2_grades) [48] <- "mjDevelpmentalESOL_semester"


colnames (q2_grades) [49] <- "mjLangArts1_quarter"
colnames (q2_grades) [50] <- "mjLangArts1_semester"



colnames (q2_grades) [51] <-"mjlangsArts1Adv_quarter"
colnames (q2_grades) [52] <-"mjlangsArts1Adv_semester"



colnames (q2_grades) [53] <-"mjLangArts2_quarter"
colnames (q2_grades) [54] <-"mjLangArts2_semester"



colnames (q2_grades) [55] <- "mjLangArts2Adv_quarter" 
colnames (q2_grades) [56] <- "mjLangArts2Adv_semester" 



colnames (q2_grades) [57] <- "mjLangArts3_quarter"
colnames (q2_grades) [58] <- "mjLangArts3_semester"


colnames (q2_grades) [59] <- "mjLangArts3Adv_quarter"
colnames (q2_grades) [60] <- "mjLangArts3Adv_semester"



colnames (q2_grades) [61] <- "mjEng2Cambsec2_quarter"
colnames (q2_grades) [62] <- "mjEng2Cambsec2_semester"



colnames (q2_grades) [63] <- "mjIBLangArts1_quarter"
colnames (q2_grades) [64] <- "mjIBLangArts1_semeser"


colnames (q2_grades) [65] <- "mjEng2CamSec1_quarter"
colnames (q2_grades) [66] <- "mjEng2CamSec1_semester"



colnames (q2_grades) [67] <- "mjIBLangArts3_quarter"
colnames (q2_grades) [68] <- "mjIBLangArts3_semester"



colnames (q2_grades) [69] <- "mjIBLangArts2_quarter"
colnames (q2_grades) [70] <- "mjIBLangArts2_semester"



colnames (q2_grades) [71] <- "mjEng3Cambsec3_quarter"
colnames (q2_grades) [72] <- "mjEng3Cambsec3_semester"



colnames (q2_grades) [73] <- "mjIntensLangArts_quarter"
colnames (q2_grades) [74] <- "mjIntensLangArts_semester"



colnames (q2_grades) [75] <- "freeLang1_quarter"
colnames (q2_grades) [76] <- "freeLang2_semester"

colnames (q2_grades) [78] <- "mjLangTran_quarter"
colnames (q2_grades) [79] <- "mjLangTran_semester"




```


```{r}
################Finished Data Entry####################################33

### Eliminate uncompleted data entry
gradesq2 <- filter(q2_grades, Finished == 1)


```

```{r}

#######################Fix Factors ###################################

### Make all girCode to upper case for matching
gradesq2$girlCode <- toupper(gradesq2$girlCode)

### Make sure R does not make this a factor variable
gradesq2$council <- as.character(gradesq2$council)

### Make sure R does not make this a factor variable 
gradesq2$girlCode <- as.character(gradesq2$girlCode)



```




```{r}
##################Duplicates#########################################

### Find the unique girlCodes and subset them
q2_gradesUnique <- gradesq2 [!(duplicated(gradesq2$girlCode) | duplicated(gradesq2$girlCode, fromLast = TRUE)), ]

dim(q2_gradesUnique)



```

```{r}


##############################Subset Duplicate Values##################
### find the duplicates
q2Dupes <-duplicated(gradesq2$girlCode) | duplicated(gradesq2$girlCode, fromLast=TRUE)

### Subset the duplicates
q2Dupes <-gradesq2[q2Dupes, ]


dim(q2Dupes)



```




```{r}

### Change council names to be consistent wiht how they displayed with the surveys
q2_gradesUnique$council <-sub("Girl Scouts of the Gateway Council", "Gateway Council", fixed=TRUE, q2_gradesUnique$council)

q2_gradesUnique$council <-sub("Girl Scouts of Citrus Council", "Citrus Council", fixed=TRUE, q2_gradesUnique$council)

q2_gradesUnique$council <-sub("Girl Scouts of Southeast Florida", "Southeast Council", fixed=TRUE, q2_gradesUnique$council)

q2_gradesUnique$council <-sub("Girl Scout Council of Tropical Florida", "Tropical Council", fixed = TRUE, q2_gradesUnique$council)

q2_gradesUnique$council <-sub("Girl Scouts of West Central Florida", "West Central Council", fixed = TRUE, q2_gradesUnique$council)

q2_gradesUnique$council <-sub("Girl Scout Council of the Panhandle", "Panhandle Council", fixed = TRUE, q2_gradesUnique$council)



```






```{r}
###############Reading Clean Up###############################################################

### Select data of interest
q2Reading <- select(q2_gradesUnique, 7,8, 19:38)




### Put the data in the shape you want it. 
mq2Reading <- melt(q2Reading, id.vars=c("girlCode", "council"))


####################change column names
colnames (mq2Reading) [4] <-"readingGrade"
colnames (mq2Reading) [3] <- "readingCourses"


### Omit the blanks 
mq2Reading <-na.omit(mq2Reading)




####Adjust Grades with a plus sign and fix spacing issues

mq2Reading$readingGrade <-sub("B+", "B", fixed=TRUE, mq2Reading$readingGrade)

mq2Reading$readingGrade <-sub("C+", "C", fixed=TRUE, mq2Reading$readingGrade)

mq2Reading$readingGrade <-sub("D+", "D", fixed=TRUE, mq2Reading$readingGrade)

mq2Reading$readingGrade <-sub("C ", "C", fixed=TRUE, mq2Reading$readingGrade)

mq2Reading$readingGrade <-sub("c ", "C", fixed=TRUE, mq2Reading$readingGrade)

mq2Reading$readingGrade <-sub("0", "F", fixed=TRUE, mq2Reading$readingGrade)

mq2Reading$readingGrade <-sub("3", "B", fixed=TRUE, mq2Reading$readingGrade)



###Change grades to all upper case to match
mq2Reading$readingGrade <- toupper(mq2Reading$readingGrade)

###change reading grade to factor 
mq2Reading$readingGrade <-as.factor(mq2Reading$readingGrade)

summary(mq2Reading$readingGrade)


### Create table to sneak peak at the data.    
table(mq2Reading$readingCourses,mq2Reading$readingGrade)

with(mq2Reading, table(council,readingGrade))

### Check the levels
levels(mq2Reading$readingGrade)

names(mq2Reading)


```


#### Check for Read Free Data Entry

```{r}

q2free_read <- select(q2_gradesUnique, 7,8, 37:38)

names(q2free_read)



```







#### Language Arts Courses

```{r}

### Select the data of interest
q2LangArts <- select(q2_gradesUnique, 7,8, 41:74, 78:79 )


### Put the data in the shape I want it in
mq2_lang <- melt(q2LangArts, id.vars=c("girlCode", "council"))



####################change column names
colnames (mq2_lang) [4] <-"langGrade"
colnames (mq2_lang) [3] <- "langCourses"


### Get rid of blanks
mq2_lang <- na.omit(mq2_lang)


###Change grades to all upper case to match
mq2_lang$langGrade <- toupper(mq2_lang$langGrade)

###change reading grade to factor 
mq2_lang$langGrade <-as.factor(mq2_lang$langGrade)

####Adjust Grades with a plus sign and fix spacing issues

mq2_lang$langGrade <-sub("B+", "B", fixed=TRUE, mq2_lang$langGrade)

mq2_lang$langGrade <-sub("C+", "C", fixed=TRUE, mq2_lang$langGrade)

mq2_lang$langGrade <-sub("A ", "A", fixed=TRUE, mq2_lang$langGrade)

mq2_lang$langGrade <-sub("2", "B", fixed=TRUE, mq2_lang$langGrade)

mq2_lang$langGrade <-sub("D+", "D", fixed=TRUE, mq2_lang$langGrade)



### Create tables to sneak at the data
table(mq2_lang$langCourses,mq2_lang$langGrade)
lang_courses <- table(mq2_lang$langCourses) #for output







```

### Free Language Arts
```{r}

### Review Free Text Entry
q2_free_lang <- select(q2_gradesUnique, 7,8, 75:76)


### Test to determine if there is any data in those columns
table(q2_free_lang$free_lang1_quarter)
table(q2_free_lang$free_lang2_semester)

```


###Find both quarter and semester grades and finalize semester grade

```{r}

##################Duplicates#########################################

### Find the unique girlCodes with just one grade 
mq2_lang_ok <- mq2_lang [!(duplicated(mq2_lang$girlCode) | duplicated(mq2_lang$girlCode, fromLast = TRUE)), ]

dim(mq2_lang_ok)


### Find the girl codes with multiple grades

##############################Subset Duplicate Values##################
### find the duplicates
q2lang_dupes <-duplicated(mq2_lang$girlCode) | duplicated(mq2_lang$girlCode, fromLast=TRUE)

### Subset the duplicates
q2lang_dupes <- mq2_lang[q2lang_dupes, ]


dim(q2lang_dupes)


```

#### Find and subset the Semester Grades in duplicate version 

```{r}
semester <- q2lang_dupes[grep("_semester", q2lang_dupes$langCourses, ignore.case = TRUE),]

dim(semester)

head(semester)
```


#### Bind the Language Arts Courses together

```{r}
mq2_lang_all <- rbind(mq2_lang_ok, semester)



dim(mq2_lang_all)

```


Calculate Grade Points
```{r}

lang_pts2 <- numeric(0)

for(i in mq2_lang_all$langGrade){
   
     lang_pts2<- c(lang_pts2,switch(i, "A" =4, "B"=3, "C"=2, "D"=1, "F"=0, "I"=0))
    
     lang_pts2

    
}

mq2_lang_all <- cbind(mq2_lang_all, lang_pts2)

head(mq2_lang_all)

```



### Unexcused Absences

```{r}

### Select the data of interest
q2_unexcused <- select(q2_gradesUnique,7,8, 12)


### Create table to view the summary
q2_unexcused_tbl <- table(q2_unexcused$unexcusedAbs)

### Print the table
q2_unexcused_tbl

```

### Excused Absences

```{r}
### Select the data of interest
q2_excused <- select(q2_gradesUnique, 7, 8, 13)


### Create table to view the data
q2_excused_tbl <- with(q2_excused,table(excusedAbs))

### View the output
q2_excused_tbl

```


### Total Absences

```{r}


#### Merge unexcused and excused objects
q2_total_abs <- inner_join(q2_unexcused, q2_excused, by = "girlCode", Copy=FALSE)


### Sum up the two columns to get a total 
q2_total_abs$sum_abs <-q2_total_abs$unexcusedAbs + q2_total_abs$excusedAbs

### Create table to view the data
q2_total_abs_tbl <- with(q2_total_abs, table(sum_abs))

### See the table output
q2_total_abs_tbl

```




### In School Suspensions

```{r}

### Look at data of interest
q2_in_school <- select(q2_gradesUnique, 7, 8, 14)


### Create table to look at data
q2_in_school_tbl <- with(q2_in_school, table(inSchoolSusp))

### View table
q2_in_school_tbl


```

### Out of School Suspenions

```{r}

q2_out_school <- select(q2_gradesUnique, 7, 8, 15)

q2_out_school_tbl <- with(q2_out_school, table(outofSchoolSusp))

q2_out_school_tbl

```


### Total suspensions

```{r}

q2_susp_total <- inner_join(q2_in_school, q2_out_school, by = "girlCode", copy=FALSE)

head(q2_susp_total)

q2_susp_total$susp_sum <- q2_in_school$inSchoolSusp + q2_out_school$outofSchoolSusp

head(q2_susp_total)

q2_susp_total_tbl <- with(q2_susp_total,table(susp_sum))

q2_susp_total_tbl



```


### Expelled

```{r}

### Select the variable of interest
q2_expelled <- select(q2_gradesUnique, 7,8,16)

dim(q2_expelled)

head(q2_expelled)

### Create table to view the summary
q2_expelled_tbl <-with(q2_expelled,table(expelled))

### Print the table
q2_expelled_tbl

```



### Merge Behavior Data

```{r}

abs_susp <- full_join(q2_total_abs, q2_susp_total)

dim(abs_susp)


behavior_data <- full_join(abs_susp, q2_expelled)


behavior_data <- select(behavior_data,council, girlCode, sum_abs, susp_sum, expelled)

colnames (behavior_data) [1] <- "council"
colnames (behavior_data) [3] <- "total_absences"
colnames (behavior_data) [4] <- "total_suspensions"


head(behavior_data)




```





### Merge Grade Data

```{r}

q2_lang_read <- full_join(mq2_lang, mq2Reading)
dim(q2_lang_read)

head(q2_lang_read)

q2_lang_read <- select(q2_lang_read, council, girlCode, langCourses, langGrade, readingCourses, readingGrade)


colnames (q2_lang_read) [1] <- "council"

head(q2_lang_read)



```

### Merge all
```{r}

q2_academic_data <- full_join(q2_lang_read, behavior_data, by="girlCode")

dim(q2_academic_data)

head(q2_academic_data)

q2_academic_data <- select(q2_academic_data, council.x, girlCode, langCourses, langGrade, readingCourses,readingGrade,total_absences, total_suspensions, expelled)

colnames (q2_academic_data) [1] <- "council"


head(q2_academic_data)
```





```{r}
### Save data objects to Sqlite

setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

dbWriteTable(conn =getReal_2016db, name = "Q2_academic_data", value = q2_academic_data, row.names = FALSE, overwrite = TRUE)



dbWriteTable(conn = getReal_2016db, name = "Q2_duplicates", value = q2Dupes, row.names=FALSE, overwrite=TRUE)


### Write Q1 Expelled data to sqlite database
dbWriteTable(conn = getReal_2016db, name = "Q2_expelled", value = q2_expelled, row.names=FALSE, overwrite=TRUE)


### Write Q1 Suspsenion data to sqlite database
dbWriteTable(conn = getReal_2016db, name = "Q2_Suspensions", value = q2_susp_total, row.names=FALSE, overwrite=TRUE)

### Write Q1 Absences to sqlite datase
dbWriteTable(conn = getReal_2016db, name = "Q2_Absences", value = q2_total_abs, row.names=FALSE, overwrite=TRUE)

### Write Q1 Lang Arts grade to sqlite database
dbWriteTable(conn = getReal_2016db, name = "Q2_lang", value = mq2_lang, row.names=FALSE, overwrite=TRUE)

### Write Q1 Reading grades to sqlite database
dbWriteTable(conn = getReal_2016db, name = "Q2_reading", value = mq2Reading, row.names=FALSE, overwrite=TRUE)

```



