---
title: "q4_Grades"
author: "Kevin Gilds, MPA"
date: "June 30, 2016"
output: html_document
---

 Intro: 

## Import Libaries needed. 

```{r "q4_loadlibaries"}

#### Load the Libraries
library(dplyr)
library(reshape2)
library(pander)
library(sqldf)


### Locate file to read from
setwd("C:/Users/kevin/Dropbox/GetReal/Data/2015-2016/July 2016")


### read the data into R
q4_grades <- read.csv('grades_q4_07172016.csv', skip = 1, na.strings="")



names(q4_grades)

```

## Make columna names easier to read
```{r "q4_changcolnames"}

### Demo Variables
colnames (q4_grades) [7] <- "council"
colnames (q4_grades) [8] <- "girlCode"
colnames (q4_grades) [9] <- "schoolName"
colnames (q4_grades) [10] <- "dateEnrolled"

#### Behavioral Variables
colnames (q4_grades) [12] <- "unexcusedAbs"
colnames (q4_grades) [13] <- "excusedAbs"
colnames (q4_grades) [14] <- "inSchoolSusp"
colnames (q4_grades) [15] <- "outofSchoolSusp"
colnames (q4_grades) [16] <- "expelled"
colnames (q4_grades) [17] <- "promoted"


### Reading Courses

colnames (q4_grades) [20] <- "mjIntensRead_quarter"
colnames (q4_grades) [21] <- "mjIntensRead_semester"

colnames (q4_grades) [22] <- "mjIntenseReadCareerPlaning_quarter"
colnames (q4_grades) [23] <- "mjIntenseReadCareerPlaning_semester"


colnames (q4_grades) [24] <- "mjRead1_quarter"
colnames (q4_grades) [25] <- "mjRead1_semester"


colnames (q4_grades) [26] <- "mjRead1Adv_quarter"
colnames (q4_grades) [27] <- "mjRead1Adv_semester"
 

colnames (q4_grades) [28] <- "mjRead2_quarter"
colnames (q4_grades) [29] <- "mjRead2_semester"


colnames (q4_grades) [30] <- "mjRead2Adv_quarter"
colnames (q4_grades) [31] <- "mjRead2Adv_semester"



colnames (q4_grades) [32] <- "mjRead3_quarter"
colnames (q4_grades) [33] <- "mjRead3_semester"



colnames (q4_grades) [34] <- "mjRead3Adv_quarter"
colnames (q4_grades) [35] <- "mjRead3Adv_semester"



colnames (q4_grades) [36] <- "mjDelaESOLRead_quarter"
colnames (q4_grades) [37] <- "mjDelaESOLRead_semester"



colnames (q4_grades) [38] <- "readFree1_quarter"
colnames (q4_grades) [39] <- "readFree2_semester"
colnames (q4_grades) [40] <- "reading_course"


### Lang Arts Courses

colnames (q4_grades) [42] <- "mjLangArts1ESOL_quarter"
colnames (q4_grades) [43] <- "mjLangArts1ESOL_semester"



colnames (q4_grades) [44] <- "mjLangArts2ESOL_quarter"
colnames (q4_grades) [45] <- "mjLangArts2ESOL_semester"



colnames (q4_grades) [46] <- "mjLangArts3ESOL_quarter"
colnames (q4_grades) [47] <- "mjLangArts3ESOL_semester"



colnames (q4_grades) [48] <- "mjDevelpmentalESOL_quarter"
colnames (q4_grades) [49] <- "mjDevelpmentalESOL_semester"


colnames (q4_grades) [50] <- "mjLangArts1_quarter"
colnames (q4_grades) [51] <- "mjLangArts1_semester"



colnames (q4_grades) [52] <-"mjlangsArts1Adv_quarter"
colnames (q4_grades) [53] <-"mjlangsArts1Adv_semester"



colnames (q4_grades) [54] <-"mjLangArts2_quarter"
colnames (q4_grades) [55] <-"mjLangArts2_semester"



colnames (q4_grades) [56] <- "mjLangArts2Adv_quarter" 
colnames (q4_grades) [57] <- "mjLangArts2Adv_semester" 



colnames (q4_grades) [58] <- "mjLangArts3_quarter"
colnames (q4_grades) [59] <- "mjLangArts3_semester"


colnames (q4_grades) [60] <- "mjLangArts3Adv_quarter"
colnames (q4_grades) [61] <- "mjLangArts3Adv_semester"



colnames (q4_grades) [62] <- "mjEng2Cambsec2_quarter"
colnames (q4_grades) [63] <- "mjEng2Cambsec2_semester"



colnames (q4_grades) [64] <- "mjIBLangArts1_quarter"
colnames (q4_grades) [65] <- "mjIBLangArts1_semeser"


colnames (q4_grades) [66] <- "mjEng2CamSec1_quarter"
colnames (q4_grades) [67] <- "mjEng2CamSec1_semester"



colnames (q4_grades) [68] <- "mjIBLangArts3_quarter"
colnames (q4_grades) [69] <- "mjIBLangArts3_semester"



colnames (q4_grades) [70] <- "mjIBLangArts2_quarter"
colnames (q4_grades) [71] <- "mjIBLangArts2_semester"



colnames (q4_grades) [72] <- "mjEng3Cambsec3_quarter"
colnames (q4_grades) [73] <- "mjEng3Cambsec3_semester"



colnames (q4_grades) [74] <- "mjIntensLangArts_quarter"
colnames (q4_grades) [75] <- "mjIntensLangArts_semester"



colnames (q4_grades) [76] <- "freeLang1_quarter"
colnames (q4_grades) [77] <- "freeLang2_semester"
colnames (q4_grades) [78] <- "course_text"

colnames (q4_grades) [79] <- "mjLangTran_quarter"
colnames (q4_grades) [80] <- "mjLangTran_semester"


names(q4_grades)

```

## Subset completed data entry
```{r "q4_completed"}
################Finished Data Entry####################################33

### Eliminate uncompleted data entry
gradesq4 <- filter(q4_grades, Finished == 1)

names(q4_grades)
```


```{r "q4councilname"}
## Update council variable names to match other data sources


### Change council names to be consistent wiht how they displayed with the surveys
gradesq4$council <-sub("Girl Scouts of the Gateway Council", "Gateway Council", fixed=TRUE, gradesq4$council)

gradesq4$council <-sub("Girl Scouts of Citrus Council", "Citrus Council", fixed=TRUE, gradesq4$council)

gradesq4$council <-sub("Girl Scouts of Southeast Florida", "Southeast Council", fixed=TRUE, gradesq4$council)

gradesq4$council <-sub("Girl Scout Council of Tropical Florida", "Tropical Council", fixed = TRUE, gradesq4$council)

gradesq4$council <-sub("Girl Scouts of West Central Florida", "West Central Council", fixed = TRUE, gradesq4$council)

gradesq4$council <-sub("Girl Scout Council of the Panhandle", "Panhandle Council", fixed = TRUE, gradesq4$council)



```



## Update factors
```{r"q4factors"}

#######################Fix Factors ###################################

### Make all girCode to upper case for matching
gradesq4$girlCode <- toupper(gradesq4$girlCode)

### Make sure R does not make this a factor variable
gradesq4$council <- as.character(gradesq4$council)

### Make sure R does not make this a factor variable 
gradesq4$girlCode <- as.character(gradesq4$girlCode)



```



## Deal with duplicates
```{r "q4_duplicates1"} 
##################Duplicates#########################################

### Find the unique girlCodes and subset them
q4_gradesUnique <- gradesq4 [!(duplicated(gradesq4$girlCode) | duplicated(gradesq4$girlCode, fromLast = TRUE)), ]

dim(q4_gradesUnique)



```
### Subset duplicate values
```{r "q4_duplicates"}


##############################Subset Duplicate Values##################
### find the duplicates
q4Dupes <-duplicated(gradesq4$girlCode) | duplicated(gradesq4$girlCode, fromLast=TRUE)

### Subset the duplicates
q4Dupes <-gradesq4[q4Dupes, ]


dim(q4Dupes)



```



## Update council variable names to match other data sources
```{r "q4_councilnames"}

### Change council names to be consistent wiht how they displayed with the surveys
q4_gradesUnique$council <-sub("Girl Scouts of the Gateway Council", "Gateway Council", fixed=TRUE, q4_gradesUnique$council)

q4_gradesUnique$council <-sub("Girl Scouts of Citrus Council", "Citrus Council", fixed=TRUE, q4_gradesUnique$council)

q4_gradesUnique$council <-sub("Girl Scouts of Southeast Florida", "Southeast Council", fixed=TRUE, q4_gradesUnique$council)

q4_gradesUnique$council <-sub("Girl Scout Council of Tropical Florida", "Tropical Council", fixed = TRUE, q4_gradesUnique$council)

q4_gradesUnique$council <-sub("Girl Scouts of West Central Florida", "West Central Council", fixed = TRUE, q4_gradesUnique$council)

q4_gradesUnique$council <-sub("Girl Scout Council of the Panhandle", "Panhandle Council", fixed = TRUE, q4_gradesUnique$council)



```

```{r "q4_freeread"}

q4free_read <- select(q4_gradesUnique, 7,8, 38:40)


q4free_read <- q4free_read[grep("read", q4free_read$reading_course, ignore.case = TRUE),]
#q4free_read1 <-subset(q4free_read, grepl("read", q4free_read$reading_course))

q4free_read <- q4free_read %>%
    select(1,2,4,5)




names(q4free_read)


q4free_read <- q4free_read %>%
    select(1:3)




q4free_read <- melt(q4free_read, id.vars=c("girlCode", "council"))

q4free_read <- slice(q4free_read, 3:10)

q4free_read

colnames(q4free_read) [3] <- "readingCourses"
colnames(q4free_read) [4] <- "readingGrade"

```




# Reading Grades Section--Split and Clean up
```{r "q4_readingmanagement"}
###############Reading Clean Up###############################################################

### Select data of interest
q4Reading <- select(q4_gradesUnique, 7,8, 20:37)


names(q4Reading)

#q4Reading <-rbind(q4Reading, q4free_read)

dim(q4Reading)

### Put the data in the shape you want it. 
mq4Reading <- melt(q4Reading, id.vars=c("girlCode", "council"))


####################change column names
colnames (mq4Reading) [4] <-"readingGrade"
colnames (mq4Reading) [3] <- "readingCourses"


mq4Reading <- rbind(mq4Reading, q4free_read)

### Omit the blanks 
mq4Reading <-na.omit(mq4Reading)

names(mq4Reading)


####Adjust Grades with a plus sign and fix spacing issues

mq4Reading$readingGrade <-sub("c+", "C", fixed=TRUE, mq4Reading$readingGrade)

mq4Reading$readingGrade <-sub("C+", "C", fixed=TRUE, mq4Reading$readingGrade)

mq4Reading$readingGrade <-sub("A+", "A", fixed=TRUE, mq4Reading$readingGrade)

mq4Reading$readingGrade <-sub("B+", "B", fixed=TRUE, mq4Reading$readingGrade)

mq4Reading$readingGrade <-sub("C+", "C", fixed=TRUE, mq4Reading$readingGrade)

mq4Reading$readingGrade <-sub("D+", "D", fixed=TRUE, mq4Reading$readingGrade)

mq4Reading$readingGrade <-sub("C ", "C", fixed=TRUE, mq4Reading$readingGrade)

mq4Reading$readingGrade <-sub("c ", "C", fixed=TRUE, mq4Reading$readingGrade)

mq4Reading$readingGrade <-sub("0", "F", fixed=TRUE, mq4Reading$readingGrade)

mq4Reading$readingGrade <-sub("3", "B", fixed=TRUE, mq4Reading$readingGrade)


###Change grades to all upper case to match
mq4Reading$readingGrade <- toupper(mq4Reading$readingGrade)

###change reading grade to factor 
mq4Reading$readingGrade <-as.factor(mq4Reading$readingGrade)

summary(mq4Reading$readingGrade)

### Create table to sneak peak at the data.    
table(mq4Reading$readingCourses,mq4Reading$readingGrade)

with(mq4Reading, table(council,readingGrade))

### Check the levels
levels(mq4Reading$readingGrade)




names(mq4Reading)

dim(mq4Reading)

test_mq4Reading<-distinct(mq4Reading, girlCode)

dim(test_mq4Reading)
```



## Check for duplicate reading grades(Quarter and Semester Grades)

```{r "q4_dupes_read"}

### Find the unique girlCodes with just one grade 
mq4_read_ok <- mq4Reading [!(duplicated(mq4Reading$girlCode) | duplicated(mq4Reading$girlCode, fromLast = TRUE)), ]

dim(mq4Reading)

##############################Subset Duplicate Values##################
### find the duplicates
q4reading_dupes <-duplicated(mq4Reading$girlCode) | duplicated(mq4Reading$girlCode, fromLast=TRUE)

### Subset the duplicates
q4reading_dupes <- mq4Reading[q4reading_dupes, ]


dim(q4reading_dupes)

head(q4reading_dupes)

```


### Find and subset the Semester Grades 

```{r "problem_chunk"}


read_quarter <- q4reading_dupes[grep("_quarter", q4reading_dupes$readingCourses, ignore.case = TRUE),]

dim(read_quarter)
head(read_quarter)

read_semester <- q4reading_dupes[grep("_semester", q4reading_dupes$readingCourses, ignore.case = TRUE),]

dim(read_semester)
head(read_semester)

```


### Anti Join to find extra grades--Cases where the student is in more than one reading course
```{r}

#extra_quarters <- anti_join(read_quarter, read_semester, by="girlCode")

#extra_quarters

#reading_pts_ex <- numeric(0)

#for(i in extra_quarters$readingGrade){
   
     #reading_pts_ex <- c(reading_pts_ex,switch(i, "A" =4, "B"=3, "C"=2, "D"=1, "F"=0, "I"=0))
    
     #reading_pts_ex

    
#}

#extra_quarters$readingCourses <- "ReadingCourseAvg"

#extra_quarters <- cbind(extra_quarters, reading_pts_ex)

#head(extra_quarters)


#extra_quarters <-with(extra_quarters, aggregate(reading_pts_ex,list(girlCode=girlCode, council=council, readingCourses=readingCourses, readingGrade=readingGrade),mean))

#extra_quarters


#colnames(extra_quarters) [5] <- "readingPts4"

#head(extra_quarters)

#extra_quarters

```


### Bind the semester grade back in 
```{r}

mq4_read_1 <- rbind(mq4_read_ok, read_semester)

dim(mq4_read_1)



```

### Reading Grade Points
```{r}

reading_pts4 <- numeric(0)  #assign variable

for(i in mq4_read_1$readingGrade){ #loop through grades
   
     reading_pts4 <- c(reading_pts4,switch(i, "A" =4, "B"=3, "C"=2, "D"=1, "F"=0, "I"=0)) #assign values base on grades
    
     reading_pts4

    
}

dim(mq4_read_1)

mq4_read_all <-cbind(mq4_read_1, reading_pts4) #bind data back in 




```

### Merge all the reading sets
```{r}

#colnames(extra_quarters) [5] <- "reading_pts4"

#mq4_read_all <- rbind(mq4_read_1, extra_quarters)

#dim(mq4_read_all)

#head(mq4_read_all)

```





# Language Arts Courses--Split and clean

```{r}

### Select the data of interest
q4LangArts <- select(q4_gradesUnique, 7,8, 42:75,79,80 )


### Put the data in the shape I want it in
mq4_lang <- melt(q4LangArts, id.vars=c("girlCode", "council"))



####################change column names
colnames (mq4_lang) [4] <-"langGrade"
colnames (mq4_lang) [3] <- "langCourses"


### Get rid of blanks
mq4_lang <- na.omit(mq4_lang)


###Change grades to all upper case to match
mq4_lang$langGrade <- toupper(mq4_lang$langGrade)

###change reading grade to factor 
mq4_lang$langGrade <-as.factor(mq4_lang$langGrade)

####Adjust Grades with a plus sign and fix spacing issues

mq4_lang$langGrade <-sub("B+", "B", fixed=TRUE, mq4_lang$langGrade)

mq4_lang$langGrade <-sub("C+", "C", fixed=TRUE, mq4_lang$langGrade)

mq4_lang$langGrade <-sub("A ", "A", fixed=TRUE, mq4_lang$langGrade)

mq4_lang$langGrade <-sub("2", "B", fixed=TRUE, mq4_lang$langGrade)

mq4_lang$langGrade <-sub("D+", "D", fixed=TRUE, mq4_lang$langGrade)

mq4_lang$langGrade <-sub("I", "F", fixed=TRUE, mq4_lang$langGrade)



#TESt  for bad date entry in grades
table(mq4_lang$langGrade)




##Test for free data entry
grep("freeLang1_quarter", mq4_lang$langCourses, ignore.case=TRUE)
grep("freelang_semester", mq4_lang$langCourses, ignore.case=TRUE)
##Test with code that I know works!
grep("mjIntensLangArts_quarter", mq4_lang$langCourses, ignore.case=TRUE)




```

## Check for Language Arts Free Data Entry

```{r}

### Review Free Text Entry
q4_free_lang <- select(q4_gradesUnique, 7,8, 76:78)

q4_free_lang_test <- q4_free_lang[grep("lang", q4_free_lang$course_text, ignore.case = TRUE),]

q4_free_lang_test
#
## Test to determine if there is any data in those columns
table(q4_free_lang$free_lang1_quarter)
table(q4_free_lang$free_lang2_semester)

```


##Find both quarter and semester grades and finalize semester grade

```{r}

##################Duplicates#########################################

### Find the unique girlCodes with just one grade 
mq4_lang_ok <- mq4_lang [!(duplicated(mq4_lang$girlCode) | duplicated(mq4_lang$girlCode, fromLast = TRUE)), ]

mq4_lang_ok

head(mq4_lang_ok)

### Find the girl codes with multiple grades

##############################Subset Duplicate Values##################
### find the duplicates
q4lang_dupes <-duplicated(mq4_lang$girlCode) | duplicated(mq4_lang$girlCode, fromLast=TRUE)

### Subset the duplicates
q4lang_dupes <- mq4_lang[q4lang_dupes, ]


dim(q4lang_dupes)


```

### Find and subset the Semester Grades in duplicate version 

```{r}
semester <- q4lang_dupes[grep("_semester", q4lang_dupes$langCourses, ignore.case = TRUE),]

dim(semester)

head(semester)
```


### Bind the Language Arts Courses together

```{r}
mq4_lang_all <- rbind(mq4_lang_ok, semester)


dim(mq4_lang_all)

distinct(mq4_lang_all, girlCode)

dim(mq4_lang_all)




```


## Calculate Grade Points Language Arts Courses
```{r}

lang_pts4 <- numeric(0)  #assign a variable

for(i in mq4_lang_all$langGrade){ #run throught all teh grades
   
     lang_pts4<- c(lang_pts4,switch(i, "A" =4, "B"=3, "C"=2, "D"=1, "F"=0, "I"=0)) # assign numeric points to grades
    
     lang_pts4

    
}

mq4_lang_all <- cbind(mq4_lang_all, lang_pts4) #bind return value with df. 

head(mq4_lang_all) #review

```

```{r}

aggregate(lang_pts4~girlCode+council+langCourses , mq4_lang_all, mean)

test_dupes <- duplicated(mq4_lang_all)

test_dupes
```


# Unexcused Absences

```{r}

### Select the data of interest
q4_unexcused <- select(q4_gradesUnique,7,8, 12)


### Create table to view the summary
q4_unexcused_tbl <- table(q4_unexcused$unexcusedAbs)

### Print the table
q4_unexcused_tbl

```

# Excused Absences

```{r}
### Select the data of interest
q4_excused <- select(q4_gradesUnique, 7, 8, 13)


### Create table to view the data
q4_excused_tbl <- with(q4_excused,table(excusedAbs))

### View the output
q4_excused_tbl

```


# Total Absences

```{r}


#### Merge unexcused and excused objects
q4_total_abs <- inner_join(q4_unexcused, q4_excused, by = "girlCode", Copy=FALSE)


### Sum up the two columns to get a total 
q4_total_abs$sum_abs <-q4_total_abs$unexcusedAbs + q4_total_abs$excusedAbs


colnames(q4_total_abs) [3] <- "q4_Unexcused" #change names for more readable variables downstreatm 
colnames(q4_total_abs) [5] <- "q4_Excused"
colnames(q4_total_abs) [6] <- "q4_Total_Abs"



head(q4_total_abs)


### Create table to view the data
#q4_total_abs_tbl <- with(q4_total_abs, table(sum_abs))

### See the table output
#q4_total_abs_tbl

```




# In School Suspensions

```{r}

### Look at data of interest
q4_in_school <- select(q4_gradesUnique, 7, 8, 14)


### Create table to look at data
q4_in_school_tbl <- with(q4_in_school, table(inSchoolSusp))

### View table
q4_in_school_tbl


```

# Out of School Suspenions

```{r}

q4_out_school <- select(q4_gradesUnique, 7, 8, 15)

q4_out_school_tbl <- with(q4_out_school, table(outofSchoolSusp))

q4_out_school_tbl

```


# Total suspensions
```{r}

q4_susp_total <- inner_join(q4_in_school, q4_out_school, by = "girlCode", copy=FALSE)

head(q4_susp_total)

q4_susp_total$susp_sum <- q4_in_school$inSchoolSusp + q4_out_school$outofSchoolSusp

head(q4_susp_total)

colnames(q4_susp_total) [3] <- "q4_InSchoool"
colnames(q4_susp_total) [5] <- "q4_OutSchool"
colnames(q4_susp_total) [6] <- "q4_Total"

#q4_susp_total_tbl <- with(q4_susp_total,table(susp_sum))

#q4_susp_total_tbl



```


# Expelled

```{r}

### Select the variable of interest
q4_expelled <- select(q4_gradesUnique, 7,8,16)

dim(q4_expelled)

head(q4_expelled)

### Create table to view the summary
q4_expelled_tbl <-with(q4_expelled,table(expelled))

### Print the table
q4_expelled_tbl

```

Promoted
```{r}

### Select the variable of interest
q4_promoted <- select(q4_gradesUnique, 7,8,17)

dim(q4_promoted)

head(q4_promoted)

### Create table to view the summary
q4_promoted_tbl <-with(q4_promoted,table(promoted))

### Print the table
q4_promoted_tbl

```




# Prepare data for database

## Merge Behavior Data

```{r eval=FALSE}

abs_susp <- full_join(q4_total_abs, q4_susp_total)

dim(abs_susp)


behavior_data <- full_join(abs_susp, q4_expelled)


behavior_data <- select(behavior_data,council, girlCode, sum_abs, susp_sum, expelled)

colnames (behavior_data) [1] <- "council"
colnames (behavior_data) [3] <- "total_absences"
colnames (behavior_data) [4] <- "total_suspensions"


head(behavior_data)




```





### Merge Grade Data

```{r eval=FALSE}

q4_lang_read <- full_join(mq4_lang_all, mq4_read_all)
dim(q4_lang_read)

head(q4_lang_read)

q4_lang_read <- select(q4_lang_read, council, girlCode, langCourses, langGrade, lang_pts4, readingCourses, readingGrade,reading_pts4)


colnames (q4_lang_read) [1] <- "council"

head(q4_lang_read)



```

### Merge all
```{r eval=FALSE}

q4_academic_data <- full_join(q4_lang_read, behavior_data, by="girlCode")

dim(q4_academic_data)

head(q4_academic_data)

q4_academic_data <- select(q4_academic_data, council.x, girlCode, langCourses, langGrade, lang_pts4, readingCourses,readingGrade, reading_pts4,total_absences, total_suspensions, expelled)

colnames (q4_academic_data) [1] <- "council"


head(q4_academic_data)
```




# Script to send to databases

```{r}
### Save data objects to Sqlite

setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

#dbWriteTable(conn =getReal_2016db, name = "Q4_academic_data", value = q4_academic_data, row.names = FALSE, overwrite = TRUE)



dbWriteTable(conn = getReal_2016db, name = "Q4_duplicates", value = q4Dupes, row.names=FALSE, overwrite=TRUE)


### Write Q1 Expelled data to sqlite database
dbWriteTable(conn = getReal_2016db, name = "Q4_expelled", value = q4_expelled, row.names=FALSE, overwrite=TRUE)


### Write Q1 Suspsenion data to sqlite database
dbWriteTable(conn = getReal_2016db, name = "Q4_Suspensions", value = q4_susp_total, row.names=FALSE, overwrite=TRUE)

### Write Q1 Absences to sqlite datase
dbWriteTable(conn = getReal_2016db, name = "Q4_Absences", value = q4_total_abs, row.names=FALSE, overwrite=TRUE)

### Write Q1 Lang Arts grade to sqlite database
dbWriteTable(conn = getReal_2016db, name = "Q4_lang", value = mq4_lang_all, row.names=FALSE, overwrite=TRUE)

### Write Q1 Reading grades to sqlite database
dbWriteTable(conn = getReal_2016db, name = "Q4_reading", value = mq4_read_all, row.names=FALSE, overwrite=TRUE)

```



