---
title: "academic_mastery"
author: "Kevin Gilds, MPA"
date: "June 14, 2016"
output: html_document
---
```{r import libaries, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(pander)
library(ggplot2)
library(sqldf)
library(psych)
library(knitr)
library(gridExtra)
library(effsize)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")


### Make connection with database
getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")




```


```{r load outcome survesy, echo=FALSE}

### Reade the girl_pre_survey database for analysis. 
pre_outcomes <- dbReadTable(getReal_2016db, "girl_pre")

post_outcomes <- dbReadTable(getReal_2016db, "girl_post")

post_outcomes <- select(post_outcomes, girlCode, council, am.avg)
###Select the variables of interest from the pre_survey
pre_outcomes <- select(pre_outcomes, girlCode, council, am.avg)

history <- dbReadTable(getReal_2016db, "basic_view")


```


```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data")

getReal_2014db<- dbConnect(SQLite(), dbname="data_Final_GetReal_2014_2015.sqlite")

prepost2014 <- dbReadTable(getReal_2014db, "girl_pre_post_matched")

am_prepost2014 <- prepost2014 %>%
    select(girlCode, council.x, am.avg.x, am.avg.y)


names(am_prepost2014)

colnames (am_prepost2014) [2] <- "council"
colnames (am_prepost2014) [3] <- "Post"
colnames (am_prepost2014) [4] <- "Pre"

am_prepost2014 <- am_prepost2014 %>%
    mutate("am.diff" = Post -Pre) %>%
    mutate("Year_Id" = "M2")

names(am_prepost2014)

am_prepost2014 <- am_prepost2014[, c(6,2,1,3,4,5)]

names(am_prepost2014)



```




```{r connect_2013_hr_data}
pre_outcomes2013 <- dbReadTable(getReal_2016db, "girl_pre2013")

post_outcomes2013 <-dbReadTable(getReal_2016db, "girl_post2013")

am_pre2013 <- pre_outcomes2013 %>%
    select(girlScoutCouncil, girlCode, am_avg)


am_post2013 <- post_outcomes2013 %>%
    select(girlScoutCouncil, girlCode, am_avg)


```



```{r join_2013_hr_data}

am_prepost2013 <- inner_join(am_pre2013, am_post2013, by="girlCode")
dim(am_prepost2013)

names(am_prepost2013)

colnames(am_prepost2013) [1] <- "council"
colnames(am_prepost2013) [3] <- "Pre"
colnames(am_prepost2013) [5]<- "Post"
    
am_prepost2013 <- am_prepost2013 %>%
    select(council, girlCode, Pre, Post)

am_prepost2013 <- am_prepost2013 %>%
    mutate(Year_Id = "M1")


am_prepost2013 <- am_prepost2013 %>%
    mutate(am.diff = Post- Pre)

```


```{r test_2013}

council <- group_by(am_prepost2013, council)

council

gateway <-with(council,table(council,Post >=4.5))

gateway

fun_test_1 <- with(am_prepost2013,table(Post >=4.5))

fun_test_1

fun_test_2 <-with(am_prepost2013,table(Post < 4.5 & am.diff >0))

fun_test_2

```

```{r}

fun_test_2014 <-with(am_prepost2014,table(Post >=4.5))

fun_test_2014

fun_test_2014_i <-with(am_prepost2014,table(Post <4.5 & am.diff >0))

fun_test_2014_i

```




```{r}
am_prepost <- inner_join(pre_outcomes, post_outcomes, by="girlCode")

dim(am_prepost)


```

```{r}
head(am_prepost)

names(am_prepost)

colnames(am_prepost) [2] <- "council"
colnames(am_prepost) [3] <- "Pre"
colnames(am_prepost) [5] <- "Post"

names(am_prepost)

am_prepost <-am_prepost %>%
    mutate(Year_Id = "M3")

am_prepost <- am_prepost %>%
    mutate(am.diff = Post - Pre)


str(am_prepost)


with(am_prepost,table(Post >=4.8))
hist(am_prepost$am.diff)

mean(am_prepost$am.diff)


am_achieved <-filter(am_prepost, Post >=4.8 )

plot(am_prepost$am.diff)
abline(h=0, col="red")




```







```{r}

names(am_prepost)

am_prepost <- am_prepost %>%
    select(girlCode, council, Pre, Post,Year_Id, am.diff)


am_prepost <- am_prepost[,c(5,2, 1,3,4,6)]

names(am_prepost)

names(am_prepost2013)

am_prepost2013 <- am_prepost2013[,c(5,1,2,3,4,6)]

names(am_prepost2013)

names(am_prepost2014)

names(am_prepost)

am_all <-rbind(am_prepost, am_prepost2013)

am_all <- rbind(am_all, am_prepost2014)





am_all$council <-sub("Girl Scouts of the Gateway Council Inc", "Gateway Council", fixed=TRUE, am_all$council)


am_high_df <- am_all %>%
    filter(Year_Id == "M3" & Post >=4.8)

nrow(am_high_df)

am_high <- with(am_all,table(Year_Id,Post >=4.8))

am_high

am_high_p <- prop.table(am_high,1)

pander(am_high_p)


am_increase_df <- filter(am_all, Post < 4.8)


am_increase <-with(am_increase_df, table(Year_Id, am.diff > 0 ))

am_increase

am_increase <- prop.table(am_increase,1)

pander(am_increase)


am_lowhigh <- filter(am_all, Pre < 4.8 & Post >=4.8)

nrow(am_lowhigh)

table(am_lowhigh$Year_Id)

head(am_lowhigh)

am_imrove <- with(am_lowhigh, table(Year_Id, Post >=4.8))


am_imrove <- prop.table(am_imrove,1)

pander(am_imrove)





```

#Tables

```{r}
am_high_df <- am_all %>%
    filter(Year_Id == "M3" & Post >=4.8)

nrow(am_high_df)

am_high <- with(am_all,table(Year_Id,Post >=4.8))

am_high

am_high_p <- prop.table(am_high,1)

pander(am_high_p)


am_increase_df <- filter(am_all, Year_Id == "M3" & Post < 4.8)

am_increase_df <- am_increase_df %>%
    filter(am.diff >0)

am_increase_df


am_increase <-with(am_increase_df, table(Year_Id, am.diff > 0 ))

am_increase

am_increase <- prop.table(am_increase,1)

pander(am_increase)


am_lowhigh <- filter(am_all, Pre < 4.8 & Post >=4.8)

am_lowhigh <- am_lowhigh %>%
    filter(Year_Id == "M3")

nrow(am_lowhigh)

table(am_lowhigh$Year_Id)

head(am_lowhigh)

am_imrove <- with(am_lowhigh, table(Year_Id, Post >=4.8))


am_imrove <- prop.table(am_imrove,1)

pander(am_imrove)





```



```{r}
mean(am_all$am.diff)
plot(am_all$am.diff)
abline(h=0, col="red")

```





```{r}

am_achieved <- function(Year) {
    
    if(Year =="M3"){
        dat <-filter(am_all, Year_Id =="M3")
        
    } else if(Year == "M1"){
        dat <- filter(am_all, Year_Id =="M1")
    } else { (Year == "M2")
    dat <- filter(am_all, Year_Id == "M2")
    }
    
    
    high <- filter(dat, Post >=4.8)
    hr_temp_1 <- nrow(high)/nrow(dat)
    hr_temp_1 <- round(hr_temp_1*100,2)
    hr_temp_1 <- paste0(hr_temp_1,"%", sep="")
    pander(hr_temp_1)
    
}

am_achieved("M1")
```





```{r}
am_match <-function(Year){
    
    if(Year =="M3"){
        dat <-filter(am_all, Year_Id =="M3")
        
    } else if(Year == "M1"){
        dat <- filter(am_all, Year_Id =="M1")
    } else { (Year == "M2")
    dat <- filter(am_all, Year_Id == "M2")
    }
    
    
    high <- filter(dat, Post >=4.8)
    increase <-filter(dat, Post < 4.8 & am.diff >0)
    ae_temp <- nrow(high) + nrow(increase)
    ae_temp_1 <- ae_temp/nrow(dat)
    ae_temp_1 <- round(ae_temp_1*100,2)
    ae_temp_1 <- paste0(ae_temp_1,"%", sep="")
    pander(ae_temp_1)
    

}

am_match("M3")
am_match("M2")
am_match("M1")

```













```{r}
am_lowHigh <-function (Year){
    if(Year =="M3"){
        dat <-filter(am_all, Year_Id =="M3")
        
    } else if(Year == "M1"){
        dat <- filter(am_all, Year_Id =="M1")
    } else { (Year == "M2")
    dat <- filter(am_all, Year_Id == "M2")
    }
    
    
    low <- filter(dat, Pre < 4.5 & Post >=4.5)
    low_1 <- nrow(low)/nrow(dat)
    ae_low_1 <- round(low_1*100,2)
    ae_low_1 <- paste0(ae_low_1, "%", sep="")
    pander(ae_low_1)
}

am_lowHigh("M1")

```



The number of pre and post survey that could be matched is **`r nrow(am_prepost)`**.

1. The number of students achieving the academic engagment outcome at a high level is **`r nrow(am_high_df)`**

2. The number of students who did not achieve outcome at high level but increased their outcome score is **`r nrow(am_increase_df)`** 


The percent of students with a successful outcome is **`r am_match("M3")`**

```{r}
am_2016 <- am_all %>%
    filter(Year_Id == "M3")

```




```{r}
pre_am_histq <- qplot(am_2016$Pre, geom="histogram", main= "Pre Survey", bins=50, xlab="Outcome Scores") + geom_vline(xintercept = 4.8, col="red") 


post_am_histq <-qplot(am_2016$Post, geom="histogram", main= "Post Survey", bins=50, xlab="Outcome Scores", ylim=c(0,60)) + geom_vline(xintercept = 4.8, col="red")

grid.arrange(pre_am_histq, post_am_histq, ncol=2)


```



The improvement in outcome scores is graphically represented below. 


```{r}
am_bar_pre <-qplot(am_2016$Pre >=4.8, geom="bar", ylim=c(0, 200), main="Pre survey Results", xlab="Achievment at High Level")

am_bar_post <-qplot(am_2016$Post >=4.8, geom ="bar", main="Post Survey Results", xlab="Achievment at High Level")

grid.arrange(am_bar_pre, am_bar_post, ncol=2)


```


```{r}

am_change <- am_2016 %>%
    filter(Pre !=6.0 & Post !=6.0)


```


The percent of students who went from low achievement to hig achievement is **`r am_lowHigh("M3")`** 
The number of students who had the opportunity to improve their academic engagement  outcome score is **`r nrow(am_change)`**, and the mean increase in outcome score is **`r mean(am_change$am.diff)`**



```{r}
am_change_p <- ggplot(am_change,(aes(x=am.diff, y=Pre)))
am_change_p + geom_count() + geom_hline(yintercept = 4.8) + geom_vline(xintercept = 0, col="red") + labs(x="Pre and Post Difference", y="Pre Outcome Score", title="Academic Mastery Survey Results")


```




