---
title: "academic_engagement"
author: "Kevin Gilds, MPA"
date: "June 13, 2016"
output: html_document
---





```{r import libaries, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(pander)
library(ggplot2)
library(sqldf)
library(psych)
library(knitr)
library(gridExtra)
library(effsize)
library(likert)


setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")


### Make connection with database
getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")




```


```{r load outcome survesy, echo=FALSE}

### Reade the girl_pre_survey database for analysis. 
pre_outcomes <- dbReadTable(getReal_2016db, "girl_pre")

post_outcomes <- dbReadTable(getReal_2016db, "girl_post")

post_outcomes <- select(post_outcomes, girlCode, council, ae.avg)
###Select the variables of interest from the pre_survey
pre_outcomes <- select(pre_outcomes, girlCode, council, ae.avg)

history <- dbReadTable(getReal_2016db, "basic_view")


```


```{r echo=FALSE}
setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data")

getReal_2014db<- dbConnect(SQLite(), dbname="data_Final_GetReal_2014_2015.sqlite")

prepost2014 <- dbReadTable(getReal_2014db, "girl_pre_post_matched")

ae_prepost2014 <- prepost2014 %>%
    select(girlCode, council.x, ae.avg.x, ae.avg.y)


#names(ae_prepost2014)

colnames (ae_prepost2014) [2] <- "council"
colnames (ae_prepost2014) [3] <- "Post"
colnames (ae_prepost2014) [4] <- "Pre"

ae_prepost2014 <- ae_prepost2014 %>%
    mutate("ae.diff" = Post -Pre) %>%
    mutate("Year_Id" = "M2")

#names(ae_prepost2014)

ae_prepost2014 <- ae_prepost2014[, c(6,2,1,3,4,5)]

#names(ae_prepost2014)



```




```{r connect_2013_ae_data, echo=FALSE}
pre_outcomes2013 <- dbReadTable(getReal_2016db, "girl_pre2013")

post_outcomes2013 <-dbReadTable(getReal_2016db, "girl_post2013")

ae_pre2013 <- pre_outcomes2013 %>%
    select(girlScoutCouncil, girlCode, ae_avg)


ae_post2013 <- post_outcomes2013 %>%
    select(girlScoutCouncil, girlCode, ae_avg)


```



```{r join_2013_ae_data, echo=FALSE}

ae_prepost2013 <- inner_join(ae_pre2013, ae_post2013, by="girlCode")

#dim(ae_prepost2013)

#names(ae_prepost2013)

colnames(ae_prepost2013) [1] <- "council"
colnames(ae_prepost2013) [3] <- "Pre"
colnames(ae_prepost2013) [5]<- "Post"
    
ae_prepost2013 <- ae_prepost2013 %>%
    select(council, girlCode, Pre, Post)

ae_prepost2013 <- ae_prepost2013 %>%
    mutate(Year_Id = "M1")


ae_prepost2013 <- ae_prepost2013 %>%
    mutate(ae.diff = Post- Pre)

```


```{r test_2013, echo=FALSE}

council <- group_by(ae_prepost2013, council)

#council

gateway <-with(council,table(council,Post >=4.5))

#gateway

fun_test_1 <- with(ae_prepost2013,table(Post >=4.5))

#fun_test_1

fun_test_2 <-with(ae_prepost2013,table(Post < 4.5 & ae.diff >0))

#fun_test_2

```

```{r echo=FALSE}

fun_test_2014 <-with(ae_prepost2014,table(Post >=4.5))

#fun_test_2014

fun_test_2014_i <-with(ae_prepost2014,table(Post <4.5 & ae.diff >0))

#fun_test_2014_i

```




```{r echo=FALSE}
ae_prepost <- inner_join(pre_outcomes, post_outcomes, by="girlCode")

#dim(ae_prepost)


```

```{r echo=FALSE}
#head(ae_prepost)

#names(ae_prepost)

colnames(ae_prepost) [2] <- "council"
colnames(ae_prepost) [3] <- "Pre"
colnames(ae_prepost) [5] <- "Post"

#names(ae_prepost)

ae_prepost <-ae_prepost %>%
    mutate(Year_Id = "M3")

ae_prepost <- ae_prepost %>%
    mutate(ae.diff = Post - Pre)



#str(ae_prepost)


#with(ae_prepost,table(Post >=4.5))
#hist(ae_prepost$ae.diff)

#mean(ae_prepost$ae.diff)


#ae_achieved <-filter(ae_prepost, Post >=4.5 )

#plot(ae_prepost$ae.diff)
#abline(h=0, col="red")




```







```{r echo=FALSE}

#names(ae_prepost)

ae_prepost <- ae_prepost %>%
    select(girlCode, council, Pre, Post,Year_Id, ae.diff)


ae_prepost <- ae_prepost[,c(5,2, 1,3,4,6)]

#names(ae_prepost)

#names(ae_prepost2013)

ae_prepost2013 <- ae_prepost2013[,c(5,1,2,3,4,6)]

#names(ae_prepost2013)

#names(ae_prepost2014)

#names(ae_prepost)

ae_all <-rbind(ae_prepost, ae_prepost2013)

ae_all <- rbind(ae_all, ae_prepost2014)





ae_all$council <-sub("Girl Scouts of the Gateway Council Inc", "Gateway Council", fixed=TRUE, ae_all$council)


ae_high_df <- ae_all %>%
    filter(Year_Id == "M3" & Post >=4.5)

#nrow(ae_high_df)

ae_high <- with(ae_all,table(Year_Id,Post >=4.5))

#ae_high

ae_high_p <- prop.table(ae_high,1)

#pander(ae_high_p)


ae_increase_df <- filter(ae_all, Year_Id == "M3" & Post < 4.5)


ae_incease_df_i <- ae_increase_df %>%
    filter(ae.diff >0)

#nrow(ae_incease_df_i)




ae_increase <-with(ae_increase_df, table(Year_Id, ae.diff > 0 ))

#ae_increase

ae_increase <- prop.table(ae_increase,1)

#pander(ae_increase)


#ae_lowhigh <- filter(ae_all, Pre < 4.5 & Post >=4.5)

#nrow(ae_lowhigh)

#table(ae_lowhigh$Year_Id)

#head(ae_lowhigh)

#ae_imrove <- with(ae_lowhigh, table(Year_Id, Post >=4.5))


#ae_imrove <- prop.table(ae_imrove,1)

#pander(ae_imrove)





```






```{r echo=FALSE}

ae_achieved <- function(Year) {
    
    if(Year =="M3"){
        dat <-filter(ae_all, Year_Id =="M3")
        
    } else if(Year == "M1"){
        dat <- filter(ae_all, Year_Id =="M1")
    } else { (Year == "M2")
    dat <- filter(ae_all, Year_Id == "M2")
    }
    
    
    high <- filter(dat, Post >=4.5)
    hr_temp_1 <- nrow(high)/nrow(dat)
    hr_temp_1 <- round(hr_temp_1*100,2)
    hr_temp_1 <- paste0(hr_temp_1,"%", sep="")
    pander(hr_temp_1)
    
}


```





```{r echo=FALSE}
ae_match <-function(Year){
    
    if(Year =="M3"){
        dat <-filter(ae_all, Year_Id =="M3")
        
    } else if(Year == "M1"){
        dat <- filter(ae_all, Year_Id =="M1")
    } else { (Year == "M2")
    dat <- filter(ae_all, Year_Id == "M2")
    }
    
    
    high <- filter(dat, Post >=4.5)
    increase <-filter(dat, Post < 4.5 & ae.diff >0)
    ae_temp <- nrow(high) + nrow(increase)
    ae_temp_1 <- ae_temp/nrow(dat)
    ae_temp_1 <- round(ae_temp_1*100,2)
    ae_temp_1 <- paste0(ae_temp_1,"%", sep="")
    pander(ae_temp_1)
    

}


```





```{r echo=FALSE}
ae_lowHigh <-function (Year){
    if(Year =="M3"){
        dat <-filter(ae_all, Year_Id =="M3")
        
    } else if(Year == "M1"){
        dat <- filter(ae_all, Year_Id =="M1")
    } else { (Year == "M2")
    dat <- filter(ae_all, Year_Id == "M2")
    }
    
    
    low <- filter(dat, Pre < 4.5 & Post >=4.5)
    low_1 <- nrow(low)/nrow(dat)
    ae_low_1 <- round(low_1*100,2)
    ae_low_1 <- paste0(ae_low_1, "%", sep="")
    pander(ae_low_1)
}



```

# Academic Engagement
Academic Engagement questions gauge tangible behaviors that help students succeed in school. Questions that measure Academic Engagement include the following.
Number	Question
1.	I talk with my teachers before or after school, or during lunch about my assignments.
2.	I hand in my assignments on time
3.	I finish my homework even if it is boring
4.	If I can't understand my schoolwork at first, I keep trying until I do understand it.


The number of pre and post survey that could be matched is **`r nrow(ae_prepost)`**.

1. The number of students achieving the academic engagment outcome at a high level is **`r nrow(ae_high_df)`**

2. The number of students who did not achieve outcome at high level but increased their outcome score is **`r nrow(ae_increase_df)`**


The percent of students with a successful outcome is **`r ae_match("M3")`**


The improvement in outcome scores is graphically represented below. 


```{r}

ae_2016 <- ae_all %>%
    filter(Year_Id == "M3")

```






```{r}
pre_ae_histq <- qplot(ae_2016$Pre, geom="histogram", main= "Pre Survey", bins=50, xlab="Outcome Scores" ) + geom_vline(xintercept = 4.5, col="red") 


post_ae_histq <-qplot(ae_2016$Post, geom="histogram", main= "Post Survey", bins=50, xlab="Outcome Scores", ylim=c(0,50)) + geom_vline(xintercept = 4.5, col="red")

grid.arrange(pre_ae_histq, post_ae_histq, ncol=2)


```


```{r}
ae_bar_pre <-qplot(ae_2016$Pre >=4.5, geom="bar", ylim=c(0, 200), main="Pre survey Results", xlab="Achievment at High Level")

ae_bar_post <-qplot(ae_2016$Post >=4.45, geom ="bar", main="Post Survey Results", xlab="Achievment at High Level")

grid.arrange(ae_bar_pre, ae_bar_post, ncol=2)


```

```{r}
ae_change <- ae_2016 %>%
    filter(Pre !=6.0 & Post !=6.0)


```

The percent of students who went from low achievement to hig achievement is **`r ae_lowHigh("M3")`** 
The number of students who had the opportunity to improve their academic engagement  outcome score is **`r nrow(ae_change)`**, and the mean increase in outcome score is **`r mean(ae_change$ae.diff)`**


The increase in the academic engagement outcome scores is represented graphically below. Marks to the right of the veticial red line represents an increase in the outcome score. Marks above the horizintal line represents scores above the high and low achievement. 



```{r}

ae_change <- ae_2016 %>%
    filter(Pre !=6.0 & Post !=6.0)


mean(ae_change$ae.diff)

ae_change_p <- ggplot(ae_change,(aes(x=ae.diff, y=Pre)))
ae_change_p + geom_count() + geom_hline(yintercept = 4.5) + geom_vline(xintercept = 0, col="red") + labs(x="Pre and Post Difference", y="Pre Outcome Score", title="Academic Engagement Survey Results")

```


A wilcox.test was administered on the healthy relationship outcome data and the results show that the 

```{r}
pander(wilcox.test(ae_2016$Pre, ae_2016$Post))

```


```{r}
cohen.d(ae_2016$Pre, ae_2016$Post, paired=TRUE)

```

## Cross Validation of Academic Engagment

Survey results from teachers and parents also provide evidence that the Get REAL! program helps students learn tangible tools to help them succeed in school. Below are tables that provide a breakdown of questions on the post survey from the parent and teacher surveys. The pattern again shows improvement in moderate agreement with the question being both with the parent survey and teacher survey. 

Parent Survey:

Question: She works on her homework at home without supervision

```{r}
pre_parent  <- dbReadTable(getReal_2016db, "pre_parent")

post_parent <- dbReadTable(getReal_2016db, "post_parent")

```

# Pre Survey
```{r}

colnames(pre_parent)[15] <- "Q5"

pre_parent_tbl <- pre_parent %>%
    select(15)

names(pre_parent_tbl)

pre_parent_tbl$Q5 <- factor(pre_parent_tbl$Q5, levels=c("Strongly Disagree", "Disagree", "Slightly Disagree", "Neither Agree/Disagree", "Slightly Agree", "Agree", "Strongly Agree"),ordered = TRUE)



```


```{r fig.height=5, fig.width=14, fig.path='Figs/', dev.args='cario-png'}

pre_parent_tbl <- likert(pre_parent_tbl)

summary(pre_parent_tbl)

plot(pre_parent_tbl, type="heat") +ggtitle("Parent Pre Survey Question 5") + theme_dark ()

```


```{r}
colnames(post_parent)[15] <- "Q6"

post_parent_tbl <- post_parent %>%
    select(15)

post_parent_tbl$Q6 <- factor(post_parent_tbl$Q6, levels=c("Strongly Disagree", "Disagree", "Slightly Disagree", "Neither Agree/Disagree", "Slightly Agree", "Agree", "Strongly Agree"),ordered = TRUE)


```


```{r fig.height=5, fig.width=14, fig.path='Figs/', dev.args='cario-png'}

post_parent_tbl <- likert(post_parent_tbl)

summary(post_parent_tbl)

plot(post_parent_tbl, type="heat") + ggtitle("Post Survey Question 6") + theme_dark ()

```


#Teacher Survey

Teacher Survey
Question 5: She positively participates in class
Question 6: She completes the homework given to her.

```{r fig.height=2, fig.width=15}
post_teacher <- dbReadTable(getReal_2016db, "post_teacher")


#names(post_teacher) checked 

colnames(post_teacher)[15] <- "Q6"
colnames(post_teacher)[14] <- "Q5"



post_teacher_tbl <- post_teacher %>%
    select(14,15)



post_teacher_tbl$Q5 <- factor(post_teacher_tbl$Q5, levels=c("Strongly Disagree", "Disagree", "Slightly Disagree", "Neither Agree/Disagree", "Slightly Agree", "Agree", "Strongly Agree"),ordered = TRUE)

post_teacher_tbl$Q6 <- factor(post_teacher_tbl$Q6, levels=c("Strongly Disagree", "Disagree", "Slightly Disagree", "Neither Agree/Disagree", "Slightly Agree", "Agree", "Strongly Agree"),ordered = TRUE)



```



```{r fig.height=5, fig.width=14, fig.path='Figs/', dev.args='cario-png'}

post_teacher_tbl <- likert(post_teacher_tbl)

summary(post_teacher_tbl)


plot(post_teacher_tbl, type="heat") + ggtitle("Teacher Post Survey Question 5 & 6") + theme_dark ()




```

