---
title: "academic_mastery"
author: "Kevin Gilds, MPA"
date: "June 14, 2016"
output: html_document
---
```{r import libaries, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(pander)
library(ggplot2)
library(sqldf)
library(psych)
library(knitr)
library(gridExtra)
library(effsize)
library(likert)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")


### Make connection with database
getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")




```


```{r load outcome survesy, echo=FALSE}

### Reade the girl_pre_survey database for analysis. 
pre_outcomes <- dbReadTable(getReal_2016db, "girl_pre")

post_outcomes <- dbReadTable(getReal_2016db, "girl_post")

post_outcomes <- select(post_outcomes, girlCode, council, am.avg)
###Select the variables of interest from the pre_survey
pre_outcomes <- select(pre_outcomes, girlCode, council, am.avg)

history <- dbReadTable(getReal_2016db, "basic_view")


```


```{r echo=FALSE}
setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data")

getReal_2014db<- dbConnect(SQLite(), dbname="data_Final_GetReal_2014_2015.sqlite")

prepost2014 <- dbReadTable(getReal_2014db, "girl_pre_post_matched")

am_prepost2014 <- prepost2014 %>%
    select(girlCode, council.x, am.avg.x, am.avg.y)


#names(am_prepost2014)

colnames (am_prepost2014) [2] <- "council"
colnames (am_prepost2014) [3] <- "Post"
colnames (am_prepost2014) [4] <- "Pre"

am_prepost2014 <- am_prepost2014 %>%
    mutate("am.diff" = Post -Pre) %>%
    mutate("Year_Id" = "M2")

#names(am_prepost2014)

am_prepost2014 <- am_prepost2014[, c(6,2,1,3,4,5)]

#names(am_prepost2014)



```




```{r connect_2013_am_data, echo=FALSE}
pre_outcomes2013 <- dbReadTable(getReal_2016db, "girl_pre2013")

post_outcomes2013 <-dbReadTable(getReal_2016db, "girl_post2013")

am_pre2013 <- pre_outcomes2013 %>%
    select(girlScoutCouncil, girlCode, am_avg)


am_post2013 <- post_outcomes2013 %>%
    select(girlScoutCouncil, girlCode, am_avg)


```



```{r join_2013_am_data, echo=FALSE}

am_prepost2013 <- inner_join(am_pre2013, am_post2013, by="girlCode")
dim(am_prepost2013)

#names(am_prepost2013)

colnames(am_prepost2013) [1] <- "council"
colnames(am_prepost2013) [3] <- "Pre"
colnames(am_prepost2013) [5]<- "Post"
    
am_prepost2013 <- am_prepost2013 %>%
    select(council, girlCode, Pre, Post)

am_prepost2013 <- am_prepost2013 %>%
    mutate(Year_Id = "M1")


am_prepost2013 <- am_prepost2013 %>%
    mutate(am.diff = Post- Pre)

```


```{r test_2013, echo=FALSE, eval=FALSE}

council <- group_by(am_prepost2013, council)



gateway <-with(council,table(council,Post >=4.5))



fun_test_1 <- with(am_prepost2013,table(Post >=4.5))



fun_test_2 <-with(am_prepost2013,table(Post < 4.5 & am.diff >0))



```

```{r echo=FALSE, eval=FALSE}

fun_test_2014 <-with(am_prepost2014,table(Post >=4.5))

#fun_test_2014

fun_test_2014_i <-with(am_prepost2014,table(Post <4.5 & am.diff >0))

#fun_test_2014_i

```




```{r join_am_2016, echo=FALSE}
am_prepost <- inner_join(pre_outcomes, post_outcomes, by="girlCode")

#dim(am_prepost)


```

```{r echo=FALSE}

#head(am_prepost)

#names(am_prepost)

colnames(am_prepost) [2] <- "council"
colnames(am_prepost) [3] <- "Pre"
colnames(am_prepost) [5] <- "Post"

#names(am_prepost)

am_prepost <-am_prepost %>%
    mutate(Year_Id = "M3")

am_prepost <- am_prepost %>%
    mutate(am.diff = Post - Pre)


#str(am_prepost)


#with(am_prepost,table(Post >=4.8))
#hist(am_prepost$am.diff)

#mean(am_prepost$am.diff)


am_achieved <-filter(am_prepost, Post >=4.8 )

#plot(am_prepost$am.diff)
#abline(h=0, col="red")




```







```{r am_setup, echo=TRUE}

#names(am_prepost)

am_prepost <- am_prepost %>%
    select(girlCode, council, Pre, Post,Year_Id, am.diff)


am_prepost <- am_prepost[,c(5,2, 1,3,4,6)]

#names(am_prepost)

#names(am_prepost2013)

am_prepost2013 <- am_prepost2013[,c(5,1,2,3,4,6)]

#names(am_prepost2013)

#names(am_prepost2014)

#names(am_prepost)

am_all <-rbind(am_prepost, am_prepost2013)

am_all <- rbind(am_all, am_prepost2014)





am_all$council <-sub("Girl Scouts of the Gateway Council Inc", "Gateway Council", fixed=TRUE, am_all$council)


am_high_df <- am_all %>%
    filter(Year_Id == "M3" & Post >=4.8)

nrow(am_high_df)

am_high <- with(am_all,table(Year_Id,Post >=4.8))

am_high

am_high_p <- prop.table(am_high,1)

pander(am_high_p)


am_increase_df <- filter(am_all, Post < 4.8)


am_increase <-with(am_increase_df, table(Year_Id, am.diff > 0 ))

am_increase

am_increase <- prop.table(am_increase,1)

#pander(am_increase)


am_lowhigh <- filter(am_all, Pre < 4.8 & Post >=4.8)

nrow(am_lowhigh)

table(am_lowhigh$Year_Id)

#head(am_lowhigh)

am_imrove <- with(am_lowhigh, table(Year_Id, Post >=4.8))


am_imrove <- prop.table(am_imrove,1)

#pander(am_imrove)





```

#Tables

```{r}
am_high_df <- am_all %>%
    filter(Year_Id == "M3" & Post >=4.8)

#nrow(am_high_df)

am_high <- with(am_all,table(Year_Id,Post >=4.8))

#am_high

am_high_p <- prop.table(am_high,1)

pander(am_high_p)


am_increase_df <- filter(am_all, Year_Id == "M3" & Post < 4.8)

am_increase_df <- am_increase_df %>%
    filter(am.diff >0)

am_increase_df


am_increase <-with(am_increase_df, table(Year_Id, am.diff > 0 ))

am_increase

am_increase <- prop.table(am_increase,1)

#pander(am_increase)


am_lowhigh <- filter(am_all, Pre < 4.8 & Post >=4.8)

am_lowhigh <- am_lowhigh %>%
    filter(Year_Id == "M3")

nrow(am_lowhigh)

table(am_lowhigh$Year_Id)

#head(am_lowhigh)

am_improve <- with(am_lowhigh, table(Year_Id, Post >=4.8))

nrow(am_improve)

am_improve <- prop.table(am_imrove,1)

#pander(am_imrove)





```



```{r echo=FALSE}
#mean(am_all$am.diff)
#plot(am_all$am.diff)
#abline(h=0, col="red")

```





```{r echo=FALSE}

am_achieved <- function(Year) {
    
    if(Year =="M3"){
        dat <-filter(am_all, Year_Id =="M3")
        
    } else if(Year == "M1"){
        dat <- filter(am_all, Year_Id =="M1")
    } else { (Year == "M2")
    dat <- filter(am_all, Year_Id == "M2")
    }
    
    
    high <- filter(dat, Post >=4.8)
    hr_temp_1 <- nrow(high)/nrow(dat)
    hr_temp_1 <- round(hr_temp_1*100,2)
    hr_temp_1 <- paste0(hr_temp_1,"%", sep="")
    pander(hr_temp_1)
    
}


```





```{r}
am_match <-function(Year){
    
    if(Year =="M3"){
        dat <-filter(am_all, Year_Id =="M3")
        
    } else if(Year == "M1"){
        dat <- filter(am_all, Year_Id =="M1")
    } else { (Year == "M2")
    dat <- filter(am_all, Year_Id == "M2")
    }
    
    
    high <- filter(dat, Post >=4.8)
    increase <-filter(dat, Post < 4.8 & am.diff >0)
    ae_temp <- nrow(high) + nrow(increase)
    ae_temp_1 <- ae_temp/nrow(dat)
    ae_temp_1 <- round(ae_temp_1*100,2)
    ae_temp_1 <- paste0(ae_temp_1,"%", sep="")
    pander(ae_temp_1)
    

}


```













```{r echo=FALSE}
am_lowHigh <-function (Year){
    if(Year =="M3"){
        dat <-filter(am_all, Year_Id =="M3")
        
    } else if(Year == "M1"){
        dat <- filter(am_all, Year_Id =="M1")
    } else { (Year == "M2")
    dat <- filter(am_all, Year_Id == "M2")
    }
    
    
    low <- filter(dat, Pre < 4.8 & Post >=4.8)
    low_1 <- nrow(low)/nrow(dat)
    ae_low_1 <- round(low_1*100,2)
    ae_low_1 <- paste0(ae_low_1, "%", sep="")
    pander(ae_low_1)
}



```



# Academic Mastery

The Academic Mastery questions gauge a student's attitude towards school and education. Questions that measure Academic Mastery include the following.

* It's important to me that I improve my skills this year in school
* It's important to me that I really understand my class work
* Learning at school is important to me
* One of my goals in school is to learn as much as I can
* The things I am learning in school will help me later in life



The number of pre and post survey that could be matched is **`r nrow(am_prepost)`**.

1. The number of students achieving the academic engagment outcome at a high level is **`r nrow(am_high_df)`**

2. The number of students who did not achieve outcome at high level but increased their outcome score is **`r nrow(am_increase_df)`** 


The percent of students with a successful outcome is **`r am_match("M3")`**

```{r}
am_2016 <- am_all %>%
    filter(Year_Id == "M3")

```




```{r}
pre_am_histq <- qplot(am_2016$Pre, geom="histogram", main= "Pre Survey", bins=50, xlab="Outcome Scores") + geom_vline(xintercept = 4.8, col="red") 


post_am_histq <-qplot(am_2016$Post, geom="histogram", main= "Post Survey", bins=50, xlab="Outcome Scores", ylim=c(0,60)) + geom_vline(xintercept = 4.8, col="red")

grid.arrange(pre_am_histq, post_am_histq, ncol=2)


```



The improvement in outcome scores is graphically represented below. 


```{r}
am_bar_pre <-qplot(am_2016$Pre >=4.8, geom="bar", ylim=c(0, 300), main="Pre survey Results", xlab="Achievment at High Level")

am_bar_post <-qplot(am_2016$Post >=4.8, geom ="bar", ylim=c(0,300), main="Post Survey Results", xlab="Achievment at High Level")

grid.arrange(am_bar_pre, am_bar_post, ncol=2)


```


```{r}

am_change <- am_2016 %>%
    filter(Pre !=6.0 & Post !=6.0)


```


The percent of students who went from low achievement to hig achievement is **`r am_lowHigh("M3")`** 
The number of students who had the opportunity to improve their academic engagement  outcome score is **`r nrow(am_change)`**, and the mean increase in outcome score is **`r mean(am_change$am.diff)`**



```{r}
am_change_p <- ggplot(am_change,(aes(x=am.diff, y=Pre)))
am_change_p + geom_count() + geom_hline(yintercept = 4.8) + geom_vline(xintercept = 0, col="red") + labs(x="Pre and Post Difference", y="Pre Outcome Score", title="Academic Mastery Survey Results")


```


A wilcox.test was administered on the healthy relationship outcome data and the results show that the 

```{r}
pander(wilcox.test(am_2016$Pre, am_2016$Post))

```


```{r}
cohen.d(am_2016$Pre, am_2016$Post, paired=TRUE)

```

## Cross Validation of Academic Mastery

Survey results from teachers and parents also provide evidence that the Get REAL! program helps students formulate better attitude toward school. Below are tables that provide a breakdown of questions on the post survey from the parent and teacher surveys. The pattern again shows improvement in moderate agreement with the question being both with the parent survey and teacher survey. 

Parent Survey
Question 1: She is motivated to graduate high school
Question 3: She has a Good Attitude About School
```{r}
pre_parent  <- dbReadTable(getReal_2016db, "pre_parent")

post_parent <- dbReadTable(getReal_2016db, "post_parent")

```



```{r fig.height=5, fig.width=10}

colnames(pre_parent) [10] <- "Q1"

colnames(pre_parent) [12] <- "Q3"


pre_parent_tbl <- pre_parent %>%
    select( 10,12 )



#names(pre_parent_tbl)

pre_parent_tbl$Q1 <- factor(pre_parent_tbl$Q1, levels=c("Strongly Disagree", "Disagree", "Slightly Disagree", "Neither Agree/Disagree", "Slightly Agree", "Agree", "Strongly Agree"),ordered = TRUE)

pre_parent_tbl$Q3 <- factor(pre_parent_tbl$Q3, levels=c("Strongly Disagree", "Disagree", "Slightly Disagree", "Neither Agree/Disagree", "Slightly Agree", "Agree", "Strongly Agree"),ordered = TRUE)


pre_parent_q1 <-table(pre_parent_tbl$Q1) #make table to test

pander(pre_parent_q1) #print results of test nicely



pre_parent_q3 <-table(pre_parent_tbl$Q3) #make tabl to test result


pander(pre_parent_q3) #print result of test nicely


nrow(pre_parent_tbl) #determine total number of observations to verify percents in likert tables 



pre_parent_tbl <- likert(pre_parent_tbl)

summary(pre_parent_tbl)








```


```{r}

colnames(post_parent) [10] <- "Q1"

colnames(post_parent) [12] <- "Q3"

post_parent_tbl <- post_parent %>%
    select(10,12)



post_parent_tbl$Q1 <- factor(post_parent_tbl$Q1, levels=c("Strongly Disagree", "Disagree", "Slightly Disagree", "Neither Agree/Disagree", "Slightly Agree", "Agree", "Strongly Agree"),ordered = TRUE)

post_parent_tbl$Q3 <- factor(post_parent_tbl$Q3, levels=c("Strongly Disagree", "Disagree", "Slightly Disagree", "Neither Agree/Disagree", "Slightly Agree", "Agree", "Strongly Agree"),ordered = TRUE)


post_parent_test_q1 <-table(post_parent_tbl$Q1) #make table to test

pander(post_parent_test_q1) #show result of test


post_parent_test_q3 <-table(post_parent_tbl$Q3) #make table to test 

pander(post_parent_test_q3)  # show results of test

nrow(post_parent_tbl) #check to determine total to make divisible. 

post_parent_tbl <- likert(post_parent_tbl) #make into liker table

summary(post_parent_tbl)  #make summary of likert items


```





Pre Survey
```{r fig.height=5, fig.width=14, fig.path='Figs/', dev.args='cario-png' }
likert.heat.plot(pre_parent_tbl) + ggtitle("Pre Parent Survey Question 1 & Question 3") + theme_dark ()

```


Post Survey
```{r fig.height=5, fig.width=14, fig.path='Figs/', dev.args='cario-png' }

likert.heat.plot(post_parent_tbl) + ggtitle("Post Parent Survey Question 1 & Question 3") + theme_dark()
```



Teacher Survey
Question 1: She is motivated to graduate high school
Question 3: She has a Good Attitude About School

```{r}
post_teacher <- dbReadTable(getReal_2016db, "post_teacher")

colnames(post_teacher) [10] <- "Q1"
colnames(post_teacher) [12] <- "Q3"

post_teacher_tbl <- post_teacher %>%
    select(10, 12)






post_teacher_tbl$Q1 <- factor(post_teacher_tbl$Q1, levels=c("Strongly Disagree", "Disagree", "Slightly Disagree", "Neither Agree/Disagree", "Slightly Agree", "Agree", "Strongly Agree"),ordered = TRUE)


post_teacher_tbl$Q3 <- factor(post_teacher_tbl$Q3, levels=c("Strongly Disagree", "Disagree", "Slightly Disagree", "Neither Agree/Disagree", "Slightly Agree", "Agree", "Strongly Agree"),ordered = TRUE)


post_teacher_q1 <- table(post_teacher_tbl$Q1) #make table to test results

pander(post_teacher_q1) #prints results of test



post_teacher_q3 <- table(post_teacher_tbl$Q3) #make table to test 

pander(post_teacher_q3) #prints tests nicely


nrow(post_teacher_tbl) #total observations



post_teacher_tbl <- likert(post_teacher_tbl)

summary(post_teacher_tbl)


```

```{r fig.height=5, fig.width=14, fig.path='Figs/', dev.args='cario-png'}

plot(post_teacher_tbl, type="heat") +ggtitle("Post Teacher Survey Question 1 & Question 3") + theme_dark()



```


