---
title: "Attendance"
author: "Kevin Gilds, MPA"
date: "May 8, 2016"
output: html_document
---


```{r echo=FALSE, warning=FALSE, message=FALSE}

library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

library(dplyr)
library(dplyr)
library(pander)
library(ggplot2)
library (ezknitr)

setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")



q1_absences <-dbReadTable(getReal_2016db, "Q1_Absences")
q2_absences <-dbReadTable(getReal_2016db, "Q2_Absences")



```



# Absences: 

```{r echo=FALSE}

absences <- inner_join(q1_absences, q2_absences, by="girlCode")



absences_1 <- absences %>%
    select(girlCode, council.x.x, sum_abs.x, sum_abs.y) 
    
absences_q2q1 <- absences_1 %>%
    mutate(abs_diff = sum_abs.y - sum_abs.x)





```


### Absences Success: % of Students who decreased their absences or had no absences. 
```{r echo=FALSE}

absences_success <- function() {
    no_absences <- filter(absences_q2q1, abs_diff == 0, sum_abs.y ==0)
    decrease_abs <- filter(absences_q2q1, abs_diff<0 )
    abs_total <- nrow(no_absences) + nrow(decrease_abs)
    abs_total <- abs_total / nrow(absences_q2q1)
    abs_total <- round(abs_total*100,2)
    pander(paste0(abs_total, "%", sep= ""))
    
}



absences_success()
```

The number of valid entries is **`r nrow(absences_q2q1)`**, and the number of students who decreased their absences or did not miss any days is **`r absences_success()`**. 


### Absences Change
```{r echo=FALSE, eval=TRUE}

absences_change <- with(absences_q2q1, table(abs_diff))

pander(absences_change)



#absences_change_1 <-with(absences_q2q1,table(abs_diff <0))

#absences_change_2 <-with(absences_q2q1,table(abs_diff ==0, sum_abs.y == 0))

#absences_change_3 <-with(absences_q2q1,table(sum_abs.x == 0, sum_abs.y == 0))

#pander(absences_change_2)

#pander(absences_change_3)


#pander(absences_change_1)

#plot(absences_change)

```

### Average Change from Quarter 1 to Quarter 2

```{r echo=FALSE}

abs_diff<- pander(mean(absences_q2q1$abs_diff, na.rm=TRUE))


```


The average difference of absences  between Quarter 1 and Quarter 2 is **`r abs_diff`**.

```{r echo=FALSE}

colnames (absences_q2q1) [2] <- "Council"
colnames (absences_q2q1) [3] <- "Q1_Abs"
colnames (absences_q2q1) [4] <- "Q2_Abs"
colnames (absences_q2q1) [5] <- "Abs_Change"

```

The plot below has the council on the vertical axix and the difference in abesences between Quarter 1 and Quarter 2. For this plot it is good to see the circles on the left to reflect decreases. 


```{r echo=FALSE, warning=FALSE}

abs_change_plot_c <- ggplot(absences_q2q1,(aes(x = Abs_Change, y = Council)))

abs_change_plot_c + geom_count()



#abs_change_plot2 <- ggplot(absences_q2q1,(aes(x = Abs_Change, y = Q1_Abs)))

#abs_change_plot2 + geom_count()

```

