---
title: "Council Report"
author: "Kevin Gilds, MPA"
date: "January 30, 2016"
output: html_document
---

```{r r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=5, fig.path='Figs/',
                       warning=FALSE, message=FALSE, echo=FALSE)




```



```{r echo=FALSE}
library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")


```

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(dplyr)
library(pander)
library(ggplot2)
library (ezknitr)

setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")


### Make connection with database
girl <- dbReadTable(getReal_2016db, "girl_pre")

###Select the neeeded data for data entry status update
girl <- select(girl, council)
###Create and add column for status update
girl$dataSource <-"girl"

### Make connection with database
parent <-dbReadTable(getReal_2016db,"pre_parent")
###Select the neeeded data for data entry status update
parent <- select(parent,council)
###Create and add column for status update
parent$dataSource <- "parent"

### Make connection with database
teacher <-dbReadTable(getReal_2016db, "pre_teacher")
###Select the neeeded data for data entry status update
teacher <-select(teacher,council)
###Create and add column for status update
teacher$dataSource <- "teacher"

###Bind girl and parent objects to prepare for status report
girl_parent <- rbind(girl,parent)

### Make connection with database
grades_q1 <- dbReadTable(getReal_2016db,"Q1_Absences")
###Select the neeeded data for data entry status update

q1_stats <- select(grades_q1,council.x)
###Change column name to make it match with other data sets
colnames (q1_stats) [1] <- "council"
###Create and add column for status update
q1_stats$dataSource <- "Q1"


### Add the teacher to binding for status report
add_teacher <- rbind(girl_parent, teacher)


###Findal addition to create data frame for status report
survey_status <- rbind(add_teacher, q1_stats)

### Read the pre girl survey for reference down stream
girl_survey_dupes <-dbReadTable(getReal_2016db, "girl_pre_duplicates")
### Read the pre girl survey for reference down stream
parent_survey_dupes <-dbReadTable(getReal_2016db, "pre_parent_duplicate")
### Read the pre girl survey for reference down stream
q1_dupes <-dbReadTable(getReal_2016db, "Q1_duplicates")

### Reade the girl_pre_survey database for analysis. 
outcomes <- dbReadTable(getReal_2016db, "girl_pre")
###Select the variables of interest from the pre_survey
outcomes <- select(outcomes, girlCode, council, hr.avg, am.avg, ae.avg)


q1_reading <-dbReadTable(getReal_2016db, "Q1_reading")
q1_langarts <-dbReadTable(getReal_2016db,"Q1_lang")
q1_absences <-dbReadTable(getReal_2016db, "Q1_Absences")
q1_suspensions <- dbReadTable(getReal_2016db, "Q1_Suspensions")


```

## Healthy Relationships

The number of valid surveys is `r nrow(outcomes)`

### Healthy Relationships Outcome Tables
```{r hr, eval=FALSE}
### create basic outcome table for healty releationship outcome

hr_tbl <- with(outcomes,table(hr.avg >=4.45))

### print in pretty table
pander(hr_tbl)

### Put percents with outcome table
hr_tbl_p <- prop.table(hr_tbl)


###Print percent table
pander(hr_tbl_p)

#

```


### Percent Achieving at high level
```{r council_hr}


## Basic outcome table for healthy relationships by council
hr_tbl_c <- with(outcomes, table(council, hr.avg >=4.45))

### print results of outcome table
#pander(hr_tbl_c)


####Percent by council

hr_tbl_cp <- prop.table(hr_tbl_c, 1)

hr_tbl_cp <- round(hr_tbl_cp *100,2)

### Print by percent
pander(hr_tbl_cp)


```


### Healthy Relationship Plots

Students must average a 4.45 on the questions to achieve this outcome a high level.


```{r}

hr <- select(outcomes, council, hr.avg)

hr_hist <- ggplot(hr, aes(x=hr.avg))
        hr_hist + geom_histogram(fill="blue") +facet_grid(~council) + labs(x=" All Outcome Scores", title = "Pre: Healthy Relationships")
        
hr_box <- ggplot(hr, aes(x=factor(council), hr.avg))
        hr_box + geom_boxplot(fill="blue") + labs(y=" All Outcome Scores", title = "Pre: Healthy Relationships")

```






## Academic Engagement

### Academic Engagement Outcome Tables

The number of valid surveys is ` r nrow(outcomes)`

```{r ae, eval=FALSE}
### Prepare data frame for tables
ae <- select(outcomes, council, ae.avg)

### Create outcome tables
ae_tbl <-with(ae,table(ae.avg >=4.5))

### Print outcome table
#pander(ae_tbl)

### Create percent outcome table
ae_tbl_p <- prop.table(ae_tbl)

### Print Outcome table
pander(ae_tbl_p)

### Make outcome table by council
ae_tbl_c <-with(ae,table(council, ae.avg >=4.5))

### Print Outcome table by council
pander(ae_tbl_c)

### Make outcome table by percent
ae_tbl_cp <- prop.table(ae_tbl_c,1)

### Print percent table. 
pander(ae_tbl_cp)



```


### Percent Achieving at high level
```{r council_ae}

### Prepare data frame for tables
ae <- select(outcomes, council, ae.avg)

### Make outcome table by council
ae_tbl_c <-with(ae,table(council, ae.avg >=4.5))

### Print Outcome table by council
#pander(ae_tbl_c)

### Make outcome table by percent
ae_tbl_cp <- prop.table(ae_tbl_c,1)

ae_tbl_cp <-round(ae_tbl_cp *100,2)

### Print percent table. 
pander(ae_tbl_cp)



```

### Academic Engagement Plots

Students must average a 4.5 on the questions to achieve this outcome a high level.

Potential high impact outcome as many students are close. 


```{r ae_plots_council}

ae <- select(outcomes, council, ae.avg)

ae_hist <- ggplot(ae, aes(x=ae.avg))
        ae_hist + geom_histogram(fill="blue") +facet_grid(~council) + labs(x=" All Outcome Scores", title = "Pre: Healthy Relationships")
        
ae_box <- ggplot(ae, aes(x=factor(council), ae.avg))
        hr_box + geom_boxplot(fill="blue") + labs(y=" All Outcome Scores", title = "Pre: Academic Engagment")

```


## Academic Mastery


### Academic Mastery Outcome Tables

The number of valid surveys entered is ` r nrow(outcomes)`

```{r am, eval=FALSE}

###Create data fram to set up outcome table
am <- select(outcomes, council, am.avg)

###Create academic mastery outcome table
am_tbl <- with(am,table(am.avg >=4.8))


### Print outcome table
#pander(am_tbl)

### Put percentage to counts
am_tbl_p <- prop.table(am_tbl)


### Print pretty percent table.
pander(am_tbl_p)



```


### Percent Achieving at high level
```{r council_am}

am  <- select(outcomes, council, am.avg)


### Outcome count by table
am_c <- with(am,table(council, am.avg >=4.8))

### Print outcome table
#pander(am_c)

#### Academic Mastery by outcome count by percent
am_cp <-prop.table(am_c,1)

am_cp <- round(am_cp,2)*100

#### Print outcome percent outcome table. 
pander(am_cp)

```

### Academic Mastery Plots

Students must average a 4.8 on the questions to achieve this outcome a high level

```{r}

am <- select(outcomes, council, am.avg)

am_hist <- ggplot(am, aes(x=hr.avg))
        hr_hist + geom_histogram(fill="blue") +facet_grid(~council) + labs(x=" All Outcome Scores", title = "Pre: Academic Mastery")
        
am_box <- ggplot(am, aes(x=factor(council), am.avg))
        am_box + geom_boxplot(fill="blue") + labs(y=" All Outcome Scores", title = "Pre: Academic Mastery")

```


Academic Data: Quarter 1

## Language Arts Grades:

Th number of valid data records for Language Arts grades is **`r nrow(q1_langarts)`**. 

```{r lang_grades, eval=FALSE}

lang_grades <-with(q1_langarts,table(langGrade))

pander(lang_grades)



```


```{r council_lang}

lang_grades_c <-with(q1_langarts,table(council,langGrade))

pander(lang_grades_c)

```


```{r}

lang_plot <- ggplot(q1_langarts,(aes(x = langGrade, y = council)))

lang_plot + geom_count()

```



## Reading Courses:

The number of valid reading courses entered is **`r nrow (q1_reading)`**. 

```{r read, eval=FALSE}

read_grades <-with(q1_reading,table(readingGrade))

pander(read_grades)




```

```{r council_read, }

read_grades_c <-with(q1_reading,table(council, readingGrade))

pander(read_grades_c)

```

### Reading Grade Plot
```{r}

read_plot <- ggplot(q1_reading,(aes(x = readingGrade, y = council)))

read_plot + geom_count()


```



## Number of Absences

The number of valid entries for attendance data is **`r nrow(q1_absences)`**.

### Total Number of Absences:

```{r total_abs, eval=FALSE}

### Create table to view the data
total_abs_tbl <- with(q1_absences, table(sum_abs))

### See the table output
pander(total_abs_tbl)




```



```{r council_abs_total, echo=FALSE}

total_abs_tbl_c <-with(q1_absences,table(council.x, sum_abs))

pander(total_abs_tbl_c)

```


```{r plot_absences}
total_absPlot <- ggplot(q1_absences,(aes(x = sum_abs, y = council.x)))

total_absPlot + geom_count()


```



### Unexcused Absences:
```{r unexcused, eval=FALSE}
unexcused <-with(q1_absences, table(unexcusedAbs))

pander(unexcused)

```


```{r council_unexcused, echo=FALSE}

unexcused_c <-with(q1_absences, table(council.x, unexcusedAbs))

pander(unexcused_c)



```




### Excused Absences:

```{r excused, eval=FALSE }
excused_abs <-with(q1_absences,table(excusedAbs))

pander(excused_abs)

```



```{r council_excused, echo=FALSE}

excused_abs_c <- with(q1_absences,table(council.x, excusedAbs))

pander(excused_abs_c)

```



## Suspensions

The number of valid entries for behavioral data is **`r nrow(q1_suspensions)`**.


### Total Suspsensions:

```{r total_susp, echo=FALSE, eval=FALSE}
susp_total <- with(q1_suspensions,table(susp_sum))

pander(susp_total)


```



```{r council_suspTotal, echo=FALSE}

susp_total_c <-with(q1_suspensions, table(council.x, susp_sum))

pander(susp_total_c)

```


```{r}

suspension_plot <- ggplot(q1_suspensions,(aes(x = susp_sum, y = council.x)))

suspension_plot + geom_count()


```



### In School Suspensions:
```{r in_school, echo=FALSE, eval=FALSE}

in_school <-with(q1_suspensions, table(inSchoolSusp))

pander(in_school)

```



```{r council_inschool, echo=FALSE}

in_school_c <-with(q1_suspensions,table(council.x, inSchoolSusp))

pander(in_school_c)

```


### Out of School Suspensions:

```{r out_school, echo=FALSE, eval=FALSE}
out_school <-with(q1_suspensions,table(outofSchoolSusp))

pander(out_school)
```

```{r council_out, echo=FALSE, eval=TRUE}

out_school_c <-with(q1_suspensions,table(council.x, outofSchoolSusp))

pander(out_school_c)

```

