---
title: "grade_analysis_2"
author: "Kevin Gilds, MPA"
date: '`r Sys.Date()`'
output: 
  html_document: 
    toc: yes
---

# Set up R to read database

```{r echo=FALSE, warning=FALSE}

library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

library(dplyr)
library(dplyr)
library(pander)
library(ggplot2)
library (ezknitr)

setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")


q1_reading <-dbReadTable(getReal_2016db, "Q1_reading")
q1_langarts <-dbReadTable(getReal_2016db,"Q1_lang")
q1_absences <-dbReadTable(getReal_2016db, "Q1_Absences")
q1_suspensions <- dbReadTable(getReal_2016db, "Q1_Suspensions")
q2_reading <- dbReadTable(getReal_2016db, "Q2_reading")
q2_langarts <-dbReadTable(getReal_2016db, "Q2_lang")
q2_absences <-dbReadTable(getReal_2016db, "Q2_Absences")
q2_suspensions <-dbReadTable(getReal_2016db, "Q2_Suspensions")



```



# Reading Data--

## Join Q1 and Q2 Data

```{r echo=FALSE}
reading <-inner_join(q1_reading, q2_reading, by="girlCode")



reading_1 <- reading %>%
    select(girlCode,council.x, reading_pts, reading_pts2)




reading_q2q1 <- reading_1 %>%
    mutate(reading_pt_diff = reading_pts2 - reading_pts)




```

```{r echo=FALSE, eval=FALSE}
reading_change <- table(reading_q2q1$reading_pt_diff, reading_q2q1$reading_pts2)

reading_change <- table(reading_q2q1$reading_pt_diff, reading_q2q1$reading_pts2)


reading_change_1 <- with(reading_q2q1, table(reading_pts2 >=2, reading_pt_diff >=0))
pander(reading_change_1)



```






### Reading Success: % of Students that increased Grade or maintained a C 
```{r echo=FALSE}
reading_outcome <- function(){
    reading_dat <-filter(reading_q2q1,reading_pts2 >=2, reading_pt_diff >=0)
    reading_dat <-  nrow(reading_dat) /nrow(reading_q2q1) 
    reading_dat <- round(reading_dat*100,2)
    pander(reading_dat)
}

pander(reading_outcome())
```

### Reading Stats

```{r echo=FALSE}

#with(reading_q2q1,table(reading_pts))

#with(reading_q2q1,table(reading_pts2))


gpa_reading_1 <- mean(reading_q2q1$reading_pts)
#hist(reading_q2q1$reading_pts)
gpa_reading_2 <- mean(reading_q2q1$reading_pts2)
#hist(reading_q2q1$reading_pts2)

#reading_gpa_change <- (gpa_reading_2 - gpa_reading_1)

#reading_gpa_change

mean(reading_q2q1$reading_pt_diff)

```



```{r echo=FALSE}
###Change name for plots


colnames (reading_q2q1) [2] <- "council"
colnames (reading_q2q1) [3] <- "Q1_Grade"
colnames (reading_q2q1) [4] <- "Q2_Grade"
colnames (reading_q2q1) [5] <- "Grade_Change"


```


### Reading Grades Plots

```{r}

reading_grades_q1 <- ggplot(reading_q2q1,(aes(x = Q1_Grade, y = council)))

reading_grades_q1 + geom_count()

reading_grades_q2 <- ggplot(reading_q2q1,(aes(x = Q2_Grade, y = council)))

reading_grades_q2 + geom_count()


```




### Reading Grade Change from Q1 to Q2 

```{r echo=FALSE}


#reading_change_plot <- ggplot(reading_q2q1,(aes(x = Grade_Change, y = council)))

#reading_change_plot + geom_count()


reading_change_plot2 <- ggplot(reading_q2q1,(aes(x = Grade_Change, y = Q1_Grade)))

reading_change_plot2 + geom_count()


#plot(reading_change, col="Red")

#reading_dat <-filter(reading_q2q1,reading_pts2 >=2, reading_pt_diff >=0)

  
```










# Language Arts Grades--
## Join Q1 and Q2 Language Arts Grades

```{r echo=FALSE}

langarts <- inner_join(q1_langarts, q2_langarts, by="girlCode")

dim(langarts)

langarts_1 <- langarts %>%
    select(girlCode, council.x, lang_pts, lang_pts2)

langarts_q2q1 <- langarts_1 %>%
    mutate(pt_diff = lang_pts2 - lang_pts)



```


### Language Arts Grade Change

```{r echo=FALSE, eval=FALSE}
lang_change <- with(langarts_q2q1, table(pt_diff, lang_pts2))

pander(lang_change)

lang_change_1 <- with(langarts_q2q1, table(lang_pts2 >=2, pt_diff >=0))

pander(lang_change_1)


plot(lang_change)

```

### Lang Grade Success Function
```{r echo=FALSE}
lang_success <- function() {
    lang_dat <- filter(langarts_q2q1, lang_pts2 >=2, pt_diff >=0)
    lang_dat <- nrow(lang_dat)/nrow(langarts_q2q1)
    lang_dat <- round(lang_dat*100,2)
    pander(lang_dat)
}

lang_success()
```




### Lang Arts Grade Stats
```{r echo=FALSE}


mean(langarts_q2q1$pt_diff)

```


# Absences 
## Join Absence data from Q1 and Q2
```{r echo=FALSE}

absences <- inner_join(q1_absences, q2_absences, by="girlCode")



absences_1 <- absences %>%
    select(girlCode, council.x.x, sum_abs.x, sum_abs.y) 
    
absences_q2q1 <- absences_1 %>%
    mutate(abs_diff = sum_abs.y - sum_abs.x)





```

### Absences Change
```{r echo=FALSE, eval=FALSE}

absences_change <- with(absences_q2q1, table(abs_diff,sum_abs.y))

pander(absences_change)

absences_change_1 <-with(absences_q2q1,table(abs_diff <0))

absences_change_2 <-with(absences_q2q1,table(abs_diff ==0, sum_abs.y == 0))

absences_change_3 <-with(absences_q2q1,table(sum_abs.x == 0, sum_abs.y == 0))

pander(absences_change_2)

pander(absences_change_3)


pander(absences_change_1)

plot(absences_change)

```

### Absences Success Function 
```{r echo=FALSE}

absences_success <- function() {
    no_absences <- filter(absences_q2q1, abs_diff == 0, sum_abs.y ==0)
    decrease_abs <- filter(absences_q2q1, abs_diff<0 )
    abs_total <- nrow(no_absences) + nrow(decrease_abs)
    abs_total <- abs_total / nrow(absences_q2q1)
    abs_total
    
}



absences_success()
```


#Suspensions
## Merge Suspensions Q1 and Q2 Data. 

```{r echo=FALSE}

suspsensions <- inner_join(q1_suspensions, q2_suspensions, by="girlCode")


head(suspsensions)

suspsensions_1 <- suspsensions %>%
    select(girlCode, council.y.x, susp_sum.x, susp_sum.y)

suspensions_q2q1 <- suspsensions_1 %>%
    mutate(susp_diff = susp_sum.y - susp_sum.x)


dim(suspensions_q2q1)

```


### Suspensions Changes

```{r echo=FALSE}

suspensions_change <- with(suspensions_q2q1,table(susp_diff, susp_sum.y))

pander(suspensions_change)

suspensions_change_1 <- with(suspensions_q2q1,table(susp_diff < 0))

pander(suspensions_change_1)


suspensions_change_2 <- with(suspensions_q2q1,table(susp_diff ==0, susp_sum.y==0))

pander(suspensions_change_2)




plot(suspensions_change)
```

### Suspensions Outcome Function
```{r echo=FALSE}
suspensions_success <- function() {
    no_suspensions <- filter(suspensions_q2q1, susp_sum.x == 0, susp_sum.y == 0)
    decrease_suspensions <- filter(suspensions_q2q1, susp_diff <0)
    total_suspensions <- nrow(no_suspensions) + nrow(decrease_suspensions)
    total_suspensions <- total_suspensions/nrow(suspensions_q2q1)
    total_suspensions <- round(total_suspensions*100,2)
    pander(total_suspensions)
}

suspensions_success()
```

```{r echo=FALSE}
setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data")

getRealdb<- dbConnect(SQLite(), dbname="data_Final_GetReal_2014_2015.sqlite")


```




# Time Series Data

## Lang Arts 

```{r echo=FALSE}
q4_lang_2014 <- dbReadTable(getRealdb, "q4_langarts")

q2_lang_2016 <-dbReadTable(getReal_2016db, "Q2_lang")

lang <- inner_join(q4_lang_2014, q2_lang_2016, by="girlCode")

dim(lang)

head(lang)


lang$value <-as.numeric(lang$value)

mean(lang$value)
mean(lang$lang_pts2)


langarts_q4q2 <- lang %>%
    mutate(pt_diff = lang_pts2 - value)

langarts_q4q2 %>%
select(girlCode, lang_pts2, value, pt_diff)




mean(langarts_q4q2$pt_diff)

plot(langarts_q4q2$pt_diff)

with(langarts_q4q2,table(pt_diff))

with(langarts_q4q2,table(lang_pts2 >=2, pt_diff >=0))

```


```{r echo=FALSE}

q4_reading_2014 <-dbReadTable(getRealdb, "q4_reading")

q4_reading_2014 <- na.omit(q4_reading_2014)

q2_reading_2016 <-dbReadTable(getReal_2016db, "Q2_reading")

reading <- inner_join(q4_reading_2014, q2_reading_2016, by="girlCode")

dim(reading)

head(reading)



reading_q4q2 <- reading %>%
    mutate(pt_diff = reading_pts2 - value)
reading_q4q2 %>%
select(girlCode, reading_pts2, value, pt_diff)


with(reading_q4q2,table(pt_diff))

with(reading_q4q2,table(reading_pts2 >=2, pt_diff >=0))


