---
title: "healthy_relationships"
author: "Kevin Gilds, MPA"
date: "May 28, 2016"
output: html_document
---


```{r import libaries, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(pander)
library(ggplot2)
library(sqldf)
library(psych)
library(knitr)
library(gridExtra)
library(effsize)

setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")


### Make connection with database
getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")




```


```{r load outcome surveys 2016, echo=FALSE}

### Reade the girl_pre_survey database for analysis. 
pre_outcomes <- dbReadTable(getReal_2016db, "girl_pre")

post_outcomes <- dbReadTable(getReal_2016db, "girl_post")

post_outcomes <- select(post_outcomes, girlCode, council, hr.avg)
###Select the variables of interest from the pre_survey
pre_outcomes <- select(pre_outcomes, girlCode, council, hr.avg)

history <- dbReadTable(getReal_2016db, "basic_view")


```


```{r read 2014 data, echo=FALSE}
setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data")

getReal_2014db<- dbConnect(SQLite(), dbname="data_Final_GetReal_2014_2015.sqlite")

prepost2014 <- dbReadTable(getReal_2014db, "girl_pre_post_matched")

hr_prepost2014 <- prepost2014 %>%
    select(girlCode, council.x, hr.avg.x, hr.avg.y)


colnames (hr_prepost2014) [2] <- "council"
colnames (hr_prepost2014) [3] <- "Post"
colnames (hr_prepost2014) [4] <- "Pre"

hr_prepost2014 <- hr_prepost2014 %>%
    mutate("hr.diff" = Post -Pre) %>%
    mutate("Year_Id" = "M2")



hr_prepost2014 <- hr_prepost2014[, c(6,2,1,3,4,5)]



```




```{r connect_2013_hr_data, echo=FALSE}
pre_outcomes2013 <- dbReadTable(getReal_2016db, "girl_pre2013")

post_outcomes2013 <-dbReadTable(getReal_2016db, "girl_post2013")

hr_pre2013 <- pre_outcomes2013 %>%
    select(girlScoutCouncil, girlCode, hr_avg)


hr_post2013 <- post_outcomes2013 %>%
    select(girlScoutCouncil, girlCode, hr_avg)


```



```{r join_2013_hr_data, echo=FALSE}

hr_prepost2013 <- inner_join(hr_pre2013, hr_post2013, by="girlCode")



colnames(hr_prepost2013) [1] <- "council"
colnames(hr_prepost2013) [3] <- "Pre"
colnames(hr_prepost2013) [5]<- "Post"
    
hr_prepost2013 <- hr_prepost2013 %>%
    select(council, girlCode, Pre, Post)

hr_prepost2013 <- hr_prepost2013 %>%
    mutate(Year_Id = "M1")


hr_prepost2013 <- hr_prepost2013 %>%
    mutate(hr.diff = Post- Pre)

```


`






```{r prep2015 data,echo=FALSE}

healthy_prepost <- inner_join(pre_outcomes, post_outcomes, by="girlCode")


colnames(healthy_prepost) [2] <- "council"
colnames(healthy_prepost) [3] <- "Pre"
colnames(healthy_prepost) [5] <- "Post"



healthy_prepost <-healthy_prepost %>%
    mutate(Year_Id = "M3")

healthy_prepost <- healthy_prepost %>%
    mutate(hr.diff = Post - Pre)





```







```{r echo=FALSE}



healthy_prepost <- healthy_prepost %>%
    select(girlCode, council, Pre, Post,Year_Id, hr.diff)


healthy_prepost <- healthy_prepost[,c(5,2, 1,3,4,6)]


hr_prepost2013 <- hr_prepost2013[,c(5,1,2,3,4,6)]



hr_all <-rbind(healthy_prepost, hr_prepost2013)

hr_all <- rbind(hr_all, hr_prepost2014)





hr_all$council <-sub("Girl Scouts of the Gateway Council Inc", "Gateway Council", fixed=TRUE, hr_all$council)




```

```{r test_tables, echo=FALSE, eval=TRUE}

hr_high_df <- hr_all %>%
    filter(Year_Id == "M3" & Post >=4.45)

hr_high <- with(hr_all,table(Year_Id,Post >=4.45))



hr_high_p <- prop.table(hr_high,1)

pander(hr_high_p)


hr_not_achieved <- filter(hr_all, Year_Id == "M3" & Post < 4.45)

#pander(hr_increase_df)

hr_increase_df <- filter(hr_not_achieved, Year_Id == "M3" & hr.diff >0)

hr_increase_tbl <-with(hr_increase_df, table(Year_Id, hr.diff > 0 ))

#hr_increase

hr_increase <- prop.table(hr_increase_tbl,1)

pander(hr_increase)


hr_lowhigh <- filter(hr_all, Pre < 4.45 & Post >=4.45)

nrow(hr_lowhigh)

table(hr_lowhigh$Year_Id)

#head(hr_lowhigh)

hr_imrove <- with(hr_lowhigh, table(Year_Id, Post >=4.45))


hr_imrove <- prop.table(hr_imrove,1)

pander(hr_imrove)


```




```{r data_frame, echo=FALSE}
hr_df <- function (df) {
    if (df == "healthy_prepost"){
        dat1 <- healthy_prepost
} else if (df == "hr_prepost2013"){
        dat1 <-hr_prepost2013 
} else (df == "hr_prepost2014")
            data1 <-hr_prepost2014
        
    high <- filter (dat1, Post >=4.45)
    increase <-filter(dat1, Post < 4.45 & hr.diff >0)
    hr_temp <- nrow(high) + nrow(increase)
    hr_temp_1 <- hr_temp/nrow(dat1)
    hr_temp_1 <- round(hr_temp_1*100,2)
    hr_temp_1 <- paste0(hr_temp_1,"%", sep="")
    pander(hr_temp_1)

    
}



```


```{r achieved_function, echo=FALSE}

hr_achieved <- function(Year) {
    
    if(Year =="M3"){
        dat <-filter(hr_all, Year_Id =="M3")
        
    } else if(Year == "M1"){
        dat <- filter(hr_all, Year_Id =="M1")
    } else { (Year == "M2")
    dat <- filter(hr_all, Year_Id == "M2")
    }
    
    
    high <- filter(dat, Post >=4.45)
    hr_temp_1 <- nrow(high)/nrow(dat)
    hr_temp_1 <- round(hr_temp_1*100,2)
    hr_temp_1 <- paste0(hr_temp_1,"%", sep="")
    pander(hr_temp_1)
    
}

```





```{r success_function, echo=FALSE}
hr_sucess <-function(Year){
    
    if(Year =="M3"){
        dat <-filter(hr_all, Year_Id =="M3")
        
    } else if(Year == "M1"){
        dat <- filter(hr_all, Year_Id =="M1")
    } else { (Year == "M2")
    dat <- filter(hr_all, Year_Id == "M2")
    }
    
    
    high <- filter(dat, Post >=4.45)
    increase <-filter(dat, Post < 4.45 & hr.diff >0)
    hr_temp <- nrow(high) + nrow(increase)
    hr_temp_1 <- hr_temp/nrow(dat)
    hr_temp_1 <- round(hr_temp_1*100,2)
    hr_temp_1 <- paste0(hr_temp_1,"%", sep="")
    pander(hr_temp_1)
    

}



```










```{r low to high,  echo=FALSE}
hr_lowHigh <-function (Year){
    if(Year =="M3"){
        dat <-filter(hr_all, Year_Id =="M3")
        
    } else if(Year == "M1"){
        dat <- filter(hr_all, Year_Id =="M1")
    } else { (Year == "M2")
    dat <- filter(hr_all, Year_Id == "M2")
    }
    
    
    low <- filter(dat, Pre < 4.45 & Post >=4.45)
    low_1 <- nrow(low)/nrow(dat)
    hr_low_1 <- round(low_1*100,2)
    hr_low_1 <- paste0(hr_low_1, "%", sep="")
    pander(hr_low_1)
}


```






## Healthy Relationship Outcome 

Relationship skils are a critical component of success in all realms of life. 
The Healthy Relationship questions measures the behaviors and attitudes of the respondent regarding their relationship skills. Questions that measure healthy relationships skills include the following:


*Healthy Relationship Questions*

1. If I have a serious problem, I have people to talk with.
2. I let people know if they have hurt my feelings.
3. I let my friends know when I think they are good at something.
4. In any relationship - romantic or not - I make it clear when I don't feel comfortable.


The number of pre and post survey that could be matched is **`r nrow(healthy_prepost)`**.
The number and percent of students achieving the health relationship outcome at a high level or increased score is  **`r hr_sucess("M3")`**

The number of students who achieved at a high level is **`r nrow(hr_high_df)`**.
The number of studens who did not achieve at high level but increased outcome socre **`r nrow(hr_increase_df)`**

The percent of students achieving at a high level is **`r hr_achieved("M3")`**. The improvement in outcome scores is graphically represented below. 





```{r}
pre_hr_histq <- qplot(healthy_prepost$Pre, geom="histogram", main= "Pre Survey", bins=40, xlab="Outcome Scores", bins=40) + geom_vline(xintercept = 4.45, col="red") 


post_hr_histq <-qplot(healthy_prepost$Post, geom="histogram", main= "Post Survey", bins=40, xlab="Outcome Scores", ylim=c(0,40)) + geom_vline(xintercept = 4.45, col="red")

grid.arrange(pre_hr_histq, post_hr_histq, ncol=2)


```



```{r}
hr_bar_pre <-qplot(healthy_prepost$Pre >=4.45, geom="bar", ylim=c(0, 200), main="Pre survey Results", xlab="Achievment at High Level")

hr_bar_post <-qplot(healthy_prepost$Post >=4.45, geom ="bar", main="Post Survey Results", xlab="Achievment at High Level")

grid.arrange(hr_bar_pre, hr_bar_post, ncol=2)


```

```{r}
healthy_change <- filter(healthy_prepost, Pre !=6.0 & Post !=6.0)


```



The percent of students who went from low achievment to high achievement **`r hr_lowHigh("M3")`**. The number of students who had the opportunity to improve their healthy relationship outcome score is **`r nrow(healthy_change)`**, and the mean increase in outcome score is **`r mean(healthy_change$hr.diff)`**

The increase in the healthy relationship outcome scores is represented graphically below. Marks to the right of the veticial red line represents an increase in the outcome score. Marks above the horizintal line represents scores above the high and low achievement. 


```{r function_test, echo=FALSE, eval=FALSE}

high <-filter(healthy_prepost, Post >=4.45)

high <- nrow(high)

high


low_increase <-filter(healthy_prepost, Post < 4.45 & hr.diff >0)

head(low_increase)
tail(low_increase)
nrow(low_increase)

low_increase <-nrow(low_increase)

hr_success <- (high + low_increase)/nrow(healthy_prepost)

pander(hr_success)


not_pre <-filter(healthy_prepost, Pre <4.45 & Post >=4.45)

not_pre

not_pre <-nrow(not_pre)/nrow(healthy_prepost)

pander(not_pre)

```





```{r}


mean(healthy_change$hr.diff)

healthy_change_p <- ggplot(healthy_change,(aes(x=hr.diff, y=Pre)))
healthy_change_p + geom_count() + geom_hline(yintercept = 4.45) + geom_vline(xintercept = 0, col="red") + labs(x="Pre and Post Difference", y="Pre Outcome Score", title="Healthy Releationship Survey Results")



```

A wilcox.test was administered on the healthy relationship outcome data and the results show that the 

```{r}
pander(wilcox.test(healthy_change$Pre, healthy_change$Post))

```


```{r}
cohen.d(healthy_prepost$Post, healthy_prepost$Pre, paired=TRUE)

```










```{r lastyeardata, echo=FALSE}

setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data")
getRealdb<- dbConnect(SQLite(), dbname="data_Final_GetReal_2014_2015.sqlite")

pre_survey_2014 <- dbReadTable(getRealdb, "pre_girl_survey")


post_survey_MY1415 <- dbReadTable(getRealdb, "post_girl_survey")


```





```{r echo=FALSE, eval=FALSE}

### Match Pre Surveys

pre_merge <- inner_join (pre_survey_2014, pre_outcomes, by = "girlCode", Copy=FALSE)



#x=2014, y=2015


```





```{r echo=FALSE, eval=FALSE}

post_merge <- inner_join(post_survey_MY1415, pre_outcomes, by = "girlCode", Copy=FALSE)

non_match <- anti_join(pre_outcomes, post_survey_MY1415, by = "girlCode", Copy = FALSE)


```







```{r hr_function, echo=FALSE, eval=FALSE}

hr <- function(){
    hr_tbl <- with(pre_outcomes,table(hr.avg >=4.45))
    pander(hr_tbl)
    
}
```







```{r hr_percent, echo=FALSE, eval=FALSE}

hr_percent <- function() {
    hr_tbl <- filter(pre_outcomes, hr.avg >=4.45)
    hr_tbl_p <- nrow(hr_tbl) /nrow(pre_outcomes)
    hr_tbl_p <- round(hr_tbl_p*100,2)
    pander(paste(hr_tbl_p, "%", sep=""))
}


```


```{r hr outcome tables, echo=FALSE, eval=FALSE}
### create basic outcome table for healty releationship outcome

hr_tbl <- with(pre_outcomes,table(hr.avg >=4.45))

### print in pretty table
pander(hr_tbl)

### Put percents with outcome table
hr_tbl_p <- prop.table(hr_tbl)


###Print percent table
pander(hr_tbl_p)

### Basic outcome table for healthy relationships by council
hr_tbl_c <- with(pre_outcomes, table(council, hr.avg >=4.45))

### print results of outcome table
pander(hr_tbl_c)


####Percent by council

hr_tbl_cp <- prop.table(hr_tbl_c, 1)

### Print by percent
pander(hr_tbl_cp)


```




```{r  echo=FALSE, message=FALSE, fig.width=15, eval=FALSE}

### Plot outcome results by council     
pre_hr_hist<-ggplot(healthy_prepost, aes(x=Pre))
     
pre_hr_hist   + geom_histogram(fill="blue") + labs(x=" All Outcome Scores", title = "Pre: Healthy Relationships")
        

post_hr_hist <- ggplot(healthy_prepost, aes(x=Post))

post_hr_hist + geom_histogram(fill="blue")  + labs(x="All Outcome Scores", title = "Post: Healthy Relationships")


grid.arrange(pre_hr_hist, post_hr_hist, ncol=2)


```








```{r hr_barchart, fig.width=15, echo=FALSE, eval=FALSE}
### Plot outcome results
hr <- select(pre_outcomes, council, hr.avg)
ggplot(hr, aes(hr.avg >=4.45)) + geom_bar(fill="blue", width = .5) + labs(x="Achieving at High Level", title = "Pre: Healthy Relationships")


```




```{r hr_hist2, echo=FALSE, eval=FALSE, message=FALSE}

### Plot outcome results by council    
hr_hist <- ggplot(hr, aes(x=hr.avg))
        hr_hist + geom_histogram(fill="blue") +facet_grid(~council) + labs(x=" All Outcome Scores", title = "Pre: Healthy Relationships")

```




### Healthy Relationships Outcome Distribution , Plots
```{r hr_hist, echo=FALSE, eval=FALSE}
### Histogram to show all the outcome scores
### Abline for ggplot
 hr_hist <- ggplot(hr, aes(x=hr.avg)) 
        hr_hist + geom_histogram(fill="blue", bins=40) + labs(x=" All Outcome Scores", title = "Pre: Healthy Relationships")



        

```


```{r hr_boxplot, echo=FALSE, eval=FALSE}

### Box plot for outcome scores
        
hr_box <- ggplot(hr, aes(x=factor(council), hr.avg))
        hr_box + geom_boxplot(fill="blue") + labs(y=" All Outcome Scores", title = "Pre: Healthy Relationships")


```



```{r hr_descrip, echo=FALSE, eval=FALSE}
## Try x-table, or kable

### Prepare data frame for just looking at hr.avg        
hr_1 <- select(hr, hr.avg)

### Stat summary of df.
hr_des <- describe(hr_1)

kable(hr_des)
        
```



```{r echo=FALSE, eval=FALSE}


hr_history <-
    select(history, Year,population, mean, sd, achieved, outcome.1) 

hr_history <-
    filter(hr_history, outcome.1 == "Healthy Relationships"& Year !="2015")


percent_achieved <- hr_history$achieved / hr_history$population

percent_achieved <- round(percent_achieved*100, 2)

percent_achieved <- paste0(percent_achieved, "%")

hr_history <- cbind(hr_history, percent_achieved)

hr_history <- select(hr_history, Year, population, mean, sd, percent_achieved)

colnames(hr_history)[5] <-"percent achieved"

hr_Year <- "2015"
hr_population <- nrow(pre_outcomes)
hr_mean <- mean(pre_outcomes$hr.avg)
hr_sd <-sd(pre_outcomes$hr.avg)
hr_achieved1 <- filter(pre_outcomes, hr.avg >=4.45)
hr_achieved <- nrow(hr_achieved1)/nrow(pre_outcomes)
hr_percent1 <- round(hr_achieved*100,2)
hr_percent <- paste0(hr_percent1, "%")


hr_df <- data.frame(hr_Year, hr_population, hr_mean, hr_sd, hr_percent )
 
colnames(hr_df)[1] <-"Year"
colnames(hr_df)[2] <- "population"
colnames(hr_df)[3] <- "mean"
colnames(hr_df)[4] <- "sd"
colnames(hr_df)[5] <- "percent achieved"


hr_history <- rbind(hr_history, hr_df)
pander(hr_history)

```





 
```{r echo=FALSE, eval=FALSE}

post_merge_hr_pre <- mean(post_merge$hr.avg.y)


post_merge_hr_post <-mean(post_merge$hr.avg.x)

non_match_hr_pre <- mean(non_match$hr.avg)






```





```{r echo=FALSE, eval=FALSE}

hr_population_pre <- "Matched: Pre 2015-2016"
hr_mean_pre <- mean(post_merge$hr.avg.y)
hr_sd_pre <- sd(post_merge$hr.avg.y)
hr_achieved_1 <- filter(post_merge, hr.avg.y >= 4.45)
hr_achieved <- nrow(hr_achieved_1)
hr_percent_1 <- nrow(hr_achieved_1)/nrow(post_merge)
hr_percent_1 <- round(hr_percent_1*100,2)
hr_percent <- paste0(hr_percent_1, "%", sep= " ")


hr_trend_pre<-data.frame(hr_population_pre, hr_mean_pre, hr_sd_pre, hr_achieved, hr_percent)

colnames(hr_trend_pre)[1] <- "Time"
colnames(hr_trend_pre)[2] <- "Mean"
colnames(hr_trend_pre)[3] <- "SD"
colnames(hr_trend_pre)[4] <- "Achieved"
colnames(hr_trend_pre)[5] <- "Percent Achieved"



```




```{r echo=FALSE, eval=FALSE}

hr_time_post <-
hr_Population_post <- "Matched: Post 2014-2015"
hr_mean_post <- mean(post_merge$hr.avg.x)
hr_sd_post <- sd(post_merge$hr.avg.x)
hr_achieved_1post <- filter(post_merge, hr.avg.x >=4.45)
hr_achieved_post <- nrow(hr_achieved_1post)
hr_percent_post1 <- nrow(hr_achieved_1post)/nrow(post_merge)
hr_percent_post <- round(hr_percent_post1*100,2)
hr_percent_post <- paste0(hr_percent_post, "%")

hr_trend_post <- data.frame(hr_Population_post, hr_mean_post, hr_sd_post, hr_achieved_post, hr_percent_post)


colnames(hr_trend_post)[1] <- "Time"
colnames(hr_trend_post)[2] <- "Mean"
colnames(hr_trend_post)[3] <- "SD"
colnames(hr_trend_post)[4] <- "Achieved"
colnames(hr_trend_post)[5] <- "Percent Achieved"





```



```{r echo=FALSE, eval=FALSE}
hr_Population_non <- "Non-Matched: Pre 2015-2016"
hr_mean_non <- mean(non_match$hr.avg)
hr_sd_non <- sd(non_match$hr.avg)
hr_achieved_1non <- filter(non_match, hr.avg >=4.45)
hr_achieved_non <- nrow(hr_achieved_1non)
hr_percent_non1 <- nrow(hr_achieved_1non)/nrow(non_match)
hr_percent_non <- round(hr_percent_non1*100,2)
hr_percent_non <- paste0(hr_percent_non, "%")

hr_trend_non <- data.frame(hr_Population_non, hr_mean_non, hr_sd_non, hr_achieved_non, hr_percent_non)



colnames(hr_trend_non)[1] <- "Time"
colnames(hr_trend_non)[2] <- "Mean"
colnames(hr_trend_non)[3] <- "SD"
colnames(hr_trend_non)[4] <- "Achieved"
colnames(hr_trend_non)[5] <- "Percent Achieved"




```

```{r echo=FALSE, eval=FALSE}

population1<- nrow(post_merge)

population2 <- nrow(post_merge)

population3 <- nrow(non_match)

population4 <- data.frame(population1, population2, population3)



hr_trend_1 <- rbind(hr_trend_post, hr_trend_pre)

hr_trend <- rbind(hr_trend_1, hr_trend_non)







pander(hr_trend)

```






```{r echo=FALSE, eval=FALSE}

kable(post_merge_hr_pre)
kable(post_merge_hr_post)

```







```{r echo= FALSE, eval=FALSE}

hr_outcome_pre_2015 <- with(post_merge,table(hr.avg.y >=4.45))



pander(hr_outcome_pre_2015)

hr_outcome_post_2014 <- with(post_merge,table(hr.avg.x >=4.45))

pander(hr_outcome_post_2014)

non_match_outcome <-with(non_match,table(hr.avg >=4.45))

pander(non_match_outcome)


wilcox.test(post_merge$hr.avg.y, post_merge$hr.avg.x)

wilcox.test(post_merge$hr.avg.y, non_match$hr.avg)

```





