---
title: "healthy_relationships"
author: "Kevin Gilds, MPA"
date: "May 28, 2016"
output: html_document
---


```{r import libaries, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(pander)
library(ggplot2)
library(sqldf)
library(psych)
library(knitr)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")


### Make connection with database
getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")




```


```{r load outcome survesy, echo=FALSE}

### Reade the girl_pre_survey database for analysis. 
pre_outcomes <- dbReadTable(getReal_2016db, "girl_pre")

post_outcomes <- dbReadTable(getReal_2016db, "girl_post")

post_outcomes <- select(post_outcomes, girlCode, council, hr.avg)
###Select the variables of interest from the pre_survey
pre_outcomes <- select(pre_outcomes, girlCode, council, hr.avg)

history <- dbReadTable(getReal_2016db, "basic_view")


```



```{r}
pre_outcomes2013 <- dbReadTable(getReal_2016db, "girl_pre2013")

post_outcomes2013 <-dbReadTable(getReal_2016db, "girl_post2013")

hr_pre2013 <- pre_outcomes2013 %>%
    select(girlScoutCouncil, girlCode, hr_avg)


hr_post2013 <- post_outcomes2013 %>%
    select(girlScoutCouncil, girlCode, hr_avg)


```



```{r}

hr_prepost2013 <- inner_join(hr_pre2013, hr_post2013, by="girlCode")
dim(hr_prepost2013)

names(hr_prepost2013)

colnames(hr_prepost2013) [1] <- "council"
colnames(hr_prepost2013) [3] <- "Pre"
colnames(hr_prepost2013) [5]<- "Post"
    
hr_prepost2013 <- hr_prepost2013 %>%
    select(council, girlCode, Pre, Post)

hr_prepost2013 <- hr_prepost2013 %>%
    mutate(Year_Id = "M1")


hr_prepost2013 <- hr_prepost2013 %>%
    mutate(hr.diff = Post- Pre)

```


```{r}

fun_test_1 <- with(hr_prepost2013,table(Post >=4.45))

fun_test_1

fun_test_2 <-with(hr_prepost2013,table(Post < 4.45 & hr.diff >0))

fun_test_2

```





```{r}
healthy_prepost <- inner_join(pre_outcomes, post_outcomes, by="girlCode")

dim(healthy_prepost)


```

```{r}
head(healthy_prepost)

names(healthy_prepost)

colnames(healthy_prepost) [2] <- "council"
colnames(healthy_prepost) [3] <- "Pre"
colnames(healthy_prepost) [5] <- "Post"

names(healthy_prepost)

healthy_prepost <-healthy_prepost %>%
    mutate(Year_Id = "M3")

healthy_prepost <- healthy_prepost %>%
    mutate(hr.diff = Post - Pre)



str(healthy_prepost)


with(healthy_prepost,table(Post >=4.45))
hist(healthy_prepost$hr.diff)

mean(healthy_prepost$hr.diff)


hr_achieved <-filter(healthy_prepost, Post >=4.45 )

plot(healthy_prepost$hr.diff)
abline(h=0, col="red")









```







```{r}

names(healthy_prepost)

healthy_prepost <- healthy_prepost %>%
    select(girlCode, council, Pre, Post,Year_Id, hr.diff)


healthy_prepost <- healthy_prepost[,c(5,2, 1,3,4,6)]

names(healthy_prepost)

names(hr_prepost2013)

hr_prepost2013 <- hr_prepost2013[,c(5,1,2,3,4,6)]

names(hr_prepost2013)

hr_all <-rbind(healthy_prepost, hr_prepost2013)

```


```{r}
hr_df <- function (df) {
    if (df == "healthy_prepost"){
        dat1 <- healthy_prepost
} else if (df == "hr_prepost2013")
        dat1 <-hr_prepost2013
    high <- filter (dat1, Post >=4.45)
    increase <-filter(dat1, Post < 4.45 & hr.diff >0)
    hr_temp <- nrow(high) + nrow(increase)
    hr_temp_1 <- hr_temp/nrow(dat1)
    hr_temp_1 <- round(hr_temp_1*100,2)
    hr_temp_1 <- paste0(hr_temp_1,"%", sep="")
    pander(hr_temp_1)

    
}

hr_df("healthy_prepost")






```{r}
hr_match_test <-function(Year){
    
    if(Year =="M3"){
        dat <-filter(hr_all, Year_Id =="M3")
        
    } else if(Year == "M1")
        dat <- filter(hr_all, Year_Id =="M1")

    
    high <- filter(dat, Post >=4.45)
    increase <-filter(dat, Post < 4.45 & hr.diff >0)
    hr_temp <- nrow(high) + nrow(increase)
    hr_temp_1 <- hr_temp/nrow(dat)
    hr_temp_1 <- round(hr_temp_1*100,2)
    hr_temp_1 <- paste0(hr_temp_1,"%", sep="")
    pander(hr_temp_1)

}

hr_match_test("M3")
```

```







```{r}
hr_match <-function(){
    high <- filter(healthy_prepost, Post >=4.45)
    increase <-filter(healthy_prepost, Post < 4.45 & hr.diff >0)
    hr_temp <- nrow(high) + nrow(increase)
    hr_temp_1 <- hr_temp/nrow(healthy_prepost)
    hr_temp_1 <- round(hr_temp_1*100,2)
    hr_temp_1 <- paste0(hr_temp_1,"%", sep="")
    pander(hr_temp_1)

}

hr_match()
```


```{r}
hr_lowHigh <-function (){
    low <- filter(healthy_prepost, Pre < 4.45 & Post >=4.45)
    low_1 <- nrow(low)/nrow(healthy_prepost)
    hr_low_1 <- round(low_1*100,2)
    hr_low_1 <- paste0(hr_low_1, "%", sep="")
    pander(hr_low_1)
}

hr_lowHigh()

```

The Healthy Relationship questions measures the behaviors and attitudes of the respondent regarding their relationship skills. 




The number of valid survey entries is **`r nrow(healthy_prepost)`**.
The percent of students achieving this outcome at a high level is **`r hr_match()`**.



```{r}

high <-filter(healthy_prepost, Post >=4.45)

high <- nrow(high)


low_increase <-filter(healthy_prepost, Post < 4.45 & hr.diff >0)

head(low_increase)
tail(low_increase)
nrow(low_increase)

low_increase <-nrow(low_increase)

hr_success <- (high + low_increase)/nrow(healthy_prepost)

pander(hr_success)


not_pre <-filter(healthy_prepost, Pre <4.45 & Post >=4.45)

not_pre

not_pre <-nrow(not_pre)/nrow(healthy_prepost)

pander(not_pre)

```








```{r lastyeardata, echo=FALSE}

setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data")
getRealdb<- dbConnect(SQLite(), dbname="data_Final_GetReal_2014_2015.sqlite")

pre_survey_2014 <- dbReadTable(getRealdb, "pre_girl_survey")


post_survey_MY1415 <- dbReadTable(getRealdb, "post_girl_survey")


```





```{r echo=FALSE}

### Match Pre Surveys

pre_merge <- inner_join (pre_survey_2014, pre_outcomes, by = "girlCode", Copy=FALSE)



#x=2014, y=2015


```





```{r echo=FALSE}

post_merge <- inner_join(post_survey_MY1415, pre_outcomes, by = "girlCode", Copy=FALSE)

non_match <- anti_join(pre_outcomes, post_survey_MY1415, by = "girlCode", Copy = FALSE)


```




## Healthy Releationships


```{r hr_function, echo=FALSE}

hr <- function(){
    hr_tbl <- with(pre_outcomes,table(hr.avg >=4.45))
    pander(hr_tbl)
    
}
```




### Percent of students achieving at a high level




```{r hr_percent, echo=FALSE}

hr_percent <- function() {
    hr_tbl <- filter(pre_outcomes, hr.avg >=4.45)
    hr_tbl_p <- nrow(hr_tbl) /nrow(pre_outcomes)
    hr_tbl_p <- round(hr_tbl_p*100,2)
    pander(paste(hr_tbl_p, "%", sep=""))
}


```


```{r hr outcome tables, echo=FALSE, eval=FALSE}
### create basic outcome table for healty releationship outcome

hr_tbl <- with(pre_outcomes,table(hr.avg >=4.45))

### print in pretty table
pander(hr_tbl)

### Put percents with outcome table
hr_tbl_p <- prop.table(hr_tbl)


###Print percent table
pander(hr_tbl_p)

### Basic outcome table for healthy relationships by council
hr_tbl_c <- with(pre_outcomes, table(council, hr.avg >=4.45))

### print results of outcome table
pander(hr_tbl_c)


####Percent by council

hr_tbl_cp <- prop.table(hr_tbl_c, 1)

### Print by percent
pander(hr_tbl_cp)


```

### Healthy Relationship Outcome Plots
```{r hr_barchart, fig.width=15, echo=FALSE}
### Plot outcome results
hr <- select(pre_outcomes, council, hr.avg)
ggplot(hr, aes(hr.avg >=4.45)) + geom_bar(fill="blue", width = .5) + labs(x="Achieving at High Level", title = "Pre: Healthy Relationships")


```




```{r hr_hist2, echo=FALSE, eval=FALSE, message=FALSE}

### Plot outcome results by council    
hr_hist <- ggplot(hr, aes(x=hr.avg))
        hr_hist + geom_histogram(fill="blue") +facet_grid(~council) + labs(x=" All Outcome Scores", title = "Pre: Healthy Relationships")

```




### Healthy Relationships Outcome Distribution Plots
```{r hr_hist, echo=FALSE}
### Histogram to show all the outcome scores
### Abline for ggplot
 hr_hist <- ggplot(hr, aes(x=hr.avg)) 
        hr_hist + geom_histogram(fill="blue", bins=40) + labs(x=" All Outcome Scores", title = "Pre: Healthy Relationships")



        

```


```{r hr_boxplot, echo=FALSE, eval=FALSE}

### Box plot for outcome scores
        
hr_box <- ggplot(hr, aes(x=factor(council), hr.avg))
        hr_box + geom_boxplot(fill="blue") + labs(y=" All Outcome Scores", title = "Pre: Healthy Relationships")


```



```{r hr_descrip, echo=FALSE, eval=FALSE}
## Try x-table, or kable

### Prepare data frame for just looking at hr.avg        
hr_1 <- select(hr, hr.avg)

### Stat summary of df.
hr_des <- describe(hr_1)

kable(hr_des)
        
```


### Pre Survey Healthy Relationship Trends from 2013-2015

Pre survey average scores are down this year along with the proportion of students achieving the outcome at a high level. The key for this analysis is the percent of students increasing their outcome score. 

```{r echo=FALSE}


hr_history <-
    select(history, Year,population, mean, sd, achieved, outcome.1) 

hr_history <-
    filter(hr_history, outcome.1 == "Healthy Relationships"& Year !="2015")


percent_achieved <- hr_history$achieved / hr_history$population

percent_achieved <- round(percent_achieved*100, 2)

percent_achieved <- paste0(percent_achieved, "%")

hr_history <- cbind(hr_history, percent_achieved)

hr_history <- select(hr_history, Year, population, mean, sd, percent_achieved)

colnames(hr_history)[5] <-"percent achieved"

hr_Year <- "2015"
hr_population <- nrow(pre_outcomes)
hr_mean <- mean(pre_outcomes$hr.avg)
hr_sd <-sd(pre_outcomes$hr.avg)
hr_achieved1 <- filter(pre_outcomes, hr.avg >=4.45)
hr_achieved <- nrow(hr_achieved1)/nrow(pre_outcomes)
hr_percent1 <- round(hr_achieved*100,2)
hr_percent <- paste0(hr_percent1, "%")


hr_df <- data.frame(hr_Year, hr_population, hr_mean, hr_sd, hr_percent )
 
colnames(hr_df)[1] <-"Year"
colnames(hr_df)[2] <- "population"
colnames(hr_df)[3] <- "mean"
colnames(hr_df)[4] <- "sd"
colnames(hr_df)[5] <- "percent achieved"


hr_history <- rbind(hr_history, hr_df)
pander(hr_history)

```





 
```{r echo=FALSE, eval=FALSE}

post_merge_hr_pre <- mean(post_merge$hr.avg.y)


post_merge_hr_post <-mean(post_merge$hr.avg.x)

non_match_hr_pre <- mean(non_match$hr.avg)






```


### Healthy Relationship Time Series

The number of student survey records that could be matched from last year is  **`r nrow(post_merge)`**.
Last year students who participated for multiple years had higher healthy relationship scores than students who had not participated in the program before. This is not the case this year. 

Healthy Relationship scores regressed from the post survey and students in the program did not score better than students in the program in terms of average scores or proportion of students achieving the skill at a high level. 


The number of matched student is **`r nrow(post_merge)`**, and the number of non matched students is   **`r nrow(non_match)`**.




```{r echo=FALSE}

hr_population_pre <- "Matched: Pre 2015-2016"
hr_mean_pre <- mean(post_merge$hr.avg.y)
hr_sd_pre <- sd(post_merge$hr.avg.y)
hr_achieved_1 <- filter(post_merge, hr.avg.y >= 4.45)
hr_achieved <- nrow(hr_achieved_1)
hr_percent_1 <- nrow(hr_achieved_1)/nrow(post_merge)
hr_percent_1 <- round(hr_percent_1*100,2)
hr_percent <- paste0(hr_percent_1, "%", sep= " ")


hr_trend_pre<-data.frame(hr_population_pre, hr_mean_pre, hr_sd_pre, hr_achieved, hr_percent)

colnames(hr_trend_pre)[1] <- "Time"
colnames(hr_trend_pre)[2] <- "Mean"
colnames(hr_trend_pre)[3] <- "SD"
colnames(hr_trend_pre)[4] <- "Achieved"
colnames(hr_trend_pre)[5] <- "Percent Achieved"



```




```{r echo=FALSE}

hr_time_post <-
hr_Population_post <- "Matched: Post 2014-2015"
hr_mean_post <- mean(post_merge$hr.avg.x)
hr_sd_post <- sd(post_merge$hr.avg.x)
hr_achieved_1post <- filter(post_merge, hr.avg.x >=4.45)
hr_achieved_post <- nrow(hr_achieved_1post)
hr_percent_post1 <- nrow(hr_achieved_1post)/nrow(post_merge)
hr_percent_post <- round(hr_percent_post1*100,2)
hr_percent_post <- paste0(hr_percent_post, "%")

hr_trend_post <- data.frame(hr_Population_post, hr_mean_post, hr_sd_post, hr_achieved_post, hr_percent_post)


colnames(hr_trend_post)[1] <- "Time"
colnames(hr_trend_post)[2] <- "Mean"
colnames(hr_trend_post)[3] <- "SD"
colnames(hr_trend_post)[4] <- "Achieved"
colnames(hr_trend_post)[5] <- "Percent Achieved"





```



```{r echo=FALSE}
hr_Population_non <- "Non-Matched: Pre 2015-2016"
hr_mean_non <- mean(non_match$hr.avg)
hr_sd_non <- sd(non_match$hr.avg)
hr_achieved_1non <- filter(non_match, hr.avg >=4.45)
hr_achieved_non <- nrow(hr_achieved_1non)
hr_percent_non1 <- nrow(hr_achieved_1non)/nrow(non_match)
hr_percent_non <- round(hr_percent_non1*100,2)
hr_percent_non <- paste0(hr_percent_non, "%")

hr_trend_non <- data.frame(hr_Population_non, hr_mean_non, hr_sd_non, hr_achieved_non, hr_percent_non)



colnames(hr_trend_non)[1] <- "Time"
colnames(hr_trend_non)[2] <- "Mean"
colnames(hr_trend_non)[3] <- "SD"
colnames(hr_trend_non)[4] <- "Achieved"
colnames(hr_trend_non)[5] <- "Percent Achieved"




```

```{r echo=FALSE}

population1<- nrow(post_merge)

population2 <- nrow(post_merge)

population3 <- nrow(non_match)

population4 <- data.frame(population1, population2, population3)



hr_trend_1 <- rbind(hr_trend_post, hr_trend_pre)

hr_trend <- rbind(hr_trend_1, hr_trend_non)







pander(hr_trend)

```






```{r echo=FALSE, eval=FALSE}

kable(post_merge_hr_pre)
kable(post_merge_hr_post)

```







```{r echo= FALSE, eval=FALSE}

hr_outcome_pre_2015 <- with(post_merge,table(hr.avg.y >=4.45))



pander(hr_outcome_pre_2015)

hr_outcome_post_2014 <- with(post_merge,table(hr.avg.x >=4.45))

pander(hr_outcome_post_2014)

non_match_outcome <-with(non_match,table(hr.avg >=4.45))

pander(non_match_outcome)


wilcox.test(post_merge$hr.avg.y, post_merge$hr.avg.x)

wilcox.test(post_merge$hr.avg.y, non_match$hr.avg)

```





