---
title: "Language Arts"
author: "Kevin Gilds, MPA"
date: "`r Sys.Date()`"
output: html_document
---

```{r echo=FALSE, warning=FALSE, message=FALSE}


library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

library(dplyr)
library(dplyr)
library(pander)
library(ggplot2)
library (ezknitr)
library(knitr)

```




```{r echo=FALSE}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")



q1_langarts <-dbReadTable(getReal_2016db,"Q1_lang")

q2_langarts <-dbReadTable(getReal_2016db, "Q2_lang")


```

# Reading Improvement:
50% of participating students will improve their reading skills as demonstrated by their Language Arts grade increasing or maintaining a "C" grade from the baseline grading period to the final grading period as evidenced by report cards/school reports.


```{r echo=FALSE}

##join langarts grades q1q2

langarts <- inner_join(q1_langarts, q2_langarts, by="girlCode")



langarts_1 <- langarts %>%
    select(girlCode, council.x, lang_pts, lang_pts2)

langarts_q2q1 <- langarts_1 %>%
    mutate(pt_diff = lang_pts2 - lang_pts)



```




```{r echo=FALSE, eval=FALSE}
lang_change <- with(langarts_q2q1, table(pt_diff, lang_pts2))

pander(lang_change)

lang_change_1 <- with(langarts_q2q1, table(lang_pts2 >=2, pt_diff >=0))

pander(lang_change_1)


plot(lang_change)

```

### Language Arts Grade: % of Students that increased Grade or maintained a C 
```{r echo=FALSE}
lang_success <- function() {
    lang_dat <- filter(langarts_q2q1, lang_pts2 >=2, pt_diff >=0)
    lang_dat <- nrow(lang_dat)/nrow(langarts_q2q1)
    lang_dat <- round(lang_dat*100,2)
    pander(paste0(lang_dat,"%", sep= ""))
   
}


```


```{r echo=FALSE}


lang_gpa_diff<-mean(langarts_q2q1$pt_diff)

#pander(lang_gpa_diff)

```


The number of students that could be matched from Quarter 1 to Quarter 2 is **`r nrow(langarts_q2q1)`**, and the percent of students that increased their grade or maintained a C  is **`r lang_success ()`**.
The mean difference between grades is Q1 to Q2 is **`r pander(lang_gpa_diff)`**. This is an impressive increase as the average difference is not picking up students who maintain their grades. 

```{r echo=FALSE}

colnames (langarts_q2q1) [2] <- "council"
colnames (langarts_q2q1) [3] <- "Q1_Grade"
colnames (langarts_q2q1) [4] <- "Q2_Grade"
colnames (langarts_q2q1) [5] <- "Grade_Change"



```





### Language Arts Grade Change from Q1 to Q2 

```{r echo=FALSE}


#reading_change_plot <- ggplot(reading_q2q1,(aes(x = Grade_Change, y = council)))

#reading_change_plot + geom_count()


langarts_change_plot2 <- ggplot(langarts_q2q1,(aes(x = Grade_Change, y = Q1_Grade)))

langarts_change_plot2 + geom_count()


#plot(reading_change, col="Red")

#reading_dat <-filter(reading_q2q1,reading_pts2 >=2, reading_pt_diff >=0)


```




```{r echo=FALSE}
setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data")

getRealdb<- dbConnect(SQLite(), dbname="data_Final_GetReal_2014_2015.sqlite")


```

### Trend Data Q4 2015 to Q2 2016

```{r echo=FALSE, eval=TRUE}

q4_lang_2014 <- dbReadTable(getRealdb, "langarts_final_matched")

q2_lang_2016 <-dbReadTable(getReal_2016db, "Q2_lang")

lang <- inner_join(q4_lang_2014, q2_lang_2016, by="girlCode")



lang$q4Grade <-as.numeric(lang$q4Grade)




langarts_q4q2 <- lang %>%
    mutate(pt_diff = lang_pts2 - q4Grade)

langarts_q4q2 <-
select(langarts_q4q2,girlCode, council, lang_pts2,q4Grade, pt_diff)


langarts_q4q2_test <- distinct(langarts_q4q2, girlCode)



```


```{r echo=FALSE, eval=TRUE}

lang_success_m <- function() {
    lang_dat <- filter(langarts_q4q2, lang_pts2 >=2, pt_diff >=0)
    lang_dat <- nrow(lang_dat)/nrow(langarts_q4q2)
    lang_dat <- round(lang_dat*100,2)
    pander(paste0(lang_dat, "%", sep=""))
}




```




```{r echo=FALSE, eval=FALSE}

langarts_grade_m <- ggplot(langarts_q4q2,(aes(x = lang_pts2, y = council)))

langarts_grade_m + geom_count()


```








### Percent of students who increased Language Arts Grade or maintained a C grade. 
```{r echo=FALSE, eval=TRUE}
m_gpa_lang <- mean(langarts_q4q2$pt_diff)

m_gpa_lang <-pander(m_gpa_lang)



#plot(langarts_q4q2$pt_diff)

#with(langarts_q4q2,table(pt_diff))

#with(langarts_q4q2,table(lang_pts2 >=2, pt_diff >=0))



```

The number of students that could be matched from Quarter 4 to Quarter 2 is **`r nrow(langarts_q4q2)`**. 
The number of studnets that increased their grade or maintained a C is **`r lang_success_m()`**. The mean difference betwween the two quarers is **`r (m_gpa_lang)`**.


```{r echo=FALSE}


colnames (langarts_q4q2) [3] <- "Q2_Grade"
colnames (langarts_q4q2) [4] <- "Q4_Grade"
colnames (langarts_q4q2) [5] <- "Grade_Change"



```

```{r echo=FALSE, eval=FALSE}

PlusGrade_m <- langarts_q4q2 %>%
    filter(Grade_Change >=0)

PlusGrade_tbl_m  <- with(PlusGrade_m, table(Q4_Grade, Grade_Change))

PlusGrade_tbl_m





with(langarts_q4q2,table(Q2_Grade, Grade_Change))
grade_change_tbl <- with(langarts_q4q2,table(Q4_Grade, Grade_Change))

grade_change_tbl <- addmargins(grade_change_tbl)

pander(grade_change_tbl, caption="Q4 Grades and Grade Change")

```


### Plot change in Grade from Quarter 4 to Quarter 2:
```{r echo=FALSE}

langarts_change_plot_m <- ggplot(langarts_q4q2,(aes(x = Grade_Change, y = Q4_Grade)))

langarts_change_plot_m + geom_count()


```


