---
title: "Language Arts"
author: "Kevin Gilds, MPA"
date: "`r Sys.Date()`"
output: html_document
---

```{r echo=FALSE, warning=FALSE, message=FALSE}


library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

library(dplyr)
library(dplyr)
library(pander)
library(ggplot2)
library(knitr)

```




```{r echo=FALSE}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")



q1_langarts <-dbReadTable(getReal_2016db,"Q1_lang")

q2_langarts <-dbReadTable(getReal_2016db, "Q2_lang")

q3_langarts <- dbReadTable(getReal_2016db, "Q3_lang")

q4_langarts <- dbReadTable(getReal_2016db, "Q4_lang")

dim(q4_langarts)


```

# Reading Improvement:

## Objective: 

*50% of participating students will improve their reading skills as demonstrated by their Language Arts grade increasing or maintaining a "C" grade from the baseline grading period to the final grading period as evidenced by report cards/school reports.*


```{r echo=FALSE}


### join lang arts grad  q1q4

langarts_q4_q1 <- inner_join(q4_langarts, q1_langarts, by="girlCode")

dim(langarts_q4_q1)

missing_q4_q1 <- anti_join(q4_langarts, q1_langarts, by= "girlCode") #subset those without a match

langarts_q4_q2 <- inner_join(missing_q4_q1, q2_langarts, by="girlCode") #try to join unmatched with q2 to q4. 

dim(langarts_q4_q2)


dim(missing_q4_q1)

##join langarts grades q1q2

langarts <- inner_join(q1_langarts, q2_langarts, by="girlCode")





names(langarts_q4_q1)


```



```{r}
langarts_q4_q1 <- langarts_q4_q1 %>%
    select(girlCode, council.x, lang_pts, lang_pts4) #select relevant variables

langarts_q4_q2 <- langarts_q4_q2 %>%
    select(girlCode, council.x, lang_pts2, lang_pts4) #select relevant variables


colnames(langarts_q4_q1) [2] <- "council"
colnames(langarts_q4_q1) [3] <- "baseline"
colnames(langarts_q4_q1) [4] <-"final"



langarts_q4_q1 <- langarts_q4_q1 %>%
    mutate("Time" = "Q1Q4") #add variable time

langarts_q4_q2 <- langarts_q4_q2 %>%
    mutate("Time" = "Q2Q4") #add variable time

colnames(langarts_q4_q2) [2] <- "council"
colnames(langarts_q4_q2) [3] <- "baseline"
colnames(langarts_q4_q2) [4] <-"final"




```


#bind
```{r}

langarts2016 <- rbind(langarts_q4_q1, langarts_q4_q2)

dim(langarts2016)

```




```{r}
langarts2016 <- langarts2016 %>%
    select(girlCode, council, baseline, final, Time)

langarts2016 <- langarts2016 %>%
    mutate(pt_diff = final - baseline)


```





```{r echo=TRUE, eval=TRUE}
lang_change <- with(langarts2016, table(pt_diff, final))

pander(lang_change)

lang_change_1 <- with(langarts2016, table(final >=2, pt_diff >=0))

pander(lang_change_1)


plot(lang_change)

```

### Language Arts Grade: % of Students that increased Grade or maintained a C 
```{r echo=FALSE}
lang_success <- function() {
    lang_dat <- filter(langarts2016, final >=2, pt_diff >=0)
    lang_dat <- nrow(lang_dat)/nrow(langarts2016)
    lang_dat <- round(lang_dat*100,2)
    pander(paste0(lang_dat,"%", sep= ""))
   
}


```


```{r echo=FALSE}


lang_gpa_diff<-mean(langarts2016$pt_diff)

#pander(lang_gpa_diff)

```


The number of students that could be matched from Quarter 1 to Quarter 2 is **`r nrow(langarts2016)`**, and the percent of students that increased their grade or maintained a C  is **`r lang_success ()`**.
The mean difference between grades is Q1 to Q2 is **`r pander(lang_gpa_diff)`**. 

```{r echo=FALSE}


names(langarts2016)

colnames (langarts2016) [6] <- "Grade_Change"



```





### Grade Change Plot from baseline to final: 
The changes in grades from baseline to final is represented below. The vertical axis represents baseline grades and the bottom axis the change from the baseline. Thus ideally we want to see circles moving to right. Note that,students with an A in Q1 can decrease but not increase. 



```{r echo=FALSE}


#reading_change_plot <- ggplot(reading_q2q1,(aes(x = Grade_Change, y = council)))

#reading_change_plot + geom_count()


langarts_change_plot2 <- ggplot(langarts2016,(aes(x = Grade_Change, y = baseline)))

langarts_change_plot2 + geom_count()


#plot(reading_change, col="Red")

#reading_dat <-filter(reading_q2q1,reading_pts2 >=2, reading_pt_diff >=0)


```




```{r echo=FALSE}
setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data")

getRealdb<- dbConnect(SQLite(), dbname="data_Final_GetReal_2014_2015.sqlite")


```

### Trend Data Q4 2015 to Q2 2016:

```{r echo=FALSE, eval=TRUE}

q4_lang_2014 <- dbReadTable(getRealdb, "langarts_final_matched")

q2_lang_2016 <-dbReadTable(getReal_2016db, "Q2_lang")

lang <- inner_join(q4_lang_2014, q2_lang_2016, by="girlCode")



lang$q4Grade <-as.numeric(lang$q4Grade)




langarts_q4q2 <- lang %>%
    mutate(pt_diff = lang_pts2 - q4Grade)

langarts_q4q2 <-
select(langarts_q4q2,girlCode, council, lang_pts2,q4Grade, pt_diff)


langarts_q4q2_test <- distinct(langarts_q4q2, girlCode)



```


```{r echo=FALSE, eval=TRUE}

lang_success_m <- function() {
    lang_dat <- filter(langarts_q4q2, lang_pts2 >=2, pt_diff >=0)
    lang_dat <- nrow(lang_dat)/nrow(langarts_q4q2)
    lang_dat <- round(lang_dat*100,2)
    pander(paste0(lang_dat, "%", sep=""))
}




```




```{r echo=FALSE, eval=FALSE}

langarts_grade_m <- ggplot(langarts_q4q2,(aes(x = lang_pts2, y = council)))

langarts_grade_m + geom_count()


```








### % of students who increased Language Arts Grade or maintained a C grade:
```{r echo=FALSE, eval=TRUE}
m_gpa_lang <- mean(langarts_q4q2$pt_diff)

m_gpa_lang <-pander(m_gpa_lang)



#plot(langarts_q4q2$pt_diff)

#with(langarts_q4q2,table(pt_diff))

#with(langarts_q4q2,table(lang_pts2 >=2, pt_diff >=0))



```

The number of students that could be matched from Quarter 4 to Quarter 2 is **`r nrow(langarts_q4q2)`**. 
The number of students that increased their grade or maintained a C is **`r lang_success_m()`**. The mean difference between the two quarters is **`r (m_gpa_lang)`**.


```{r echo=FALSE}


colnames (langarts_q4q2) [3] <- "Q2_Grade"
colnames (langarts_q4q2) [4] <- "Q4_Grade"
colnames (langarts_q4q2) [5] <- "Grade_Change"



```

```{r echo=FALSE, eval=FALSE}

PlusGrade_m <- langarts_q4q2 %>%
    filter(Grade_Change >=0)

PlusGrade_tbl_m  <- with(PlusGrade_m, table(Q4_Grade, Grade_Change))

PlusGrade_tbl_m





with(langarts_q4q2,table(Q2_Grade, Grade_Change))
grade_change_tbl <- with(langarts_q4q2,table(Q4_Grade, Grade_Change))

grade_change_tbl <- addmargins(grade_change_tbl)

pander(grade_change_tbl, caption="Q4 Grades and Grade Change")

```


### Plot change in Grade from Quarter 4 to Quarter 2:
```{r echo=FALSE}

langarts_change_plot_m <- ggplot(langarts_q4q2,(aes(x = Grade_Change, y = Q4_Grade)))

langarts_change_plot_m + geom_count()


```


