---
title: "Reading Grade"
author: "Kevin Gilds, MPA"
date: "May 7, 2016"
output: html_document
---

```{r echo=FALSE, warning=FALSE, message=FALSE}


library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

library(dplyr)
library(dplyr)
library(pander)
library(ggplot2)
library (ezknitr)
library(knitr)

```




```{r}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")



q1_reading <-dbReadTable(getReal_2016db,"Q1_reading")

q2_reading <-dbReadTable(getReal_2016db, "Q2_reading")


```



```{r echo=FALSE}

##join langarts grades q1q2

reading <- inner_join(q1_reading, q2_reading, by="girlCode")



reading_1 <- reading %>%
    select(girlCode, council.x, reading_pts, reading_pts2)

reading_q2q1 <- reading_1 %>%
    mutate(pt_diff = reading_pts2 - reading_pts)



```



```{r}

reading_change <- with(reading_q2q1, table(pt_diff, reading_pts2))

pander(reading_change)

reading_change_1 <- with(reading_q2q1, table(reading_pts2 >=2, pt_diff >=0))

pander(reading_change_1)




```


### Reading Success: % of Students that increased Grade or maintained a C 
```{r echo=FALSE}
reading_outcome <- function(){
    reading_dat <-filter(reading_q2q1,reading_pts2 >=2, pt_diff >=0)
    reading_dat <-  nrow(reading_dat) /nrow(reading_q2q1) 
    reading_dat <- round(reading_dat*100,2)
    paste(reading_dat, "%", sep= " ")
    
}


```


The number of matching students from Quarter 1 and Quarter 2 is **`r nrow(reading_q2q1)`**, and the percent of students who increased their reading grade is **`r reading_outcome()`**.





### GPA Difference between Q1 and Q2

```{r echo=FALSE}

#with(reading_q2q1,table(reading_pts))

#with(reading_q2q1,table(reading_pts2))


gpa_reading_1 <- mean(reading_q2q1$reading_pts)
#hist(reading_q2q1$reading_pts)
gpa_reading_2 <- mean(reading_q2q1$reading_pts2)
#hist(reading_q2q1$reading_pts2)

#reading_gpa_change <- (gpa_reading_2 - gpa_reading_1)

#reading_gpa_change

gpa_diff <- mean(reading_q2q1$pt_diff)



```

The average reading grade difference is **`r pander(gpa_diff)`**. This is impressive increase because many students may maintain their current grade. 

```{r echo=FALSE}
###Change name for plots


colnames (reading_q2q1) [2] <- "council"
colnames (reading_q2q1) [3] <- "Q1_Grade"
colnames (reading_q2q1) [4] <- "Q2_Grade"
colnames (reading_q2q1) [5] <- "Grade_Change"


```


### Reading Grades Plots

```{r echo=FALSE}

#reading_grades_q1 <- ggplot(reading_q2q1,(aes(x = Q1_Grade, y = council)))

#reading_grades_q1 + geom_count()

#reading_grades_q2 <- ggplot(reading_q2q1,(aes(x = Q2_Grade, y = council)))

#reading_grades_q2 + geom_count()


```

The changes in grades from Q1 to Q2 is represented below. The vertical axis represents Q1 grades and the bottom axis the change from Q1. For example those with an A in Q1 can decrease but not increase. Thus ideally we want to see circles heading to right. 


### Reading Grade Change from Q1 to Q2 

```{r echo=FALSE}


#reading_change_plot <- ggplot(reading_q2q1,(aes(x = Grade_Change, y = council)))

#reading_change_plot + geom_count()


reading_change_plot2 <- ggplot(reading_q2q1,(aes(x = Grade_Change, y = Q1_Grade)))

reading_change_plot2 + geom_count()


#plot(reading_change, col="Red")

#reading_dat <-filter(reading_q2q1,reading_pts2 >=2, reading_pt_diff >=0)

  
```




```{r}


setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data")

getRealdb<- dbConnect(SQLite(), dbname="data_Final_GetReal_2014_2015.sqlite")


```






```{r echo=FALSE}

q4_reading_2014 <- dbReadTable(getRealdb, "reading_final_matched")



q4_reading_2014 <- na.omit(q4_reading_2014)

q2_reading_2016 <-dbReadTable(getReal_2016db, "Q2_reading")

reading <- inner_join(q4_reading_2014, q2_reading_2016, by="girlCode")




reading_q4q2 <- reading %>%
    mutate(pt_diff = reading_pts2 - value)

reading_q4q2 <- 
select(reading_q4q2,girlCode, reading_pts2, value, pt_diff)


```


```{r echo=FALSE}




with(reading_q4q2,table(pt_diff))

with(reading_q4q2,table(reading_pts2 >=2, pt_diff >=0))

```

```{r echo=FALSE}

read_success_m <- function() {
    read_dat <- filter(reading_q4q2, reading_pts2 >=2, pt_diff >=0)
    read_dat <- nrow(read_dat)/nrow(reading_q4q2)
    read_dat <- round(read_dat*100,2)
    pander(read_dat)
}

read_success_m()


```


```{r echo=FALSE}
reading_mean_m<- mean(reading_q4q2$pt_diff)

pander(reading_mean_m)

#plot(langarts_q4q2$pt_diff)

#with(langarts_q4q2,table(pt_diff))

#with(langarts_q4q2,table(lang_pts2 >=2, pt_diff >=0))



```



```{r echo=FALSE, eval=FALSE}




colnames (reading_q4q2) [2] <- "Q1_Grade"
colnames (reading_q4q2) [3] <- "Q4_Grade"
colnames (reading_q4q2) [4] <- "Grade_Change"



```


```{r echo=FALSE, eval=FALSE}

### Reading Grades Plots



#reading_grades_q1 <- ggplot(reading_q2q1,(aes(x = Q1_Grade, y = council)))

#reading_grades_q1 + geom_count()

#reading_grades_q2 <- ggplot(reading_q2q1,(aes(x = Q2_Grade, y = council)))

#reading_grades_q2 + geom_count()


```


```{r echo=FALSE, eval=FALSE}

reading_change_plot_m <- ggplot(reading_q4q2,(aes(x = Grade_Change, y = Q4_Grade)))

reading_change_plot_m + geom_count()


```






