---
title: "Reading Grade"
author: "Kevin Gilds, MPA"
date: "`r Sys.Date()`"
output: html_document
---

```{r echo=FALSE, warning=FALSE, message=FALSE}


library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

library(dplyr)
library(pander)
library(ggplot2)
library(knitr)

```




```{r echo=FALSE}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")



q1_reading <-dbReadTable(getReal_2016db,"Q1_reading")

q2_reading <-dbReadTable(getReal_2016db, "Q2_reading")


```



```{r echo=FALSE}

##join langarts grades q1q2

reading <- inner_join(q1_reading, q2_reading, by="girlCode")



reading_1 <- reading %>%
    select(girlCode, council.x, reading_pts, reading_pts2)

reading_q2q1 <- reading_1 %>%
    mutate(pt_diff = reading_pts2 - reading_pts)



```



```{r echo=FALSE, eval=FALSE}

reading_change <- with(reading_q2q1, table(pt_diff, reading_pts2))

pander(reading_change)

reading_change_1 <- with(reading_q2q1, table(reading_pts2 >=2, pt_diff >=0))

pander(reading_change_1)




```


### Reading Success: % of Students that increased Grade or maintained a C 
```{r echo=FALSE}
reading_outcome <- function(){
    reading_dat <-filter(reading_q2q1,reading_pts2 >=2, pt_diff >=0)
    reading_dat <-  nrow(reading_dat) /nrow(reading_q2q1) 
    reading_dat <- round(reading_dat*100,2)
    paste(reading_dat, "%", sep= " ")
    
}


```


The number of matching students from Quarter 1 and Quarter 2 is **`r nrow(reading_q2q1)`**, and the percent of students who increased their reading grade is **`r reading_outcome()`**.





### GPA Difference between Q1 and Q2

```{r echo=FALSE}

#with(reading_q2q1,table(reading_pts))

#with(reading_q2q1,table(reading_pts2))


gpa_reading_1 <- mean(reading_q2q1$reading_pts)
#hist(reading_q2q1$reading_pts)
gpa_reading_2 <- mean(reading_q2q1$reading_pts2)
#hist(reading_q2q1$reading_pts2)

#reading_gpa_change <- (gpa_reading_2 - gpa_reading_1)

#reading_gpa_change

gpa_diff <- mean(reading_q2q1$pt_diff)



```

The reading gpa for students is **`r (gpa_reading_2)`**. The average reading grade difference is **`r pander(gpa_diff)`**. This is impressive increase because many students may maintain their current grade. 

```{r echo=FALSE}
###Change name for plots



colnames (reading_q2q1) [2] <- "council"
colnames (reading_q2q1) [3] <- "Q1_Grade"
colnames (reading_q2q1) [4] <- "Q2_Grade"
colnames (reading_q2q1) [5] <- "Grade_Change"


```


### Reading Grades Plots

```{r echo=FALSE}

#reading_grades_q1 <- ggplot(reading_q2q1,(aes(x = Q1_Grade, y = council)))

#reading_grades_q1 + geom_count()

#reading_grades_q2 <- ggplot(reading_q2q1,(aes(x = Q2_Grade, y = council)))

#reading_grades_q2 + geom_count()


```

The changes in grades from Q1 to Q2 is represented below. The vertical axis represents Q1 grades and the bottom axis the change from Q1. Thus ideally we want to see circles heading to right. However,students with an A in Q1 can decrease but not increase. 


### Reading Grade Change from Q1 to Q2 

```{r echo=FALSE}


#reading_change_plot <- ggplot(reading_q2q1,(aes(x = Grade_Change, y = council)))

#reading_change_plot + geom_count()


reading_change_plot2 <- ggplot(reading_q2q1,(aes(x = Grade_Change, y = Q1_Grade)))

reading_change_plot2 + geom_count()


#plot(reading_change, col="Red")

#reading_dat <-filter(reading_q2q1,reading_pts2 >=2, reading_pt_diff >=0)

  
```


## Reading Trend Data


```{r echo=FALSE}


setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data")

getRealdb<- dbConnect(SQLite(), dbname="data_Final_GetReal_2014_2015.sqlite")


```






```{r echo=FALSE}

q4_reading_2014 <- dbReadTable(getRealdb, "reading_final_matched")



q4_reading_2014 <- na.omit(q4_reading_2014)

q2_reading_2016 <-dbReadTable(getReal_2016db, "Q2_reading")

reading <- inner_join(q4_reading_2014, q2_reading_2016, by="girlCode")

#names(q2_reading_2016)

reading_q4q2 <- reading %>%
    mutate(pt_diff = reading_pts2 - Q4Grade)

reading_q4q2 <- 
select(reading_q4q2,girlCode, reading_pts2, Q4Grade, pt_diff)


```


```{r echo=FALSE,eval=FALSE}




with(reading_q4q2,table(pt_diff))

with(reading_q4q2,table(reading_pts2 >=2, pt_diff >=0))

```

```{r echo=FALSE}

read_success_m <- function() {
    read_dat <- filter(reading_q4q2, reading_pts2 >=2, pt_diff >=0)
    read_dat <- nrow(read_dat)/nrow(reading_q4q2)
    read_dat <- round(read_dat*100,2)
    pander(paste0(read_dat, "%", sep=""))
}




```



```{r echo=FALSE}
reading_mean_m<- mean(reading_q4q2$pt_diff)



#plot(langarts_q4q2$pt_diff)

#with(langarts_q4q2,table(pt_diff))

#with(langarts_q4q2,table(lang_pts2 >=2, pt_diff >=0))



```

The number of students that could be matched from last year is **`r nrow(reading_q4q2)`**. The current reading gpa for students who particpated last year is **`r mean(reading_q4q2$reading_pts2)`**
The percent of studuents of who increased their grade or maintained their grade is **`r read_success_m()`**. The average difference between Q4 2015 and Q2 is **`r (reading_mean_m)`**.

```{r echo=FALSE}




colnames (reading_q4q2) [2] <- "Q1_Grade"
colnames (reading_q4q2) [3] <- "Q4_Grade"
colnames (reading_q4q2) [4] <- "Grade_Change"



```


```{r echo=FALSE}

### Reading Grades Plots



#reading_grades_q1 <- ggplot(reading_q2q1,(aes(x = Q1_Grade, y = council)))

#reading_grades_q1 + geom_count()

#reading_grades_q2 <- ggplot(reading_q2q1,(aes(x = Q2_Grade, y = council)))

#reading_grades_q2 + geom_count()


```


```{r echo=FALSE}

reading_change_plot_m <- ggplot(reading_q4q2,(aes(x = Grade_Change, y = Q4_Grade)))

reading_change_plot_m + geom_count()


```

```{r echo=FALSE, eval=FALSE}

non_match <- anti_join(q2_reading_2016, q4_reading_2014, by="girlCode")

dim(non_match)

names(non_match )

non_match_gpa <- mean(non_match$reading_pts2)

non_match_gpa

```





