---
title: "Reading Grade"
author: "Kevin Gilds, MPA"
date: "`r Sys.Date()`"
output: html_document
---

```{r echo=FALSE, warning=FALSE, message=FALSE}


library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

library(dplyr)
library(dplyr)
library(pander)
library(ggplot2)
library(knitr)

```




```{r echo=FALSE}

setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")



q1_reading <-dbReadTable(getReal_2016db,"Q1_reading")

q2_reading <-dbReadTable(getReal_2016db, "Q2_reading")

q3_reading <-dbReadTable(getReal_2016db, "Q3_reading")

q4_reading <-dbReadTable(getReal_2016db, "Q4_reading")



```



```{r echo=FALSE}

##join langarts grades q1q2

reading_q1q4 <- inner_join(q4_reading, q1_reading, by="girlCode")

#head(reading_q1q4)

missing_q1q4 <- anti_join(q4_reading, q1_reading, by="girlCode")

#head(missing_q1q4)

reading_q2q4 <- inner_join(missing_q1q4, q2_reading, by="girlCode")

#dim(reading_q2q4)
#head(reading_q2q4)


#names(reading_q2q4)
#names(reading_q1q4)

```



```{r echo=FALSE}
reading_q1q4 <- reading_q1q4 %>%
    select(1,2,5,9)

#names(reading_q1q4)

colnames(reading_q1q4) [2] <- "council"
colnames(reading_q1q4) [3] <- "final"
colnames(reading_q1q4) [4] <-"baseline"


reading_q1q4 <- reading_q1q4 %>%
    mutate("Time" = "Q1Q4")

```


```{r echo=FALSE}

reading_q2q4 <- reading_q2q4 %>%
    select(1,2,5, 9)

#names(reading_q2q4)

colnames(reading_q2q4) [2] <- "council"
colnames(reading_q2q4) [3] <- "final"
colnames(reading_q2q4) [4] <-"baseline"

reading_q2q4 <- reading_q2q4 %>%
    mutate("Time" = "Q2Q4")



#names(reading_q1q4)

#names(reading_q2q4)

```


```{r echo=FALSE}

reading_2016 <- rbind(reading_q1q4, reading_q2q4)

#dim(reading_2016)

reading_2016_test <- distinct(reading_2016, girlCode)

#dim(reading_2016_test)


reading_2016 <- reading_2016 %>%
    mutate("pt_diff" = final- baseline)

#names(reading_2016)

```

```{r council_filter, echo=FALSE}

reading_2016 <- reading_2016 %>%
    filter(council == "West Central Council")

#dim(reading_2016)

```



```{r echo=FALSE, eval=FALSE}

reading_change <- with(reading_2016, table(pt_diff, reading_pts2))

pander(reading_change)

reading_change_1 <- with(reading_2016 table(reading_pts2 >=2, pt_diff >=0))

pander(reading_change_1)




```

```{r echo=FALSE}

read_maintain <- filter(reading_2016, final >=2, pt_diff ==0)

#head(read_maintain)
#nrow(read_maintain)


read_increase <- filter(reading_2016, final >=2, pt_diff >0)

#head(read_increase)


#nrow(read_increase)
```




### Reading Success: % of Students that increased Grade or maintained a C 
```{r echo=FALSE}
reading_outcome <- function(){
    reading_dat <-filter(reading_2016,final >=2, pt_diff >=0) #final great 
    reading_dat <-  nrow(reading_dat) /nrow(reading_2016) 
    reading_dat <- round(reading_dat*100,2)
    paste(reading_dat, "%", sep= " ")
    
}


```


The number of  students records that could be matched is **`r nrow(reading_2016)`**, 

The percent of students with a successful outcome is  **`r reading_outcome()`**.

1. The number of students who increased their reading grade is **`r nrow(read_increase)`**

2. The number of stuents who maintained at least a "C" grade is **`r nrow(read_maintain)`**





### GPA Difference between baseline and final:

```{r echo=FALSE}

#with(reading_q2q1,table(reading_pts))

#with(reading_q2q1,table(reading_pts2))


gpa_reading_1 <- mean(reading_2016$baseline)
#hist(reading_q2q1$reading_pts)
gpa_reading_2 <- mean(reading_2016$final)
#hist(reading_q2q1$reading_pts2)


gpa_reading_2 <-round(gpa_reading_2,2)

#reading_gpa_change <- (gpa_reading_2 - gpa_reading_1)

#reading_gpa_change

gpa_diff <- mean(reading_2016$pt_diff)


```

The reading gpa for students is **`r (gpa_reading_2)`**,and the average reading grade difference is **`r pander(gpa_diff)`**. 

```{r echo=FALSE}
###Change name for plots



colnames (reading_2016) [2] <- "council"
colnames (reading_2016) [4] <- "basline"
colnames (reading_2016) [3] <- "final"
colnames (reading_2016) [6] <- "Grade_Change"


```


### Reading Grades Plots:

```{r echo=FALSE}

#reading_grades_q1 <- ggplot(reading_q2q1,(aes(x = Q1_Grade, y = council)))

#reading_grades_q1 + geom_count()

#reading_grades_q2 <- ggplot(reading_q2q1,(aes(x = Q2_Grade, y = council)))

#reading_grades_q2 + geom_count()


```

The changes in grades from basline to final is represented below. The vertical axis represents Q1 grades and the bottom axis the change from Q1. Thus ideally we want to see circles moving to right. Note,students with an A in Q1 can decrease but not increase. 


### Reading Grade Change from baseline to final:

```{r echo=FALSE}


#reading_change_plot <- ggplot(reading_q2q1,(aes(x = Grade_Change, y = council)))

#reading_change_plot + geom_count()


reading_change_plot2 <- ggplot(reading_2016,(aes(x = Grade_Change, y = basline)))

reading_change_plot2 + geom_count()


#plot(reading_change, col="Red")

#reading_dat <-filter(reading_q2q1,reading_pts2 >=2, reading_pt_diff >=0)

  
```


## Reading Trend Data:


```{r echo=FALSE, eval=FALSE}


setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data")

getRealdb<- dbConnect(SQLite(), dbname="data_Final_GetReal_2014_2015.sqlite")


```






```{r echo=FALSE, eval=FALSE}

q4_reading_2014 <- dbReadTable(getRealdb, "reading_final_matched")



q4_reading_2014 <- na.omit(q4_reading_2014)

q2_reading_2016 <-dbReadTable(getReal_2016db, "Q2_reading")

reading <- inner_join(q4_reading_2014, q2_reading_2016, by="girlCode")

#names(q2_reading_2016)

reading_q4q2 <- reading %>%
    mutate(pt_diff = reading_pts2 - Q4Grade)

reading_q4q2 <- 
select(reading_q4q2,girlCode, reading_pts2, Q4Grade, pt_diff)


```


```{r echo=FALSE,eval=FALSE}




with(reading_q4q2,table(pt_diff))

with(reading_q4q2,table(reading_pts2 >=2, pt_diff >=0))

```

```{r echo=FALSE, eval=FALSE}

read_success_m <- function() {
    read_dat <- filter(reading_q4q2, reading_pts2 >=2, pt_diff >=0)
    read_dat <- nrow(read_dat)/nrow(reading_q4q2)
    read_dat <- round(read_dat*100,2)
    pander(paste0(read_dat, "%", sep=""))
}




```



```{r echo=FALSE, eval=FALSE}
reading_mean_m<- mean(reading_q4q2$pt_diff)

reading_mean_m <- round(reading_mean_m,2)


reading_gpa_m <- mean(reading_q4q2$reading_pts2)

reading_gpa_m <-round(reading_gpa_m,2)

#plot(langarts_q4q2$pt_diff)

#with(langarts_q4q2,table(pt_diff))

#with(langarts_q4q2,table(lang_pts2 >=2, pt_diff >=0))



```


```{r echo=FALSE, eval=FALSE}




colnames (reading_q4q2) [2] <- "Q1_Grade"
colnames (reading_q4q2) [3] <- "Q4_Grade"
colnames (reading_q4q2) [4] <- "Grade_Change"



```


```{r echo=FALSE, eval=FALSE}

### Reading Grades Plots



#reading_grades_q1 <- ggplot(reading_q2q1,(aes(x = Q1_Grade, y = council)))

#reading_grades_q1 + geom_count()

#reading_grades_q2 <- ggplot(reading_q2q1,(aes(x = Q2_Grade, y = council)))

#reading_grades_q2 + geom_count()


```


```{r echo=FALSE, eval=FALSE}

reading_change_plot_m <- ggplot(reading_q4q2,(aes(x = Grade_Change, y = Q4_Grade)))

reading_change_plot_m + geom_count()


```

```{r echo=FALSE, eval=FALSE}

non_match <- anti_join(q2_reading_2016, q4_reading_2014, by="girlCode")

dim(non_match)

names(non_match )

non_match_gpa <- mean(non_match$reading_pts2)

non_match_gpa

```





