---
title: "Status Report"
author: "Kevin Gilds, MPA"
date: "February 27, 2016"
output: html_document
---

```{r echo=FALSE}
library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")


```

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(dplyr)
library(pander)
library(ggplot2)
library (ezknitr)
library(shiny)
library(shinyapps)

setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")


### Make connection with database
girl <- dbReadTable(getReal_2016db, "girl_pre")

###Select the neeeded data for data entry status update
girl <- select(girl, council)
###Create and add column for status update
girl$dataSource <-"girl"

### Make connection with database
parent <-dbReadTable(getReal_2016db,"pre_parent")
###Select the neeeded data for data entry status update
parent1 <- select(parent,council)
###Create and add column for status update
parent1$dataSource <- "parent"

### Make connection with database
teacher <-dbReadTable(getReal_2016db, "pre_teacher")
###Select the neeeded data for data entry status update
teacher <-select(teacher,council)
###Create and add column for status update
teacher$dataSource <- "teacher"

###Bind girl and parent objects to prepare for status report
girl_parent <- rbind(girl,parent1)

### Make connection with database
grades_q1 <- dbReadTable(getReal_2016db,"Q1_Absences")
###Select the neeeded data for data entry status update

q1_stats <- select(grades_q1,council.x)
###Change column name to make it match with other data sets
colnames (q1_stats) [1] <- "council"
###Create and add column for status update
q1_stats$dataSource <- "Q1"


### Add the teacher to binding for status report
add_teacher <- rbind(girl_parent, teacher)


###Findal addition to create data frame for status report
survey_status <- rbind(add_teacher, q1_stats)

### Read the pre girl survey for reference down stream
girl_survey_dupes <-dbReadTable(getReal_2016db, "girl_pre_duplicates")
### Read the pre girl survey for reference down stream
parent_survey_dupes <-dbReadTable(getReal_2016db, "pre_parent_duplicate")
### Read the pre girl survey for reference down stream
q1_dupes <-dbReadTable(getReal_2016db, "Q1_duplicates")

### Reade the girl_pre_survey database for analysis. 
outcomes <- dbReadTable(getReal_2016db, "girl_pre")
###Select the variables of interest from the pre_survey
outcomes <- select(outcomes, girlCode, school, council, hr.avg, am.avg, ae.avg)

#### Read q1_reading data from database for analysis
q1_reading <-dbReadTable(getReal_2016db, "Q1_reading")

### Read q1_langarts data from database for analysis
q1_langarts <-dbReadTable(getReal_2016db,"Q1_lang")

###Read q1_absences data from database for analysis
q1_absences <-dbReadTable(getReal_2016db, "Q1_Absences")

###Read q2_absences data from database for analysis
q1_suspensions <- dbReadTable(getReal_2016db, "Q1_Suspensions")


###Read academic data from database for file explort
academic_data <- dbReadTable(getReal_2016db, "academic_data")



```


### Data Entry Status
```{r}
library(DT)

survey_status <-with(survey_status,table(council,dataSource))

pander(survey_status)



```



### Student Survey

```{r}


### Read girl survey data
girl_tbl <- select(outcomes, council, school, girlCode, hr.avg, ae.avg,am.avg )

### create table to see how many to be expected
girl_tbl_test <- with(girl_tbl, table(council))

###Show output
#pander(girl_tbl_test)





```

### Interactive Student Survey Status

```{r}
library(DT)

datatable(girl_tbl)
```


```{r}


```



### Girl Survey Duplicates Report

```{r}

###Read girl survey dupes
girl_survey_dupes1 <- select(girl_survey_dupes,council, school, girlCode)

###Create table to see how many to be expected
student_survey_dupe_ <-with(girl_survey_dupes, table(council))

###Create output
pander(student_survey_dupe_)



```

### Girl Survey Duplicate Interactive Report

```{r}
library(DT)

girl_survey_dupes <- select(girl_survey_dupes, 24:27)

datatable(girl_survey_dupes)


```







### Interactive Table for Academic Data
```{r}
datatable(academic_data)
```



###  Data Table for Duplicate Entries for Q1

```{r}

###Read girl survey dupes
girl_survey_dupes1 <- select(girl_survey_dupes,council, school, girlCode)

###Create table to see how many to be expected
student_survey_dupe_ <-with(girl_survey_dupes, table(council))

###Create output
pander(student_survey_dupe_)



```


```{r}

q1_dupes <- select(q1_dupes, 7:10)

datatable(q1_dupes)

```






### Interactive Table for Academic Data
```{r}
datatable(academic_data)
```



### Summary of  Duplicate Entries for Q1 by Council

```{r}

q1_dupes_tbl <-with(q1_dupes, table(council))

pander(q1_dupes_tbl)

```



### Interactive Table for Parent Survey

```{r}

parent <- select(parent, 6:9)

datatable(parent)


```


### Duplicate Entries for Parent Survey

```{r}

parent_survey_dupes_tbl <-with(parent_survey_dupes, table(council))

```


### Interactive Table for Duplicate Parent Survey

```{r}

parent_survey_dupes <- select(parent_survey_dupes, 6:9)

datatable(parent_survey_dupes)

```

