---
title: "student_survey_analysis"
author: "Kevin Gilds"
date: '`r Sys.Date()`'
output:
  html_document:
    toc: yes
  pdf_document:
    toc: yes
---



```{r import libaries, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(pander)
library(ggplot2)
library(sqldf)
library(psych)
library(knitr)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")


### Make connection with database
getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")




```


```{r load outcome survesy, echo=FALSE}

### Reade the girl_pre_survey database for analysis. 
outcomes <- dbReadTable(getReal_2016db, "girl_pre")
###Select the variables of interest from the pre_survey
outcomes <- select(outcomes, girlCode, council, hr.avg, am.avg, ae.avg)

history <- dbReadTable(getReal_2016db, "basic_view")


```



```{r}

setwd("C:/Users/kevin/Dropbox/GetReal/Analyis_data")

getReal_2013 <-dbConnect(SQLite (), dbname="getReal.sqlite")

girl_2013 <- dbReadTable(getReal_2013, "girlSurvey")

outcomes_2013 <- girl_2013 %>%
    select(girlScoutCouncil, Time, girlCode, hr_avg, am_avg, ae_avg)



```


###Pre 2013
```{r}

pre_outcomes2013  <- outcomes_2013 %>%
    filter(Time =="Pre")


dim(pre_outcomes2013)

pre_outcomes2013<- pre_outcomes2013 [!(duplicated(pre_outcomes2013$girlCode) | duplicated(pre_outcomes2013$girlCode, fromLast = TRUE)), ]

dim(pre_outcomes2013)

```



```{r}

post_outcomes2013 <- outcomes_2013 %>%
    filter(Time =="Post")


dim(post_outcomes2013)

post_outcomes2013<- post_outcomes2013 [!(duplicated(post_outcomes2013$girlCode) | duplicated(post_outcomes2013$girlCode, fromLast = TRUE)), ]


dim(post_outcomes2013)




```


```{r}
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

dbWriteTable(conn = getReal_2016db, name = "girl_pre2013", value = pre_outcomes2013, row.names=FALSE, overwrite=TRUE)

dbWriteTable(conn = getReal_2016db, name = "girl_post2013", value = post_outcomes2013, row.names=FALSE, overwrite=TRUE)


```



```{r lastyeardata, echo=FALSE}

setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data")
getRealdb<- dbConnect(SQLite(), dbname="data_Final_GetReal_2014_2015.sqlite")

pre_survey_2014 <- dbReadTable(getRealdb, "pre_girl_survey")


post_survey_MY1415 <- dbReadTable(getRealdb, "post_girl_survey")




```


```{r echo=FALSE}

### Match Pre Surveys

pre_merge <- inner_join (pre_survey_2014, outcomes, by = "girlCode", Copy=FALSE)



#x=2014, y=2015


```





```{r echo=FALSE}

post_merge <- inner_join(post_survey_MY1415, outcomes, by = "girlCode", Copy=FALSE)

non_match <- anti_join(outcomes, post_survey_MY1415, by = "girlCode", Copy = FALSE)


```




## Healthy Releationships


```{r hr_function, echo=FALSE}

hr <- function(){
    hr_tbl <- with(outcomes,table(hr.avg >=4.45))
    pander(hr_tbl)
    
}
```






### Percent of students achieving at a high level




```{r hr_percent, echo=FALSE}

hr_percent <- function() {
    hr_tbl <- filter(outcomes, hr.avg >=4.45)
    hr_tbl_p <- nrow(hr_tbl) /nrow(outcomes)
    hr_tbl_p <- round(hr_tbl_p*100,2)
    pander(paste(hr_tbl_p, "%", sep=""))
}


```

The Healthy Relationship questions measures the behaviors and attitudes of the respondent regarding their relationship skills. The number of valid survey entries is **`r nrow(outcomes)`**.
The percent of students achieving this outcome at a high level is **`r hr_percent()`**.

```{r hr outcome tables, echo=FALSE, eval=FALSE}
### create basic outcome table for healty releationship outcome

hr_tbl <- with(outcomes,table(hr.avg >=4.45))

### print in pretty table
pander(hr_tbl)

### Put percents with outcome table
hr_tbl_p <- prop.table(hr_tbl)


###Print percent table
pander(hr_tbl_p)

### Basic outcome table for healthy relationships by council
hr_tbl_c <- with(outcomes, table(council, hr.avg >=4.45))

### print results of outcome table
pander(hr_tbl_c)


####Percent by council

hr_tbl_cp <- prop.table(hr_tbl_c, 1)

### Print by percent
pander(hr_tbl_cp)


```

### Healthy Relationship Outcome Plots
```{r hr_barchart, fig.width=15, echo=FALSE}
### Plot outcome results
hr <- select(outcomes, council, hr.avg)
ggplot(hr, aes(hr.avg >=4.45)) + geom_bar(fill="blue", width = .5) + labs(x="Achieving at High Level", title = "Pre: Healthy Relationships")


```




```{r hr_hist2, echo=FALSE, eval=FALSE, message=FALSE}

### Plot outcome results by council    
hr_hist <- ggplot(hr, aes(x=hr.avg))
        hr_hist + geom_histogram(fill="blue") +facet_grid(~council) + labs(x=" All Outcome Scores", title = "Pre: Healthy Relationships")

```




### Healthy Relationships Outcome Distribution Plots
```{r hr_hist, echo=FALSE}
### Histogram to show all the outcome scores
### Abline for ggplot
 hr_hist <- ggplot(hr, aes(x=hr.avg)) 
        hr_hist + geom_histogram(fill="blue", bins=40) + labs(x=" All Outcome Scores", title = "Pre: Healthy Relationships")



        

```


```{r hr_boxplot, echo=FALSE, eval=FALSE}

### Box plot for outcome scores
        
hr_box <- ggplot(hr, aes(x=factor(council), hr.avg))
        hr_box + geom_boxplot(fill="blue") + labs(y=" All Outcome Scores", title = "Pre: Healthy Relationships")


```



```{r hr_descrip, echo=FALSE, eval=FALSE}
## Try x-table, or kable

### Prepare data frame for just looking at hr.avg        
hr_1 <- select(hr, hr.avg)

### Stat summary of df.
hr_des <- describe(hr_1)

kable(hr_des)
        
```


### Pre Survey Healthy Relationship Trends from 2013-2015

Pre survey average scores are down this year along with the proportion of students achieving the outcome at a high level. The key for this analysis is the percent of students increasing their outcome score. 

```{r echo=FALSE}


hr_history <-
    select(history, Year,population, mean, sd, achieved, outcome.1) 

hr_history <-
    filter(hr_history, outcome.1 == "Healthy Relationships"& Year !="2015")


percent_achieved <- hr_history$achieved / hr_history$population

percent_achieved <- round(percent_achieved*100, 2)

percent_achieved <- paste0(percent_achieved, "%")

hr_history <- cbind(hr_history, percent_achieved)

hr_history <- select(hr_history, Year, population, mean, sd, percent_achieved)

colnames(hr_history)[5] <-"percent achieved"

hr_Year <- "2015"
hr_population <- nrow(outcomes)
hr_mean <- mean(outcomes$hr.avg)
hr_sd <-sd(outcomes$hr.avg)
hr_achieved1 <- filter(outcomes, hr.avg >=4.45)
hr_achieved <- nrow(hr_achieved1)/nrow(outcomes)
hr_percent1 <- round(hr_achieved*100,2)
hr_percent <- paste0(hr_percent1, "%")


hr_df <- data.frame(hr_Year, hr_population, hr_mean, hr_sd, hr_percent )
 
colnames(hr_df)[1] <-"Year"
colnames(hr_df)[2] <- "population"
colnames(hr_df)[3] <- "mean"
colnames(hr_df)[4] <- "sd"
colnames(hr_df)[5] <- "percent achieved"


hr_history <- rbind(hr_history, hr_df)
pander(hr_history)

```





 
```{r echo=FALSE, eval=FALSE}

post_merge_hr_pre <- mean(post_merge$hr.avg.y)


post_merge_hr_post <-mean(post_merge$hr.avg.x)

non_match_hr_pre <- mean(non_match$hr.avg)






```


### Healthy Relationship Time Series

The number of student survey records that could be matched from last year is  **`r nrow(post_merge)`**.
Last year students who participated for multiple years had higher healthy relationship scores than students who had not participated in the program before. This is not the case this year. 

Healthy Relationship scores regressed from the post survey and students in the program did not score better than students in the program in terms of average scores or proportion of students achieving the skill at a high level. 


The number of matched student is **`r nrow(post_merge)`**, and the number of non matched students is   **`r nrow(non_match)`**.




```{r echo=FALSE}

hr_population_pre <- "Matched: Pre 2015-2016"
hr_mean_pre <- mean(post_merge$hr.avg.y)
hr_sd_pre <- sd(post_merge$hr.avg.y)
hr_achieved_1 <- filter(post_merge, hr.avg.y >= 4.45)
hr_achieved <- nrow(hr_achieved_1)
hr_percent_1 <- nrow(hr_achieved_1)/nrow(post_merge)
hr_percent_1 <- round(hr_percent_1*100,2)
hr_percent <- paste0(hr_percent_1, "%", sep= " ")


hr_trend_pre<-data.frame(hr_population_pre, hr_mean_pre, hr_sd_pre, hr_achieved, hr_percent)

colnames(hr_trend_pre)[1] <- "Time"
colnames(hr_trend_pre)[2] <- "Mean"
colnames(hr_trend_pre)[3] <- "SD"
colnames(hr_trend_pre)[4] <- "Achieved"
colnames(hr_trend_pre)[5] <- "Percent Achieved"



```




```{r echo=FALSE}

hr_time_post <-
hr_Population_post <- "Matched: Post 2014-2015"
hr_mean_post <- mean(post_merge$hr.avg.x)
hr_sd_post <- sd(post_merge$hr.avg.x)
hr_achieved_1post <- filter(post_merge, hr.avg.x >=4.45)
hr_achieved_post <- nrow(hr_achieved_1post)
hr_percent_post1 <- nrow(hr_achieved_1post)/nrow(post_merge)
hr_percent_post <- round(hr_percent_post1*100,2)
hr_percent_post <- paste0(hr_percent_post, "%")

hr_trend_post <- data.frame(hr_Population_post, hr_mean_post, hr_sd_post, hr_achieved_post, hr_percent_post)


colnames(hr_trend_post)[1] <- "Time"
colnames(hr_trend_post)[2] <- "Mean"
colnames(hr_trend_post)[3] <- "SD"
colnames(hr_trend_post)[4] <- "Achieved"
colnames(hr_trend_post)[5] <- "Percent Achieved"





```



```{r echo=FALSE}
hr_Population_non <- "Non-Matched: Pre 2015-2016"
hr_mean_non <- mean(non_match$hr.avg)
hr_sd_non <- sd(non_match$hr.avg)
hr_achieved_1non <- filter(non_match, hr.avg >=4.45)
hr_achieved_non <- nrow(hr_achieved_1non)
hr_percent_non1 <- nrow(hr_achieved_1non)/nrow(non_match)
hr_percent_non <- round(hr_percent_non1*100,2)
hr_percent_non <- paste0(hr_percent_non, "%")

hr_trend_non <- data.frame(hr_Population_non, hr_mean_non, hr_sd_non, hr_achieved_non, hr_percent_non)



colnames(hr_trend_non)[1] <- "Time"
colnames(hr_trend_non)[2] <- "Mean"
colnames(hr_trend_non)[3] <- "SD"
colnames(hr_trend_non)[4] <- "Achieved"
colnames(hr_trend_non)[5] <- "Percent Achieved"




```

```{r echo=FALSE}

population1<- nrow(post_merge)

population2 <- nrow(post_merge)

population3 <- nrow(non_match)

population4 <- data.frame(population1, population2, population3)



hr_trend_1 <- rbind(hr_trend_post, hr_trend_pre)

hr_trend <- rbind(hr_trend_1, hr_trend_non)







pander(hr_trend)

```






```{r echo=FALSE, eval=FALSE}

kable(post_merge_hr_pre)
kable(post_merge_hr_post)

```







```{r echo= FALSE, eval=FALSE}

hr_outcome_pre_2015 <- with(post_merge,table(hr.avg.y >=4.45))



pander(hr_outcome_pre_2015)

hr_outcome_post_2014 <- with(post_merge,table(hr.avg.x >=4.45))

pander(hr_outcome_post_2014)

non_match_outcome <-with(non_match,table(hr.avg >=4.45))

pander(non_match_outcome)


wilcox.test(post_merge$hr.avg.y, post_merge$hr.avg.x)

wilcox.test(post_merge$hr.avg.y, non_match$hr.avg)

```





## Academic Engagement


```{r echo=FALSE, eval=FALSE}
ae <- function() {
    ae_tbl <-with(outcomes,table(ae.avg >=4.5))
    pander(ae_tbl)
    
}

ae()
```



```{r echo = FALSE}
ae_percent <-function() {
    ae_tbl <-filter(outcomes,ae.avg >=4.5)
    ae_p <-nrow(ae_tbl)/nrow(outcomes)
    ae_p <-round(ae_p*100,2)
    pander(paste(ae_p, "%", sep=""))
    
}




```


### Percent of students achieving at a high level: 

Academic Engagement questions gauge tangible behaviors that help students succeed in school.The number of valid survey entries is **`r nrow(outcomes)`** The percent of students achieving the academic achievement at a high skill level is **`r ae_percent()`**. 
```{r echo = FALSE}

### Prepare data frame for tables
ae <- select(outcomes, council, ae.avg)


```






```{r echo=FALSE, eval = FALSE}
### Prepare data frame for tables
ae <- select(outcomes, council, ae.avg)

### Create outcome tables
ae_tbl <-with(ae,table(ae.avg >=4.5))

### Print outcome table
pander(ae_tbl)

### Create percent outcome table
ae_tbl_p <- prop.table(ae_tbl)

### Print Outcome table
pander(ae_tbl_p)

### Make outcome table by council
ae_tbl_c <-with(ae,table(council, ae.avg >=4.5))

### Print Outcome table by council
pander(ae_tbl_c)

### Make outcome table by percent
ae_tbl_cp <- prop.table(ae_tbl_c,1)

### Print percent table. 
pander(ae_tbl_cp)



```

### Academic Engagment Outcome Plots

```{r fig.width=15, echo = FALSE}
###Create outcome plot 
ae_plot <-ggplot(ae, aes(ae.avg >= 4.5)) 
         ae_plot + geom_bar(fill="blue", width = .5) + labs(x="Achieving at High Level", title = "Pre: Academic Engagement"
                                                                               ) 


         
```


```{r echo=FALSE, eval= FALSE}

### Create outcome plot by council    
ae_hist <- ggplot(ae, aes(x=ae.avg))
        ae_hist + geom_histogram(fill="blue") +facet_grid(~council) + labs(x=" All Outcome Scores", title = "Pre: Healthy Relationships")

```



### Academic Engagement Distribution Plots

```{r echo = FALSE}

### Create Histogram of all outcome scores
ae_hist <- ggplot(ae, aes(ae.avg)) 
        ae_hist + geom_histogram(fill="blue", bins=20) + labs(x="All Outcome Scores", title="Pre: Academic Engagement")


```



```{r fig.width=20, echo=FALSE, eval=FALSE}

###Create box plot by council
ae_box <-ggplot(ae, aes(x=factor(council), ae.avg))
ae_box + geom_boxplot(fill="blue") + labs(y="All Outcome Scores", title = "Pre: Academic Engagement")
```



```{r echo = FALSE, eval=FALSE}
###Summary stats for academic engagement variable
ae_desc <- describe(ae$ae.avg)

###Make Summary table look nice
kable(ae_desc)
        
        
```



### Academic Engagement Trends from 2013-2015

Pre survey average scores are comparable to last year along with the proportion of students achieving the outcome at a high level. The key for this analysis is the percent of students increasing their outcome score. 


```{r echo=FALSE}


ae_history <-
    select(history, Year,population, mean, sd, achieved, outcome.1) 

ae_history <-
    filter(ae_history, outcome.1 == "Academic Engagement"& Year !="2015")


ae_percent_achieved <- ae_history$achieved / ae_history$population

ae_percent_achieved <- round(ae_percent_achieved*100, 2)

ae_percent_achieved <- paste0(ae_percent_achieved, "%")

ae_history <- cbind(ae_history, ae_percent_achieved)

ae_history <-select(ae_history, Year, population, mean, sd, ae_percent_achieved)

colnames(ae_history)[5]<-"percent achieved"


ae_Year <- "2015"
ae_population <- nrow(outcomes)
ae_mean <- mean(outcomes$ae.avg)
ae_sd <-sd(outcomes$ae.avg)
ae_achieved1 <- filter(outcomes, ae.avg >=4.5)
ae_achieved <- nrow(ae_achieved1)/nrow(outcomes)
ae_percent1 <- round(ae_achieved*100,2)
ae_percent <- paste0(ae_percent1, "%")


ae_df <- data.frame(ae_Year, ae_population, ae_mean, ae_sd, ae_percent )
 
colnames(ae_df)[1] <-"Year"
colnames(ae_df)[2] <- "population"
colnames(ae_df)[3] <- "mean"
colnames(ae_df)[4] <- "sd"
colnames(ae_df)[5] <- "percent achieved"


ae_history <- rbind(ae_history, ae_df)
pander(ae_history)



```

### Academic Engagement Time Series

The table below illustrates that the students who participated in the program last year regressed from the post survey but still outperform students who were not in the program last year in both average scores and proportion of achieving the skill at a high level. However, the difference between the two groups was not statistically significant using a Wilcoxon sign rank test at the .05 level. This means that there is 95 percent certain is that these difference  is not due to chance.


The number of matched student is **`r nrow(post_merge)`** and the number of non matched students is   **`r nrow(non_match)`**.




```{r echo=FALSE}

ae_population_pre <- "Matched: Pre 2015-2016"
ae_mean_pre <- mean(post_merge$ae.avg.y)
ae_sd_pre <- sd(post_merge$ae.avg.y)
ae_achieved_1 <- filter(post_merge, ae.avg.y >= 4.5)
ae_achieved <- nrow(ae_achieved_1)
ae_percent_1 <- nrow(ae_achieved_1)/nrow(post_merge)
ae_percent_1 <- round(ae_percent_1*100,2)
ae_percent <- paste0(ae_percent_1, "%", sep= " ")


ae_trend_pre<-data.frame(ae_population_pre, ae_mean_pre, ae_sd_pre, ae_achieved, ae_percent)



colnames(ae_trend_pre)[1] <- "Population"
colnames(ae_trend_pre)[2] <- "Mean"
colnames(ae_trend_pre)[3] <- "SD"
colnames(ae_trend_pre)[4] <- "Achieved"
colnames(ae_trend_pre)[5] <- "Percent Achieved"




```




```{r echo=FALSE}

ae_Population_post <- "Matched: Post 2014-2015"
ae_mean_post <- mean(post_merge$ae.avg.x)
ae_sd_post <- sd(post_merge$ae.avg.x)
ae_achieved_1post <- filter(post_merge, ae.avg.x >=4.5)
ae_achieved_post <- nrow(ae_achieved_1post)
ae_percent_post1 <- nrow(ae_achieved_1post)/nrow(post_merge)
ae_percent_post <- round(ae_percent_post1*100,2)
ae_percent_post <- paste0(ae_percent_post, "%")

ae_trend_post <- data.frame(ae_Population_post, ae_mean_post, ae_sd_post, ae_achieved_post, ae_percent_post)



colnames(ae_trend_post)[1] <- "Population"
colnames(ae_trend_post)[2] <- "Mean"
colnames(ae_trend_post)[3] <- "SD"
colnames(ae_trend_post)[4] <- "Achieved"
colnames(ae_trend_post)[5] <- "Percent Achieved"



```


```{r echo=FALSE}
ae_Population_non <- "Non-Matched: Pre 2015-2016"
ae_mean_non <- mean(non_match$ae.avg)
ae_sd_non <- sd(non_match$ae.avg)
ae_achieved_1non <- filter(non_match, ae.avg >=4.5)
ae_achieved_non <- nrow(ae_achieved_1non)
ae_percent_non1 <- nrow(ae_achieved_1non)/nrow(non_match)
ae_percent_non <- round(ae_percent_non1*100,2)
ae_percent_non <- paste0(ae_percent_non, "%")

ae_trend_non <- data.frame(ae_Population_non, ae_mean_non, ae_sd_non, ae_achieved_non, ae_percent_non)




colnames(ae_trend_non)[1] <- "Population"
colnames(ae_trend_non)[2] <- "Mean"
colnames(ae_trend_non)[3] <- "SD"
colnames(ae_trend_non)[4] <- "Achieved"
colnames(ae_trend_non)[5] <- "Percent Achieved"


```


```{r echo=FALSE}

### Academic Mastery Time Series Data


ae_trend_1 <- rbind(ae_trend_post, ae_trend_pre)

ae_trend <- rbind(ae_trend_1, ae_trend_non)

pander(ae_trend)

```



```{r echo=FALSE, eval=FALSE}

post_merge_ae_pre <- describe(post_merge$ae.avg.y)
post_merge_ae_post <- describe(post_merge$ae.avg.x)

non_match_ae_pre <-describe(non_match$ae.avg)


kable(post_merge_ae_pre)
kable(post_merge_ae_post)
kable(non_match_ae_pre)

wilcox.test(post_merge$ae.avg.y, post_merge$ae.avg.x, "less",paired=TRUE)

wilcox.test(post_merge$ae.avg.y, post_merge$ae.avg.x, paired=TRUE)

wilcox.test(post_merge$ae.avg.y, post_merge$ae.avg.x, "greater", paired=TRUE)



wilcox.test(post_merge$ae.avg.y, non_match$ae.avg, paired = FALSE)




```


```{r echo=FALSE, eval=FALSE}


ae_outcome_pre <- with(post_merge, table(ae.avg.y >=4.5))

pander(ae_outcome_pre)

ae_outcome_post <- with(post_merge, table(ae.avg.x <=4.5))

pander(ae_outcome_post)

```




## Academic Mastery

```{r echo = FALSE, eval = FALSE}
am <- function() {
    am_tbl <-with(outcomes,table(am.avg >=4.8))
    pander(am_tbl)
}

am()


```


```{r echo=FALSE}
am_percent <-function() {
    am_table <-filter(outcomes,am.avg >=4.8)
    am_p <-nrow(am_table)/nrow(outcomes)
    am_p <-round(am_p*100,2)
    pander(paste(am_p, "%", sep= ""))
}


```


### Percent of students achieving at a high level
The Academic Mastery questions gauge a student's attitude towards school and education.The number of valid survey entries is **`r nrow(outcomes)`**.
The percent of students achieving this outcome at a high level is **`r am_percent()`**.


```{r echo = FALSE}

###Create data fram to set up outcome table
am <- select(outcomes, council, am.avg)

```





```{r echo= FALSE, eval= FALSE}

###Create data fram to set up outcome table
am <- select(outcomes, council, am.avg)

###Create academic mastery outcome table
am_tbl <- with(am,table(am.avg >=4.8))


### Print outcome table
pander(am_tbl)

### Put percentage to counts
am_tbl_p <- prop.table(am_tbl)


### Print pretty percent table.
pander(am_tbl_p)

### Outcome count by table
am_c <- with(am,table(council, am.avg >=4.8))

### Print outcome table
pander(am_c)

#### Academic Mastery by outcome count by percent
am_cp <-prop.table(am_c,1)

#### Print outcome percent outcome table. 
pander(am_cp)

```


### Academic Mastery Outcome Plots

```{r fig.width=15, echo = FALSE}

### Plot outcome results for academic masters
am_plot <-ggplot(am, aes(am.avg >= 4.8)) 
         am_plot + geom_bar(fill="blue", width = .5) + labs(x="Achieving at High Level", title = "Pre: Academic Mastery") 
     
         


```



### Academic Mastery Distribution Plots

```{r echo = FALSE, eval=TRUE}

### Create histogram from academic mastery scores
am_hist <- ggplot(am, aes(am.avg)) 
        am_hist + geom_histogram(fill="blue", bins=40) + labs(x="All Outcome Scores", title="Pre: Academic Mastery")
        


```





```{r fig.width=15, echo = FALSE, eval = FALSE}
        
### Create box plot of academic master outcome scores. 
am_box <-ggplot(am, aes(x=factor(council), am.avg))
am_box + geom_boxplot(fill="blue") + labs(y="All Outcome Scores", title = "Pre: Academic Mastery")

```



```{r echo = FALSE, eval=FALSE}

### Create stats summary
am_s <- describe(am$am.avg)

### Print summary with kable        
kable(am_s)
        
```


### Academic Mastrey Trends from 2013-2015

Pre survey average scores are comparable to last year along with the proportion of students achieving the outcome at a high level. The key for this analysis is the percent of students maintaining at a high level. 



```{r echo=FALSE}


am_history <-
    select(history, Year,population, mean, sd, achieved, outcome.1) 

am_history <-
    filter(am_history, outcome.1 == "Academic Mastery"& Year !="2015")


am_percent_achieved <- am_history$achieved / am_history$population

am_percent_achieved <- round(am_percent_achieved*100, 2)

am_percent_achieved <- paste0(am_percent_achieved, "%")

am_history <- cbind(am_history, am_percent_achieved)

am_history <- select(am_history, Year, population, mean, sd, am_percent_achieved)

colnames(am_history)[5] <- "percent achieved"



am_Year <- "2015"
am_population <- nrow(outcomes)
am_mean <- mean(outcomes$am.avg)
am_sd <-sd(outcomes$am.avg)
am_achieved1 <- filter(outcomes, am.avg >=4.8)
am_achieved <- nrow(am_achieved1)/nrow(outcomes)
am_percent1 <- round(am_achieved*100,2)
am_percent <- paste0(am_percent1, "%")


am_df <- data.frame(am_Year, am_population, am_mean, am_sd, am_percent )
 
colnames(am_df)[1] <-"Year"
colnames(am_df)[2] <- "population"
colnames(am_df)[3] <- "mean"
colnames(am_df)[4] <- "sd"
colnames(am_df)[5] <- "percent achieved"


am_history <- rbind(am_history, am_df)
pander(am_history)




```


The table below illustrates that the students who participated in the program last year increased  from the post survey and  outperformed students who were not in the program last year in both average scores and proportion of achieving the skill at a high level. The difference is statistically significant at the .05 level using a Wilcoxon Signed rank test. 

The number of matched student is **`r nrow(post_merge)`** and the number of non matched students is   **`r nrow(non_match)`**.


```{r echo=FALSE}



population_pre <- "Matched: Pre 2015-2016"
mean_pre <- mean(post_merge$am.avg.y)
sd_pre <- sd(post_merge$am.avg.y)
achieved_1 <- filter(post_merge, am.avg.y >= 4.8)
achieved <- nrow(achieved_1)
percent_1 <- nrow(achieved_1)/nrow(post_merge)
percent_1 <- round(percent_1*100,2)
percent <- paste0(percent_1, "%", sep= " ")


am_trend_pre<-data.frame(population_pre, mean_pre, sd_pre, achieved, percent)



colnames(am_trend_pre)[1] <- "Population"
colnames(am_trend_pre)[2] <- "Mean"
colnames(am_trend_pre)[3] <- "SD"
colnames(am_trend_pre)[4] <- "Achieved"
colnames(am_trend_pre)[5] <- "Percent Achieved"




```




```{r echo=FALSE}

Population_non <- "Non-Matched: Pre 2015-2016"
mean_non <- mean(non_match$am.avg)
sd_non <- sd(non_match$am.avg)
achieved_1non <- filter(non_match, am.avg >=4.8)
achieved_non <- nrow(achieved_1non)
percent_non1 <- nrow(achieved_1non)/nrow(non_match)
percent_non <- round(percent_non1*100,2)
percent_non <- paste0(percent_non, "%")

am_trend_non <- data.frame(Population_non, mean_non, sd_non, achieved_non, percent_non)

colnames(am_trend_non)[1] <- "Population"
colnames(am_trend_non)[2] <- "Mean"
colnames(am_trend_non)[3] <- "SD"
colnames(am_trend_non)[4] <- "Achieved"
colnames(am_trend_non)[5] <- "Percent Achieved"


```



```{r echo=FALSE}
Population_post <- "Matched: Post 2014-2015"
mean_post <- mean(post_merge$am.avg.x)
sd_post <- sd(post_merge$am.avg.x)
achieved_1post <- filter(post_merge, am.avg.x >=4.8)
achieved_post <- nrow(achieved_1post)
percent_post1 <- nrow(achieved_1post)/nrow(post_merge)
percent_post <- round(percent_post1*100,2)
percent_post <- paste0(percent_post, "%")

am_trend_post <- data.frame(Population_post, mean_post, sd_post, achieved_post, percent_post)

colnames(am_trend_post)[1] <- "Population"
colnames(am_trend_post)[2] <- "Mean"
colnames(am_trend_post)[3] <- "SD"
colnames(am_trend_post)[4] <- "Achieved"
colnames(am_trend_post)[5] <- "Percent Achieved"




```

### Academic Mastery Time Series Data


```{r echo=FALSE}

am_trend_1 <- rbind(am_trend_post, am_trend_pre)

am_trend <- rbind(am_trend_1, am_trend_non)

pander(am_trend)

```


#### Wilcox Test: Compare students in the program Pre and Post Surveys

```{r echo=FALSE, comment=NA}
post_merge_am_pre <- describe(post_merge$am.avg.y)
post_merge_am_post <- describe(post_merge$am.avg.x)

#non_match_am_pre <- describe(non_match$am.avg)

#kable(post_merge_am_pre)
#kable(post_merge_am_post)
#kable(non_match_am_pre)


wilcox.test(post_merge$am.avg.y, post_merge$am.avg.x, paired = TRUE)


#wilcox.test(post_merge$am.avg.y, non_match$am.avg, "greater", paired = FALSE)


```



#### Wilcox Test: Compare students in the program last year and those not in the program last year
```{r echo=FALSE,comment=NA}
wilcox.test(post_merge$am.avg.y, non_match$am.avg, paired = FALSE)


```



```{r echo=FALSE, eval=FALSE}

am_outcome_pre <-with(post_merge,table(am.avg.y >=4.8))

pander(am_outcome_pre)

am_outcome_post <- with(post_merge,table(am.avg.x >=4.8))

pander(am_outcome_post)

```



