---
title: "Suspensions"
author: "Kevin Gilds, MPA"
date: "`r Sys.Date()`"
output: html_document
---


```{r echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(dplyr)
library(pander)
library(ggplot2)
library (ezknitr)
library(sqldf)

###Set directory to find data 
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

### Connect with database
getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

###Read q1 suspension data from data base and assign varible
q1_suspensions <- dbReadTable(getReal_2016db, "Q1_Suspensions")

### Read q2 suspension data base and assign to variable
q2_suspensions <-dbReadTable(getReal_2016db, "Q2_Suspensions")



```



#Improvement In School Behavior

## Objective:
*70% of participating students will show improvement in behavior by decreasing their number of suspensions from the baseline grading period to final grading period or not having a suspension during the school year as evidenced from the student's report card/school reports.*
 

```{r echo=FALSE}

### Merge q1 and q2 suspension data by girlCode
suspsensions <- inner_join(q1_suspensions, q2_suspensions, by="girlCode")



### Narrow variables of interest
suspsensions_1 <- suspsensions %>%
    select(girlCode, council.y.x, susp_sum.x, susp_sum.y)

### Make calculated field from q2 and q1 
suspensions_q2q1 <- suspsensions_1 %>%
    mutate(susp_diff = susp_sum.y - susp_sum.x)

### Get rid of can cases that have a NA value
suspensions_q2q1 <- suspensions_q2q1 %>%
    filter(susp_diff !="NA")

```

### Suspensions: % of students who reduced the number of supsensions or never received a suspsenion
```{r echo=FALSE}
suspensions_success <- function() {
    no_suspensions <- filter(suspensions_q2q1, susp_sum.x == 0, susp_sum.y == 0) ##Filter students without a suspension
    decrease_suspensions <- filter(suspensions_q2q1, susp_diff <0) ##Filter students who decreased their suspensions
    total_suspensions <- nrow(no_suspensions) + nrow(decrease_suspensions) # add no suspensions and decreased students together for positive outcome
    total_suspensions <- total_suspensions/nrow(suspensions_q2q1) # divide positive outcome students from total students
    total_suspensions <- round(total_suspensions*100,2) #make into percentage
    pander(paste0(total_suspensions, "%", sep= "")) # add in percent sign
}


```





```{r echo=FALSE}

suspensions_change <- with(suspensions_q2q1,table(susp_diff)) ###Make a table showing all outcomes

pander(suspensions_change) ### display pretty table

susp_diff<- pander(mean(suspensions_q2q1$susp_diff, na.rm=TRUE)) ##obtain mean difference

#suspensions_change_1 <- with(suspensions_q2q1,table(susp_diff < 0))

#pander(suspensions_change_1)


#suspensions_change_2 <- with(suspensions_q2q1,table(susp_diff ==0, susp_sum.y==0))

#pander(suspensions_change_2)




#plot(suspensions_change)
```

The number of the valid entries is **`r nrow(suspensions_q2q1)`**, and the percent of students who have decreased their suspensions or did not have any suspensions is **`r suspensions_success()`**. The average difference of suspensions between Quarter 1 and Quarter 2 is **`r susp_diff`**





```{r echo=FALSE}

colnames (suspensions_q2q1) [2] <- "Council"  #change element #1 name to make a pretty graph
colnames (suspensions_q2q1) [3] <- "Q1_Suspenions"#change element #2 to make a pretty graph
colnames (suspensions_q2q1) [4] <- "Q2_Suspensions"#change element #3 to make a pretty graph
colnames (suspensions_q2q1) [5] <- "Suspensions_Change"#change name of element #5 to make a pretty graph

```




### Suspensions Change Plots from Quarter 1 to Quarter 2:

The plot below reflects that their has been an increase in suspensions from  Quarter 1 to  Quarter 2. The council is on the vertical axis and the suspensions change is on the bottom axis. The desire is for the circles to be on the left.  
```{r echo=FALSE, warning=FALSE}

suspenesions_change_plot_c <- ggplot(suspensions_q2q1,(aes(x = Suspensions_Change, y = Council)))

suspenesions_change_plot_c + geom_count() #display ggplot of Suspsenion change by Council 

#suspenesions_change_plot2 <- ggplot(suspensions_q2q1,(aes(x = Suspensions_Change, y = Q1_Suspenions)))

#suspenesions_change_plot2 + geom_count()






```


### Trend Data:

### Trend Data Q4 2015 to Q2 2016:
```{r echo=FALSE}

## Trend Data

###Change working directory
setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data")

###Conncent to database with 2015 data
getRealdb<- dbConnect(SQLite(), dbname="data_Final_GetReal_2014_2015.sqlite")

### Read data from with 2015 data
suspensions_2015 <- dbReadTable(getRealdb, "matched_suspenions")



```

```{r echo=FALSE}


###Merge and find matches from q4 2015 to q2 2015
susp_match <- inner_join(suspensions_q2q1, suspensions_2015, by="girlCode")



###Make calculated field from old database
susp_match <- susp_match %>%
    mutate(final.x + final.y)


###Change column name to make for easir calculated field
colnames(susp_match)[16] <-"Q4_2015"

### Make calculated field
susp_match <- susp_match %>%
    mutate(Q4_2015-Q2_Suspensions)


### Give caluculated field a better name
colnames(susp_match)[17] <- "susp_trend"



```


```{r echo=FALSE, eval=FALSE}

###narrow variable selection
susp_history <- susp_match %>%
    select(Q1_Suspenions, Q2_Suspensions, Q4_2015)

### List value
susp_history

### Plot the values
plot(susp_history)

```



```{r echo=FALSE}

susp_success <-function(){
    susp_match_no <-filter(susp_match, Q4_2015 == 0, Q2_Suspensions ==0) #find studens with no suspensions
    susp_data_m <-filter(susp_match, susp_trend <0) #find students who decreased their suspsenions
    susp_data_m2 <- nrow(susp_match_no) + nrow(susp_data_m) #add positive outcome students together
    susp_data_1m <- susp_data_m2/nrow(susp_match) #divide postive outcomes from total
    susp_data_percen1 <- round(susp_data_1m*100,2) #obtain percent
    pander(paste0(susp_data_percen1, "%", sep=""))#make pretty and add percent sign
}



```

```{r echo=FALSE}

susp_match_m <- mean(susp_match$susp_trend)

susp_match_m <- round(susp_match_m,2)

```



The number of students that could be matched from Quarter 4, 2015 is **`r nrow(susp_match)`**. The mean difference between Quarter 4 2015 and Quarter 2 2016 is **`r (susp_match_m) `**. The percent of students who decreased their number of suspensions from Quarter 4 to Quarter 2 or never received a suspension is   **`r susp_success()`**.


### Plot of differences in Suspensions by Council:

```{r echo=FALSE}
suspenesions_change_plot_m <- ggplot(susp_match,(aes(x = susp_trend, y = Council)))

suspenesions_change_plot_m + geom_count() #plots change by council


```




### Plot of differences in Suspensions by student:
```{r echo=FALSE}

plot(susp_match$susp_trend, ylab="Suspension Difference", xlab="Matched Students")
abline(h=0, col="red") #plots changes by student observation
```



