---
title: "Suspensions"
author: "Kevin Gilds, MPA"
date: "May 8, 2016"
output: html_document
---


```{r echo=FALSE, warning=FALSE, message=FALSE}

library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

library(dplyr)
library(dplyr)
library(pander)
library(ggplot2)
library (ezknitr)

setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")



q1_suspensions <- dbReadTable(getReal_2016db, "Q1_Suspensions")

q2_suspensions <-dbReadTable(getReal_2016db, "Q2_Suspensions")



```



#Suspensions
 

```{r echo=FALSE}

suspsensions <- inner_join(q1_suspensions, q2_suspensions, by="girlCode")




suspsensions_1 <- suspsensions %>%
    select(girlCode, council.y.x, susp_sum.x, susp_sum.y)

suspensions_q2q1 <- suspsensions_1 %>%
    mutate(susp_diff = susp_sum.y - susp_sum.x)


suspensions_q2q1 <- suspensions_q2q1 %>%
    filter(susp_diff !="NA")

```

### Suspensions: % of students who reduced the number of supsensions or never received a suspsenion. 
```{r echo=FALSE}
suspensions_success <- function() {
    no_suspensions <- filter(suspensions_q2q1, susp_sum.x == 0, susp_sum.y == 0)
    decrease_suspensions <- filter(suspensions_q2q1, susp_diff <0)
    total_suspensions <- nrow(no_suspensions) + nrow(decrease_suspensions)
    total_suspensions <- total_suspensions/nrow(suspensions_q2q1)
    total_suspensions <- round(total_suspensions*100,2)
    pander(paste0(total_suspensions, "%", sep= ""))
}


```

The number of the valid entries is **`r nrow(suspensions_q2q1)`**, and the percent of students who have decreased their suspensions or did not have any suspensions is **`r suspensions_success()`**

### Suspensions Change: Plot of suspsention changes from Q1 to Q2. 

```{r echo=FALSE}

suspensions_change <- with(suspensions_q2q1,table(susp_diff))

pander(suspensions_change)

susp_diff<- pander(mean(suspensions_q2q1$susp_diff, na.rm=TRUE))

#suspensions_change_1 <- with(suspensions_q2q1,table(susp_diff < 0))

#pander(suspensions_change_1)


#suspensions_change_2 <- with(suspensions_q2q1,table(susp_diff ==0, susp_sum.y==0))

#pander(suspensions_change_2)




#plot(suspensions_change)
```

The average difference of supsentions between Quarter 1 and Quarter 2 is `r susp_diff`


```{r echo=FALSE}

colnames (suspensions_q2q1) [2] <- "Council"
colnames (suspensions_q2q1) [3] <- "Q1_Suspenions"
colnames (suspensions_q2q1) [4] <- "Q2_Suspensions"
colnames (suspensions_q2q1) [5] <- "Suspensions_Change"

```

Suspensions Change Plots from Quarter 1 to Quarter 2. 

The plot below reflects that their has been an increase in suspensions from  Quarter 1 to  Quarter 2. The council is on the veticial axis and the suspensions change is on the bottom axis. The desire is for the cirlces to be on the left.  
```{r echo=FALSE, warning=FALSE}

suspenesions_change_plot_c <- ggplot(suspensions_q2q1,(aes(x = Suspensions_Change, y = Council)))

suspenesions_change_plot_c + geom_count()

#suspenesions_change_plot2 <- ggplot(suspensions_q2q1,(aes(x = Suspensions_Change, y = Q1_Suspenions)))

#suspenesions_change_plot2 + geom_count()






```


### Trend Data

### Trend Data Q4 2015 to Q2 2016

