---
title: "Suspensions"
author: "Kevin Gilds, MPA"
date: "`r Sys.Date()`"
output: html_document
---


```{r echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(dplyr)
library(pander)
library(ggplot2)
library(sqldf)

###Set directory to find data 
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

### Connect with database
getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")

###Read q1 suspension data from data base and assign varible
q1_suspensions <- dbReadTable(getReal_2016db, "Q1_Suspensions")

### Read q2 suspension data base and assign to variable
q2_suspensions <-dbReadTable(getReal_2016db, "Q2_Suspensions")

q3_suspensions <-dbReadTable(getReal_2016db, "Q3_Suspensions")

q4_suspensions <-dbReadTable(getReal_2016db, "Q4_Suspensions")


```



#Improvement In School Behavior

## Objective:
*70% of participating students will show improvement in behavior by decreasing their number of suspensions from the baseline grading period to final grading period or not having a suspension during the school year as evidenced from the student's report card/school reports.*
 

```{r echo=FALSE}

### Merge q1 and q2 suspension data by girlCode
susp_q1q4 <- inner_join(q1_suspensions, q4_suspensions, by="girlCode")

#head(susp_q1q4)

missing_q1q4 <- anti_join(q4_suspensions, q1_suspensions, by="girlCode")

#head(missing_q1q4)

susp_q2q4 <- inner_join(missing_q1q4, q2_suspensions, by="girlCode")

#head(susp_q1q4)

#dim(susp_q2q4)

#names(susp_q1q4)
#names(susp_q2q4)

```


```{r echo=FALSE}
susp_q1q4 <-susp_q1q4 %>%
    select(1,2, 6, 11)

#names(susp_q1q4)

colnames(susp_q1q4) [1] <- "council"
colnames(susp_q1q4) [3]<- "baseline"
colnames(susp_q1q4) [4]<- "final"

susp_q1q4 <- susp_q1q4 %>%
    mutate("Time" = "Q1Q4")

```



```{r echo=FALSE}
susp_q2q4 <-susp_q2q4 %>%
    select(1,2, 6, 11)

#names(susp_q2q4)

colnames(susp_q2q4) [1] <- "council"
colnames(susp_q2q4) [3]<- "baseline"
colnames(susp_q2q4) [4]<- "final"

susp_q2q4 <- susp_q2q4 %>%
    mutate("Time" = "Q2Q4")

#head(susp_q2q4)

#dim(susp_q2q4)

#names(susp_q2q4)
#names(susp_q1q4)

```


```{r echo=FALSE}

susp_2016 <- rbind(susp_q1q4, susp_q2q4)

#dim(susp_2016)

```

```{r echo=FALSE}
###make caluculated field   
susp_2016 <- susp_2016 %>%
    mutate(susp_diff = final - baseline)

##Ensure there are no cases with NA
susp_2016 <- susp_2016 %>%
    filter(susp_diff != "NA")


#head(susp_2016)
```


```{r council_filter_suspenions, echo=FALSE}
susp_2016 <- susp_2016 %>%
    filter(council == "West Central Council")


```



```{r echo=FALSE}
no_susp <- filter(susp_2016, baseline == 0 & final == 0)

#nrow(no_susp)

#head(no_susp)

decrease <- filter( susp_2016, susp_diff < 0 )

#head(decrease)

#nrow(decrease)

```



```{r echo=FALSE}
suspensions_success <- function() {
    no_suspensions <- filter(susp_2016, baseline == 0, final == 0) ##Filter students without a suspension
    decrease_suspensions <- filter(susp_2016, susp_diff <0) ##Filter students who decreased their suspensions
    total_suspensions <- nrow(no_suspensions) + nrow(decrease_suspensions) # add no suspensions and decreased students together for positive outcome
    total_suspensions <- total_suspensions/nrow(susp_2016) # divide positive outcome students from total students
    total_suspensions <- round(total_suspensions*100,2) #make into percentage
    pander(paste0(total_suspensions, "%", sep= "")) # add in percent sign
}


```





```{r echo=FALSE}

suspensions_change <- with(susp_2016,table(susp_diff)) ###Make a table showing all outcomes

pander(suspensions_change) ### display pretty table

susp_diff<- pander(mean(susp_2016$susp_diff, na.rm=TRUE)) ##obtain mean difference

#suspensions_change_1 <- with(suspensions_q2q1,table(susp_diff < 0))

#pander(suspensions_change_1)


#suspensions_change_2 <- with(suspensions_q2q1,table(susp_diff ==0, susp_sum.y==0))

#pander(suspensions_change_2)




#plot(suspensions_change)
```

The number of student records that could be matched is **`r nrow(susp_2016)`**.  

* The percent of students with a successufl outcome is **`r suspensions_success()`**. 

1. The number of students who decreased their suspensions from baseline to final  is  **`r nrow(decrease)`**

2. The number of students who had no suspensions during baseline and final grading period **`r nrow(no_susp)`**

The average difference of suspensions between basline and final grading period is **`r susp_diff`**





```{r echo=FALSE}

colnames (susp_2016) [1] <- "Council"  #change element #1 name to make a pretty graph
colnames (susp_2016) [3] <- "basline"#change element #2 to make a pretty graph
colnames (susp_2016) [4] <- "final"#change element #3 to make a pretty graph
colnames (susp_2016) [6] <- "Suspensions_Change"#change name of element #5 to make a pretty graph

```




### Suspensions Change Plots from baseline to final grading period:

The plot below reflects that their has been an increase in suspensions from baseline  to final. The council is on the vertical axis and the suspensions change is on the bottom axis
```{r echo=FALSE, warning=FALSE}

suspenesions_change_plot_c <- ggplot(susp_2016,(aes(x = Suspensions_Change, y = Council)))

suspenesions_change_plot_c + geom_count() #display ggplot of Suspsenion change by Council 

#suspenesions_change_plot2 <- ggplot(suspensions_q2q1,(aes(x = Suspensions_Change, y = Q1_Suspenions)))

#suspenesions_change_plot2 + geom_count()






```

```{r echo=FALSE, eval=FALSE}

## Trend Data

###Change working directory
setwd("C:/Users/kevin/Dropbox/GetReal/Reports/MY-2014-2015/Summ Evaluation Report/data")

###Conncent to database with 2015 data
getRealdb<- dbConnect(SQLite(), dbname="data_Final_GetReal_2014_2015.sqlite")

### Read data from with 2015 data
suspensions_2015 <- dbReadTable(getRealdb, "matched_suspenions")



```

```{r echo=FALSE, eval=FALSE}


###Merge and find matches from q4 2015 to q2 2015
susp_match <- inner_join(suspensions_q2q1, suspensions_2015, by="girlCode")



###Make calculated field from old database
susp_match <- susp_match %>%
    mutate(final.x + final.y)


###Change column name to make for easir calculated field
colnames(susp_match)[16] <-"Q4_2015"

### Make calculated field
susp_match <- susp_match %>%
    mutate(Q4_2015-Q2_Suspensions)


### Give caluculated field a better name
colnames(susp_match)[17] <- "susp_trend"



```


```{r echo=FALSE, eval=FALSE}

###narrow variable selection
susp_history <- susp_match %>%
    select(Q1_Suspenions, Q2_Suspensions, Q4_2015)

### List value
susp_history

### Plot the values
plot(susp_history)

```



```{r echo=FALSE}

susp_success <-function(){
    susp_match_no <-filter(susp_match, Q4_2015 == 0, Q2_Suspensions ==0) #find studens with no suspensions
    susp_data_m <-filter(susp_match, susp_trend <0) #find students who decreased their suspsenions
    susp_data_m2 <- nrow(susp_match_no) + nrow(susp_data_m) #add positive outcome students together
    susp_data_1m <- susp_data_m2/nrow(susp_match) #divide postive outcomes from total
    susp_data_percen1 <- round(susp_data_1m*100,2) #obtain percent
    pander(paste0(susp_data_percen1, "%", sep=""))#make pretty and add percent sign
}



```

```{r echo=FALSE, eval=FALSE}

susp_match_m <- mean(susp_match$susp_trend)

susp_match_m <- round(susp_match_m,2)

```




```{r echo=FALSE, eval=FALSE}
suspenesions_change_plot_m <- ggplot(susp_match,(aes(x = susp_trend, y = Council)))

suspenesions_change_plot_m + geom_count() #plots change by council


```


```{r echo=FALSE, eval=FALSE}

plot(susp_match$susp_trend, ylab="Suspension Difference", xlab="Matched Students")
abline(h=0, col="red") #plots changes by student observation
```



