---
title: "Widget_test"
author: "Kevin Gilds, MPA"
date: "February 15, 2016"
output: html_document
---

```{r}
library(sqldf)
setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")

getReal_2016db<- dbConnect(SQLite(), dbname="outcome_history.sqlite")


```

```{r}
library(htmlwidgets)

```


```{r}

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(dplyr)
library(pander)
library(ggplot2)
library (ezknitr)

setwd("C:/Users/kevin/Dropbox/GetReal/Data/sqlite")


### Make connection with database
girl <- dbReadTable(getReal_2016db, "girl_pre")

###Select the neeeded data for data entry status update
girl <- select(girl, council)
###Create and add column for status update
girl$dataSource <-"girl"

### Make connection with database
parent <-dbReadTable(getReal_2016db,"pre_parent")
###Select the neeeded data for data entry status update
parent <- select(parent,council)
###Create and add column for status update
parent$dataSource <- "parent"

### Make connection with database
teacher <-dbReadTable(getReal_2016db, "pre_teacher")
###Select the neeeded data for data entry status update
teacher <-select(teacher,council)
###Create and add column for status update
teacher$dataSource <- "teacher"

###Bind girl and parent objects to prepare for status report
girl_parent <- rbind(girl,parent)

### Make connection with database
grades_q1 <- dbReadTable(getReal_2016db,"Q1_Absences")
###Select the neeeded data for data entry status update

q1_stats <- select(grades_q1,council.x)
###Change column name to make it match with other data sets
colnames (q1_stats) [1] <- "council"
###Create and add column for status update
q1_stats$dataSource <- "Q1"


### Add the teacher to binding for status report
add_teacher <- rbind(girl_parent, teacher)


###Findal addition to create data frame for status report
survey_status <- rbind(add_teacher, q1_stats)

### Read the pre girl survey for reference down stream
girl_survey_dupes <-dbReadTable(getReal_2016db, "girl_pre_duplicates")
### Read the pre girl survey for reference down stream
parent_survey_dupes <-dbReadTable(getReal_2016db, "pre_parent_duplicate")
### Read the pre girl survey for reference down stream
q1_dupes <-dbReadTable(getReal_2016db, "Q1_duplicates")

### Reade the girl_pre_survey database for analysis. 
outcomes <- dbReadTable(getReal_2016db, "girl_pre")
###Select the variables of interest from the pre_survey
outcomes <- select(outcomes, girlCode, school, council, hr.avg, am.avg, ae.avg)

#### Read q1_reading data from database for analysis
q1_reading <-dbReadTable(getReal_2016db, "Q1_reading")

### Read q1_langarts data from database for analysis
q1_langarts <-dbReadTable(getReal_2016db,"Q1_lang")

###Read q1_absences data from database for analysis
q1_absences <-dbReadTable(getReal_2016db, "Q1_Absences")

###Read q2_absences data from database for analysis
q1_suspensions <- dbReadTable(getReal_2016db, "Q1_Suspensions")


###Read academic data from database for file explort
academic_data <- dbReadTable(getReal_2016db, "academic_data")



```

```{r}
library(DT)



datatable(outcomes, options = list(pageLength = 5))

```


